### 2015-02-03 abstract.tex
Updating with a new abstract

In this work, we cast the well-known Poisson surface reconstruction algorithm into a more general setting, we reformulate it in terms of shift invariant spaces (spaces that are spanned by lattice translates of an admissible generating function). The treatment is general, but our specific interest is in reconstructing a surface of a solid model from an oriented point-set within function spaces defined over the body centred cubic lattice. We also propose a general framework for approximating the solution to Poisson?s equation in a hypercube with zero Dirichlet boundary conditions, and a new variational scheme to re-sample the initial oriented point-set onto a regular grid. Once the points have been re-sampled onto a grid, the rest of the pipeline is purely based on digital filtering. We also analyze the error incurred via the digital filtering approximation methodology and propose a Fourier domain error kernel that can be used to design solution filters that fully exploit the approximation capabilities of the target space. Finally, we show that a host of Poisson-like methods fail to take advantage of the full approximation spaces over which they are defined.

%We analyze the error incurred via this approximation methodology and propose a Fourier domain error kernel that can be used to design solution filters that fully exploit the approximation capabilities of the target space and are akin to interpolation and quasi-interpolation filters.

%Our error kernel formulation is validated by conducting numerical experiments on the two dimensional square lattice and the three dimensional Cartesian and body-centered cubic lattices. Additionally, we comment on the equivalence between our method and the finite element method and show how our error kernel formulation can be easily extended to a larger class of differential operators.

%1. Intro:
%Highlight the additional contribution that we formulate a way to solve the Poisson equation on non-Cartesian lattices.

%2. Related work:
%Update references with the work Torsten pointed out and the recent surface reconstruction survey that I mentioned. 
%Cite additional work that talks about the benefits of non-Cartsian lattices (in volume rendering, flow simulation etc.). 
There are a couple of works that deal with solving Poisson?s equation on non-Cartesian lattices. Please see the attached version of my paper.

3. Preliminaries:
Move sections 3.3.1 and 3.3.2 to section 6. Introduce 3.4 earlier.

4. Approach:
Expand 4.3 into a new section ? section 5. Move Table 1 to section 6.

5. Solving Poisson?s Equation.
This section spells out the details of the filtering methodology for solving Poisson?s equation. I will work on this part. The aim would be to condense the material so that it blends well with the rest of the paper.

6. Results and Discussion.
Start by introducing the specific lattices, basis functions, filters used for the experiments (3.3.1, 3.3.2 and table 1 should come here). Additionally, need a subsection here that derives the filter weights for CC and BCC. The rest of the section shows the comparative surface reconstruction experimental results + discussion.

7. Conclusion.
Usual mumbo jumbo.

### 2015-02-03 abstract.tex
Adding old intro and old figures

@@
 %Cite additional work that talks about the benefits of non-Cartsian lattices (in volume rendering, flow simulation etc.). 
-There are a couple of works that deal with solving Poisson?s equation on non-Cartesian lattices. Please see the attached version of my paper.
+%There are a couple of works that deal with solving Poisson?s equation on non-Cartesian lattices. Please see the attached version of my paper.
 
-3. Preliminaries:
-Move sections 3.3.1 and 3.3.2 to section 6. Introduce 3.4 earlier.
+%3. Preliminaries:
+%Move sections 3.3.1 and 3.3.2 to section 6. Introduce 3.4 earlier.
 
-4. Approach:
-Expand 4.3 into a new section ? section 5. Move Table 1 to section 6.
+%4. Approach:
+%Expand 4.3 into a new section ? section 5. Move Table 1 to section 6.
 
-5. Solving Poisson?s Equation.
-This section spells out the details of the filtering methodology for solving Poisson?s equation.
+%5. Solving Poisson?s Equation.
+%This section spells out the details of the filtering methodology for solving Poisson?s equation.
 I will work on this part.
@@
 
-6. Results and Discussion.
-Start by introducing the specific lattices, basis functions, filters used for the experiments (3.3.1, 3.3.2 and table 1 should come here).
+%6. Results and Discussion.
+%Start by introducing the specific lattices, basis functions, filters used for the experiments (3.3.1, 3.3.2 and table 1 should come here).
 Additionally, need a subsection here that derives the filter weights for CC and BCC.
@@
 
-7. Conclusion.
-Usual mumbo jumbo.
+%7. Conclusion.
+%Usual mumbo jumbo.

### 2015-02-03 introduction.tex
Adding old intro and old figures

\section{Introduction}

\label{sec:intro}
The reconstruction of solid models from scattered point data is common and well studied problem in the field of computer graphics. Interest stems from the desire to convert real life data-sets acquired from range scanners to polygonal models. The idea also has applications in mesh cleaning (re-meshing or hole filling.) A common approach, given an oriented point set, is to find an implicit function such whose iso-surface corresponds to an approximation of the original surface.

In this work we apply the theory behind shift-invariant spaces (function spaces spanned by the lattice translates of a generating kernel) to the Poisson surface reconstruction problem. The extension to these function spaces allows us to choose non-Cartesian lattice sites to which we anchor our kernel functions (\SC{sec:smpl_review}). Although our approach is general and applicable to any shift-invariant spanned by sufficiently smooth basis functions, we are specifically interested in those defined over the \emph{Body Centered Cubic} (BCC) lattice. Our focus is on reconstructing an approximate indicator function (a function that evaluates to one inside the model, and zero outside) in optimal function spaces, arguing that the sub-optimality of Cartesian-like methodologies may impact the accuracy of reconstructed surfaces.

\begin{figure*}
  \centering
  \mbox{} \hfill
	\includegraphics[width=.3\linewidth]{figures/lattice/cc}
	\includegraphics[width=.3\linewidth]{figures/lattice/bcc}
	\includegraphics[width=.3\linewidth]{figures/lattice/fcc} \\

  \mbox{} \hfill
	\includegraphics[width=.3\linewidth]{figures/lattice/cc_cell}
	\includegraphics[width=.3\linewidth]{figures/lattice/bcc_cell}
	\includegraphics[width=.3\linewidth]{figures/lattice/fcc_cell} \\
   \hfill \mbox{}
  \caption{\label{fig:lattices}%
  Sampling lattices (top) with with their corresponding Voronoi regions (bottom). Left to right are the CC, BCC and FCC lattices respectively.
  }
\end{figure*}

The advantage of moving to the BCC lattice is two fold. First, it is well known that the BCC lattice generates the optimal sampling pattern in $\realn^3$. The argument for optimality is simple; a sampling of a function with respect to the BCC lattice is tantamount to a periodization of it's frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice. Optimality follows from the observation that the FCC lattice represents the optimal sphere packing in three dimensions, that is, it packs frequency replica as tightly as possible, resulting in less \emph{pre-aliasing} from sampling. For isotropically band-limited functions, the tighter packing of frequency content allows for about 30\% more information to be captured when compared to samplings generated from the Cartesian lattice. Second, there exist reconstruction filters on the BCC lattice that outperform equivalent filters on the Cartesian lattice in terms of both speed and accuracy \cite{practicalbox} (in software implementations.) These filters are also more compact than their typical Cartesian counterparts. In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice, and tend to provide faster convergence.

Our surface reconstruction methodology follows the general Poisson
approach. First, we construct a smoothed approximation to the gradient
field of a model's indicator function. The divergence of the gradient
field is estimated and subsequently fed into a Poisson solver that
outputs the coefficients needed to approximate the smoothed indicator
function in a target shift invariant space. This Poisson solver is tailored to cater to the approximation power provided by each space \cite{}. However, our approach is novel in two notable ways. Firstly, we employ a variational scheme to obtain a lattice-based approximation of the gradient field. This
scheme depends only on the generating kernel of the target space and optimizes a functional that incorporates interpolation and smoothness constraints. Secondly, we utilize the theory behind shift-invariant spaces to seek discretizations of the divergence and Laplacian operators that are tailored to exploit the full approximation capabilities of the target space.

Additionally, we also consider the possibility of approximating the
smoothed gradient field representation within function spaces that are
spanned by shifted versions of a single generating kernel. In the
context of gradient estimation, introducing a shift in the direction
of the derivative has shown to improve overall gradient
approximation fidelity in terms of gradient orientation and magnitude,
as well as displaying the ability to capture higher frequency details
that are smoothed out in non-shifted schemes~\cite{gradrev}. Since the
divergence operator is intimately connected to the gradient operator,
these results are of interest to us as using an appropriate
discretization of the derivative/divergence operator is an important facet
of recovering the indicator function of the initial model.

To summarize, our contributions are as follows:
\begin{itemize}
\item[$\bullet$] We cast the Poisson surface reconstruction problem
  into the framework of shift-invariant spaces.
\item[$\bullet$] Specifically, we investigate the reconstruction of
  surfaces in both a sub-optimal (Cartesian) and an optimal (BCC)
  box-spline function space.
\item[$\bullet$] We present a variational scheme that not only considers
  the usual centered generating kernels, but allows for the
  possibility of recovering each component of the gradient field in a
  space spanned by a shifted kernel. On the Cartesian
  lattice, these components are orthogonal whereas on the BCC lattice,
  the components are non-orthogonal and correspond to the directions
  associated with the underlying box-spline matrix.
\item[$\bullet$] While our focus is on comparing the surface reconstruction algorithm on both the CC and BCC lattices, we also provide qualitative and quantitative comparisons between the presented technique (on both the Cartesian and BCC lattices) and similar methods. 
\end{itemize}

### 2015-02-04 introduction.tex
Reworking intro (trimming the fat, and adding error kernel stuffs.

@@
 \label{sec:intro}
-The reconstruction of solid models from scattered point data is common and well studied problem in the field of computer graphics.
-Interest stems from the desire to convert real life data-sets acquired from range scanners to polygonal models.
-The idea also has applications in mesh cleaning (re-meshing or hole filling.) A common approach, given an oriented point set, is to find an implicit function such whose iso-surface corresponds to an approximation of the original surface.
+Reconstructing a solid model from a scattered set of points is a common and well studied problem in computer graphics.
+Interest in this problem is rooted in the desire to convert real life data-sets -- acquired from range and now increasingly from commodity hardware like the Kinect -- to 3D polygonal models.
+The idea also has a applications in model re-meshing and hole filling.
+\ednote{This needs more meat, it's a pretty weak ending to the intro paragraph.}
 
-In this work we apply the theory behind shift-invariant spaces (function spaces spanned by the lattice translates of a generating kernel) to the Poisson surface reconstruction problem.
-The extension to these function spaces allows us to choose non-Cartesian lattice sites to which we anchor our kernel functions (\SC{sec:smpl_review}).
-Although our approach is general and applicable to any shift-invariant spanned by sufficiently smooth basis functions, we are specifically interested in those defined over the \emph{Body Centered Cubic} (BCC) lattice.
-Our focus is on reconstructing an approximate indicator function (a function that evaluates to one inside the model, and zero outside) in optimal function spaces, arguing that the sub-optimality of Cartesian-like methodologies may impact the accuracy of reconstructed surfaces.
+Given an oriented point-set, a common approach is to find an implicit function whose iso-contour corresponds to an approximation of the original surface.
+In this work we take a ``signal processing'' approach to this problem -- we cast the problem into a general shift-invariant setting.
+More explicitly, we reconstruct the desired implicit function within a function space spanned by lattice translates of a single generating function.
+The extension to this class of function spaces allows us to consider anchoring our basis functions at non-Cartesian lattice sites (\SC{sec:smpl_review}).
+Our approach is general and applicable to any valid lattice and generator, but our implementation is narrowed to applicable function spaces over the \emph{Body Centred Cubic} (BCC) and \emph{Cartesian} (CC) lattices.
 
@@
 The advantage of moving to the BCC lattice is two fold.
-First, it is well known that the BCC lattice generates the optimal sampling pattern in $\realn^3$.
-The argument for optimality is simple; a sampling of a function with respect to the BCC lattice is tantamount to a periodization of it's frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice.
-Optimality follows from the observation that the FCC lattice represents the optimal sphere packing in three dimensions, that is, it packs frequency replica as tightly as possible, resulting in less \emph{pre-aliasing} from sampling.
-For isotropically band-limited functions, the tighter packing of frequency content allows for about 30\% more information to be captured when compared to samplings generated from the Cartesian lattice.
-Second, there exist reconstruction filters on the BCC lattice that outperform equivalent filters on the Cartesian lattice in terms of both speed and accuracy \cite{practicalbox} (in software implementations.) These filters are also more compact than their typical Cartesian counterparts.
-In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice, and tend to provide faster convergence.
+First, it's well known that the BCC lattice generates the optimal sampling pattern in $\realn^3$.
+The argument for optimality is simple; the sampling of a function with respect to the BCC lattice is equivalent to a periodization of it's frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice.
+Optimality follows from the observation that the FCC lattice is the optimal sphere packing lattice in three dimensions, that is, it packs frequency replica as tightly as possible in the Fourier domain, resulting in less \emph{pre-aliasing} from sampling.
+For isotropically band-limited functions, this tighter packing of frequency content allows for about 30\% more information to be captured when compared to samplings generated from a Cartesian lattice.
+The second advantage to moving to the BCC lattice is that there exist reconstruction filters on the BCC lattice that outperform commonly used filters of equivalent order on the CC lattice in terms of both speed and accuracy \cite{practicalbox} (in software implementations) -- these filters are also more compact than their typical CC counterparts.
+In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice and tend to provide faster convergence when optimizing the initial point set (\SC{sec:that-section-where-i-describe-this}.)
 
-Our surface reconstruction methodology follows the general Poisson
-approach. First, we construct a smoothed approximation to the gradient
-field of a model's indicator function. The divergence of the gradient
-field is estimated and subsequently fed into a Poisson solver that
-outputs the coefficients needed to approximate the smoothed indicator
-function in a target shift invariant space.
-This Poisson solver is tailored to cater to the approximation power provided by each space \cite{}.
+Our surface reconstruction methodology follows the general Poisson approach, but with a few twists.
+First, we construct a smoothed approximation to the gradient field of a model's indicator function.
+The divergence of the gradient field is estimated and subsequently fed into a Poisson solver that outputs the coefficients needed to approximate the smoothed indicator function in a target shift invariant space.
+This Poisson solver is tailored to cater to the approximation power provided by each space.
 However, our approach is novel in two notable ways.
 Firstly, we employ a variational scheme to obtain a lattice-based approximation of the gradient field.
-This
-scheme depends only on the generating kernel of the target space and optimizes a functional that incorporates interpolation and smoothness constraints.
+This scheme depends only on the generating kernel of the target space and optimizes a functional that incorporates interpolation and smoothness constraints.
 Secondly, we utilize the theory behind shift-invariant spaces to seek discretizations of the divergence and Laplacian operators that are tailored to exploit the full approximation capabilities of the target space.
 
-Additionally, we also consider the possibility of approximating the
-smoothed gradient field representation within function spaces that are
-spanned by shifted versions of a single generating kernel. In the
-context of gradient estimation, introducing a shift in the direction
-of the derivative has shown to improve overall gradient
-approximation fidelity in terms of gradient orientation and magnitude,
-as well as displaying the ability to capture higher frequency details
-that are smoothed out in non-shifted schemes~\cite{gradrev}. Since the
-divergence operator is intimately connected to the gradient operator,
-these results are of interest to us as using an appropriate
-discretization of the derivative/divergence operator is an important facet
-of recovering the indicator function of the initial model.
+Additionally, we consider the possibility of approximating the smoothed gradient field representation within function spaces that are
+spanned by shifted versions of a single generating kernel. In the context of gradient estimation, introducing a shift in the direction
+of the derivative has shown to improve overall gradient approximation fidelity in terms of gradient orientation and magnitude,
+as well as displaying the ability to capture higher frequency details that are smoothed out in non-shifted schemes~\cite{gradrev}.
+Since the divergence operator is intimately connected to the gradient operator, these results are of interest to us.
+Using an appropriate discretization of the derivative/divergence operator is an important step in recovering the indicator function of the initial model.
+\ednote{Need to emphasize the error-kern here}
 
@@
 \begin{itemize}
-\item[$\bullet$] We cast the Poisson surface reconstruction problem
-  into the framework of shift-invariant spaces.
-\item[$\bullet$] Specifically, we investigate the reconstruction of
-  surfaces in both a sub-optimal (Cartesian) and an optimal (BCC)
+\item[$\bullet$] We cast the Poisson surface reconstruction problem into the framework of shift-invariant spaces.
+\item[$\bullet$] Specifically, we investigate the reconstruction of surfaces in both a sub-optimal (Cartesian) and an optimal (BCC)
   box-spline function space.
-\item[$\bullet$] We present a variational scheme that not only considers
-  the usual centered generating kernels, but allows for the
-  possibility of recovering each component of the gradient field in a
-  space spanned by a shifted kernel. On the Cartesian
-  lattice, these components are orthogonal whereas on the BCC lattice,
-  the components are non-orthogonal and correspond to the directions
-  associated with the underlying box-spline matrix.
+\item[$\bullet$] We present a variational scheme that not only considers the usual centered generating kernels, but allows for the
+  possibility of recovering each component of the gradient field in a space spanned by a shifted kernel. On the Cartesian
+  lattice, these components are orthogonal whereas on the BCC lattice,  the components are non-orthogonal and correspond to the directions associated with the underlying box-spline matrix.
+\item[$\bullet$] We present an extension of the error kernel of Blu and Unser to general linear operators, and show how to design filters that respect the approximation order of the approximation space.
 \item[$\bullet$] While our focus is on comparing the surface reconstruction algorithm on both the CC and BCC lattices, we also provide qualitative and quantitative comparisons between the presented technique (on both the Cartesian and BCC lattices) and similar methods.
 \end{itemize}
+
+\ednote{OVERALL: What is lacking from this intro is the true purpose of this work (from the surface reconstruction aspect.) We want to show that the BCC beats the CC lattice.
+NOT that our scheme is better than Kazhdan's.
+We do show this, but we need to emphasize it above!}

### 2015-02-05 relatedwork.tex
Importing the old prelim and bg info.

\section{Related Work}
.
Surface reconstruction is an active area of research in computer graphics. It is beyond the scope of this work to touch on all the relevant research surrounding the subject. Thus, we only very briefly review some relevant contributions. Those seeking a more in-depth review may look to a recent survey of the subject \cite{sve05ss}, we focus mainly on some of the more related recent developments.

Surface reconstruction algorithms generally fall under two categories:
\emph{implicit} algorithms and \emph{explicit} algorithms. The common
theme of implicit algorithms is the desire to find an implicit
function $f : \realn^3 \mapsto \realn $, for which the iso-surface
defined by $f(\mathbf{x})=s$ (for some iso-value $s \in \realn$)
represents an approximation to the original surface. Explicit
algorithms rely on combinatorial techniques, inferring meshes through
a set predefined logic or rules.

In terms of explicit algorithms, there exist many Delaunay style
algorithms in which a triangulation is constructed using only a subset
of the original point-set \cite{delaunay}. The Power Crust
\cite{powercrust} and Cocone \cite{cocone} algorithms are two
well-known techniques that fall under this category. These techniques
often aim to interpolate the input point set, thus in the presence of
noise, tend to over-fit the surface. When the input data are noisy,
implicit approaches often perform better, as they inherently attempt
to fit locally smooth basis functions to the data, averaging out any
noise. Reconstructing either a distance function or an indicator
function is common to these approaches.

One of the most well known implicit algorithms is the %Graph Cut \tm{this is not graph cuts!!}
algorithm of by Hoppe et al.~\cite{hoppecut}. In this work a set of
tangent planes is constructed to create an approximation to a
surface's distance function. A more recent work, is the Smoothed
Signed Distance Field reconstruction technique \cite{ssdrecon}, in
which an oriented point set imposes constraints on the reconstructed
function, its gradient, and its Hessian. These constraints are
tantamount to requiring that the reconstructed function be an
approximation to the distance field of the original model. Other
techniques attempt to reconstruct a signed distance function within a
function space spanned by radial basis functions \cite{radial}.
Recently, there has also been research that incorporates point normals
into the radial basis reconstruction framework \cite{hermite}.

Another approach is to find an approximate indicator function of the
original model. A well known technique \cite{fftk} transforms the
smoothed gradient to the Fourier domain, inverts it, then reconstructs
it in the spatial domain. This approach often deals well with
incomplete, missing or otherwise noisy data, with the guarantee of
creating a water tight surface. However, it involves reconstructing
the indicator on a regular grid, which becomes very memory intensive
as the grid is refined.

Poisson surface reconstruction techniques make the observation that
the Fourier method is equivalently stated as a spatial Poisson problem
\cite{Kazhdan06,screenedk}. Moreover, they seek to rectify the memory
limitations of said work, while still maintaining the benefits it
provides. However, current techniques based on this idea have been
shown to over-smooth the initial point-set, and thus the resulting
surface. \cite{reconbench}.

It is also possible to reconstruct the indicator of a point set within
a wavelet basis \cite{wavelet}. In this work, an approximate indicator
function of the model is projected onto a compact wavelet basis. This
leads to a simple and efficient algorithm even when the data sets
are massive. However the method's speed comes at a price, as the
resulting surfaces are often non-smooth, and display many ``jagged''
artifacts (although a form of smoothing is applied to the resulting
indicator function in an attempt to rectify this.)

Our approach aims to solve the Poisson surface reconstruction problem
in the setting of shift-invariant spaces. A crucial step in this
regard is the accurate estimation of the divergence of the gradient
field from the oriented point-set. Radial basis functions (RBFs) are
generally used in the context of the reconstruction of scattered data. 
However, RBF techniques are often computationally
expensive, requiring the solution of large unstable systems of
equations (for exact interpolation.) A proposed solution to this
problem is to ``\emph{re-sample}'' the input data onto a regular
shift-invariant space . This allows one to use efficient compact
reconstruction kernels and data processing techniques
\cite{variational,onvari}. Recently, an extension of this idea to box
spline spaces \cite{xu2012rec} proposes a variational reconstruction
framework in which the BCC lattice consistently outperforms the
Cartesian lattice. Our method takes a similar variational approach and
seeks to construct a smoothed lattice-based approximation of the
gradient of the indicator function (\SC{sec:obtainingV}). Our employed
constraints force the gradient to be close to zero away from the
surface, while maintaining a certain degree of smoothness in the
resulting approximation. This is preferable in comparison to other
works \cite{fftk,Kazhdan06,screenedk} in which each sample is
trilinearly distributed about either a grid or an oct-tree
respectively, and is known to over-smooth data.

Having obtained a high-quality lattice-based approximation of the
gradient field, we invoke the theory behind shift-invariant spaces,
and accurately estimate the divergence by applying derivative filters
that are designed to harness the full approximation capabilities of
the target space (\SC{sec:divergence}). In a similar manner, we then
solve the Poisson equation by applying an \emph{inverse} Laplacian
filter that is tailored to match the approximation order of the target
space (\SC{sec:recoveringX}).

### 2015-02-05 review.tex
Importing the old prelim and bg info.

\section{Preliminaries}\label{sec:pois_review}
\subsection{Poisson Surface Reconstruction}
We denote the indicator function of a model $M$ as $$ \chi_M(\mathbf{x}) :=
\begin{cases}
1, & \text{if }\mathbf{x}\text{ is in the interior of the model } M \\
\frac{1}{2}, & \text{if } \mathbf{x}\text{ is on the model's surface}\\
0, & \text{if }\mathbf{x}\text{ is exterior to } M
\end{cases}. $$
Integral to formulating surface reconstruction as a Poisson problem, is the observation that if one obtains some function $\vec{V}(\mathbf{x})\approx{\nabla}\chi_M$ that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small 
\begin{equation} \label{eq:poisson}
	\lapl{\inda} = {\grad} \cdot \vec{V}.
\end{equation}}
We define the set of input surface points to be $P:=\{(\mathbf{p}_1,\mathbf{n}_1), (\mathbf{p}_2,\mathbf{n}_2) \hdots (\mathbf{p}_M,\mathbf{n}_M) : (\mathbf{p}_i,\mathbf{n}_i) \in
\realn^3 \times \realn^3 \}$ where $\mathbf{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively. Orientation can be succinctly represented with only two values, however, it is convenient to keep it denoted as the normal at a point. This is because the length of the normal can be used to encode the sampling density of the point-set at a point. For the following discussion, we also need to introduce the notation $\patch_{\mathbf{s}}$, which denotes a patch of the surface model about the sample location $\mathbf{s}$.

Inspired by the approach of Kazhdan et al.~\cite{Kazhdan06} the approximation $\vec{V}(\vx)$ is defined to be  {\small 
\begin{eqnarray}
	\vec{V}(\vx) & := & \sum_{(\mathbf{s},\mathbf{n}) \in P}\left|\patch_s\right|F(\vx-\mathbf{s})\cdot\vn \label{eq:vdef} \\
	 & \approx & \sum_{(\mathbf{s},\mathbf{n}) \in P} \int_{\patch_s}{F(\mathbf{x} - \mathbf{p}) \nabla \chi (\mathbf{p})} \mathrm{d} \mathbf{p}. \notag  
\end{eqnarray}}
Thus, $\vec{V}(\vx)$ approximates the gradient of the indicator smoothed by some filter $F$, broken up over surface patches of the model. We assume the point sampling to be uniform, thus the area of each patch $\left|\patch_s\right|$ should be a constant, and our resulting approximation will be scaled by an unknown factor. We return to this in \SC{sec:levelset}. The choice of $F$ places computational constraints on the resulting algorithm.

$F$ is often explicitly chosen to be a compactly supported function. This simplifies and reduces the computational cost of the method when used in conjunction with an oct-tree based representation of $\vec{V}(\vx)$ \cite{Kazhdan06}. However, there is a disadvantage in that $F$ may over smooth data in areas of high curvature \cite{reconbench}, much in the same way that a representation of a sampled signal may fail to take advantage of the full approximation power of the function space in which it is represented if it is not properly prefiltered. Theoretically, one could reconstruct the surface at higher resolutions, allowing the basis functions to become more ``fine'', but increasing the total amount of memory used. However, this is not realistic in praxis. Another approach is to impose a type of ``interpolation'' constraint on the original data \cite{screenedk}.

Ideally, the filter $F$ should correspond to some globally supported RBF. However, as the support of $F$ grows, so does the cost of evaluating it at lattice sites. Moreover, the added benefit of a globally supported RBF is partially lost as the subsequent steps are entirely lattice-based and do not take the RBF into consideration. Our approach circumvents the choice of $F$ entirely by posing the gradient approximation problem as a variational problem that, in addition to imposing the interpolation constraint, also imposes constraints on the ``compactness'' and ``smoothness'' of the gradient approximation. The only kernel we need to consider is the one that generates our target shift-invariant space, i.e. the space used to recover the smoothed indicator function. This type of variational reconstruction can be seen as an approximation to radial basis approaches~\cite{variational}, and is well-suited to our Poisson formulation in shift-invariant spaces.

Before presenting our approach (\SC{sec:pipeline}), we review the necessary background behind shift-invariant spaces and its connection to irregular sampling.
%\ednote{UA: Provided additional motivation for the variational framework, and added a gluing paragraph to imrpove the flow.}

\subsection{Sampling Lattices} \label{sec:smpl_review}
In the univariate case, there is only one way to uniformly sample a signal; take equally spaced samples along the independent axis. However, when sampling multivariate signals, the situation is not as straightforward. A common approach is to inherit the ideas from the univariate case, and sample the function at regular intervals in each axis (known as a Cartesian sampling), while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling). If $\mathbf{L}$ is a unimodular matrix, the set $\{\mathbf{L}\cdot\mathbf{n} : \mathbf{n} \in \intn^3 \}$ (linear combinations of the vectors of $\mathbb{L}$ with integer coefficients), represents all possible sampling lattices. $\mathbf{L}$ is often called the \emph{generating matrix} for a lattice. To control the sampling rate of a function, a uniform scaling parameter $h$ is introduced. Typically, for the problem of surface reconstruction, our input data are not uniformly distributed in space (or even about the surface of the model). However, the concept of a sampling lattice is fundamental in forming the definition of our target approximation spaces (\SC{sec:sis_review}).

The Cartesian lattice is given by the generating matrix $\mathbf{L}_C:=\mathbf{I}_3$, where $\mathbf{I}_3$ is the $3 \times 3$ identity matrix. There are many factors that contribute to the ubiquity of the Cartesian lattice in practice. Possibly one of its most attractive features is its separability. Owing to this, the implementation of generating functions that span function spaces on the Cartesian lattice may be realized by a tensor product extension of existing univariate techniques. Filtering techniques are also easy to implement, as the Fast Fourier Transform is also separable, and may be applied independently to each axis of the data. However, in terms of sampling efficiency, the BCC lattice is the optimal lattice in $\realn^3$, while the Cartesian is sub-optimal.

The Body-Centered Cubic (BCC) lattice is generated by the integer matrix  {\footnotesize
\begin{equation*} 
	\mathbf{L}_B := 
	\begin{bmatrix}
		-1 & 1 & 1 \\ 
		1 & -1 & 1 \\ 
		1 & 1 & -1 
	\end{bmatrix}.
\end{equation*}}
However, the BCC lattice is non-separable, and requires special care in data retrieval and indexing. \FG{fig:lattices} shows these lattices and their Voronoi regions, including the dual of the BCC lattice, the FCC lattice (the Cartesian lattice is dual to itself.)

\subsection{Box Splines}
\label{sec:box_review}
Box splines are compact piece-wise polynomial functions $ M_\mathbf{\Xii} : \realn^s \to \realn.$ The matrix $\mathbf{\Xii}$ denotes a collection of direction vectors, $\mathbf{\Xii} := \left[ \xi_1 \ \xi_2 \hdots \xi_n\right].$ When $n=s$, the function $M_\mathbf{\Xii}(\vx)$ is defined to be $\frac{1}{det|\mathbf{\Xii}|}$ inside the polytope formed by the Minkowski sum of the direction vectors of $\mathbf{\Xii}$, and zero otherwise (that is, $\frac{1}{det|\mathbf{\Xii}|}$ when $\vx \in \{ \mathbf{\xi}_1 t_1 + \hdots + \mathbf{\xi}_s t_s  : t_i\in [0,1) \})$. When $n > s$, the box spline is recursively defined as {\small 
\begin{equation} \label{eq:box_def}
	M_{\mathbf{\Xii}}(\vx) := \int_0^1{\!M_{\mathbf{\Xii/\xi}_n}(\vx - t\mathbf{\xi}_n)} \mathrm{d}t,
\end{equation}}
where $\!M_{\mathbf{\Xii/\xi}_n}$ is the matrix obtained by removing the column vector $\xi_n$ from $\mathbf{\Xii}$. Box splines are a natural fit for our purposes, and are chosen to span our function spaces. One motivating factor that encourages the use of box splines on the BCC lattice over the Cartesian lattice is that the support of the box splines on the BCC lattice contains less lattice sites as opposed to their Cartesian counterparts. At the same time, they maintain the same order of accuracy and smoothness. This implies that one should expect roughly the same quality reconstruction, with less memory accesses per reconstructed value.

The evaluation of a box spline, in general, can be achieved by evaluating a simple recursive expression \cite{boorboxsplines}. However, for many purposes, this form of evaluation is too slow. There has been a line of research \cite{firstbox} aimed towards obtaining fast piecewise polynomial representations of the box splines on the BCC lattice, and showing their advantage in speed and accuracy over splines on the Cartesian lattice when the data to be interpolated are sufficiently smooth.

\begin{figure}
  \centering
  \mbox{} \hfill
	\includegraphics[width=\linewidth]{figures/boxspline/2dex}
  \caption{\label{fig:box2d}%
  An example of box splines in 2D. On the left is the box spline comprised of the direction vectors $\mathbf{\xi}_1, \mathbf{\xi}_2$, (the case n=s) which is the indicator function of the Minkowski sum of the vectors. The box spline on the right, includes a third vector $\mathbf{\xi}_3$, which can be thought of as ``smearing'' the first spline along the direction $\mathbf{\xi}_3$.
  }
\end{figure}

\subsubsection{Cartesian Lattice}
Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial. It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions. Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ I_3  \ I_3 \ I_3  \ I_3 \right]}$. A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$. We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$.

\subsubsection{BCC Lattice}
On the BCC lattice, a choice of {\footnotesize
\begin{equation*}
	\mathbf{\Xii_{B}} := 
	\begin{bmatrix} 
		-1 & 1 & 1 & -1 \\
		1 & -1 & 1 & -1 \\
		1 & 1 & -1 & -1 
	\end{bmatrix}
\end{equation*}}
generates a piecewise linear polynomial function \cite{practicalbox}. The support of this box spline is a rhombic dodecahedron, which incidentally contains the set of first nearest neighbors to the Voronoi region of the lattice at the origin, and is a natural fit for the lattice. The quintic box spline is given by the matrix $\mathbf{\Xii_{B2}} := \left[\mathbf{\Xii_{B}} \ \mathbf{\Xii_{B}}\right]$, or may also be seen as the convolution of the linear box spline with itself.  However, there exist both an efficient piecewise polynomial representation \cite{practicalbox}, and an efficient implementation \cite{fastbox} of these piecewise quintic polynomial functions.

\subsubsection{Shifted Basis Functions}
We also consider shifted box splines $M_{\mathbf{\Xii}}^{\xi_i}(\vx) := M_{\mathbf{\Xii}}(\vx - \frac{1}{2}\mathbf{\xi}_i)$, where $\mathbf{\xi}_i$ is any direction vector in $\mathbf{\Xii}$. In the univariate case with linear B-splines, it has been shown that introducing a shift can offer an improvement when representing scalar data \cite{linearrev}. More generally and relevant to our purposes, they have also been shown to reduce error when approximating the gradient of scalar fields \cite{gradrev}.

\subsection{Shift Invariant Spaces} \label{sec:sis_review}
As our target reconstruction spaces, we consider the shift-invariant spaces defined by {\small 
\begin{equation*}
	\fspce{\varphi}{h\mathbf{L}} := \left\{ g(\vx) := \displaystyle\sum_{\mathbf{m} \in \intn^3} c[\mathbf{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
\end{equation*}}
where $\varphi$ is the generating function for the space, $h$ is a scaling parameter that controls the sampling rate or granularity, and $\mathbf{L}$ is the generating matrix for a given sampling lattice. Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\mathbf{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.

If the generating function that spans the space satisfies the \emph{Strang-Fix} conditions of order $k$, and $f$ belongs to the Sobolev space of at least order $k$, then it can be shown that the minimum approximation error (in the least-squares sense) decays asymptotically as $O(h^k)$, and the space is said to have approximation order $k$. We often only have access to $f$ through a discrete amount of samples, $\mathbf{f} := \left[ f_1 \ f_2 \ \hdots \ f_M \right]^T$ located at sample points $S := \{\vx_1, \vx_2 \hdots \vx_M \}$ respectively. When this is the case, the minimum-error approximation is unattainable. However, interpolative and quasi-interpolative methods \cite{quasibcc,interprev}, which can be seen as oblique projections onto $\fspce{\varphi}{h\mathbf{L}}$, maintain the same order of accuracy.

For sufficiently smooth functions $f$ that are uniformly sampled and properly prefiltered, the trilinear and linear reconstruction filters (Cartesian and BCC respectively) assure second order convergence, while the tricubic and Quintic assure fourth order. Another nicety of these spaces is that data processing techniques --- derivative approximation for example --- can often be represented by a convolution of the coefficient vector with either an \emph{Infinite Impulse Response} (IIR) or \emph{Finite Impulse Response} (FIR) filter.

Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice. We denote the set of such points as $\{\mathbf{s}_1,\mathbf{s}_2,\ \hdots  \ \mathbf{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\mathbf{s}_k)$; from this perspective, our function space is now {\small 
\begin{equation}
	\left\{ \displaystyle\sum_{k=0}^N c_k \varphi_k(\vx) \right\} \subset \fspce{\varphi}{h\mathbf{L}}.
\end{equation}}
Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $\Phii_{i,j} := \varphi_j(\vx_i)$. Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites, and we must consider alternative schemes for finding $\mathbf{c}.$

\subsection{Irregular Sampling}
\label{sec:vari_review}
%When reconstructing functions whose data are sampled regularly on a lattice, finding an oblique projection of the original function in the target function space is relatively straight-forward. However, except on very rare occasions, samples placed over the surface of a model do not coincide with lattice sites. A solution to this problem is to ``re-sample'' the input point set onto said lattices sites.
In the work by Kazdhan et al. \cite{fftk} the range data are splatted via a linear filter onto a regular Cartesian grid. This tends to over-smooth the resulting reconstruction, as it allows the surface to deviate from the original sample locations. Ideally, we would like to find a function that not only interpolates the input data, but provides the representation with the smallest possible ``shell'' about the initial point set (i.e., the fewest non zero coefficients) while still interpolating the data and eliciting a unique solution.

Thus, we recast the problem of finding a representation of $g$ within our function space as an optimization problem. There are similar works that impose variational constraints on random point samples for images \cite{variational}, as well as multi-resolution techniques for volumetric data \cite{onvari} and an extension to box spline spaces \cite{xu2012rec}. In the same vein, we seek a function $g \in \fspce{\varphi}{h\mathbf{L}}$ that attempts to interpolate the input data, and minimize a functional $E$. Specifically, we seek a $g$ that minimizes {\small 
\begin{equation} \label{eq:minexp}
 	\sump_{i=1}^{M} (g(\vx_i) -  f_i)^2 + E(g).
\end{equation}}
It is important to introduce a bit of notation before proceeding, $\dv{\mathbf{v}} f := \mathbf{v} \cdot \grad f$ defines the directional derivative of $f$ in the direction $\mathbf{v}$. The Beppo-Levi inner product of order $n$ is defined as $\blip{n}{f}{g}:= \sum_{|\mathbf{p}|=n}({n!}/{\mathbf{p}!}) \innerp{\mathbf{D^p}f}{\mathbf{D^p}g}$, where $\mathbf{p}$ is an integer vector such that $\left| \mathbf{p}\right| := p_1 + p_2 + p_3 $. We also use the short hand $\mathbf{D^p}f := \partial^{\left| \mathbf{p}\right|}f/({\partial^{p_1}x_1}{\partial^{p_2}x_2}{\partial^{p_3}x_3}).$ The second order Beppo-Levi norm of $f$ is defined as $\bln{2}{f}^2:=\blip{2}{f}{f}$.

The second order Beppo-Levi norm can be thought to measure the ``smoothness'' of a function. However, constraining the smoothness of our approximation alone is not sufficient to elicit the desired solution in our case. We propose that the smoothed normal field should also minimize the inner product of the function with itself. This has the physical interpretation of forcing the solution to be close to zero everywhere except near the input points. Our proposed cost functional is then $E(g) := \lambda_1 \left|\left|{g}\right|\right| + \lambda_2 \bln{2}{g}.$ Here, $\lambda_1$ controls the amount to which the function is penalized for large coefficient values. When combined with the interpolation constraint, this imposes the behavior of forcing the function to be zero away from the surface. The parameter $\lambda_2$ controls the smoothness of the resulting normal field.
%\begin{equation} \label{eq:functional}
%	E(g) := \lambda_1 \left|\left|{g}\right|\right| + \lambda_2 \bln{2}{g}.
%\end{equation}

Finding $g$ that minimizes equation \EQ{eq:minexp} involves rewriting the minimization problem in terms of $\mathbf{c}$ \cite{xu2012rec}. Following some straightforward algebraic manipulations (see \cite{xu2012rec} for details), the coefficient vector can be obtained by taking $\mathbf{c} = ( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S})^{-1}\mathbf{\Phii}^T\mathbf{f}$, where $G_{i,j}:=\innerp{\varphi_i}{\varphi_j}$ and $S_{i,j}:=\blip{2}{\varphi_i}{\varphi_j}$. Since $\varphi$ is known in closed form, the entries of both $\mathbf{G}$ and $\mathbf{S}$ can be evaluated analytically. The above vector equation can be efficiently solved using the Conjugate Gradient method.
%\begin{equation}
%	\mathbf{c} = \left( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S}\right)^{-1}\mathbf{\Phii}^T\mathbf{f},
%\label{eq:variationalSolution}
%\end{equation}

### 2015-02-10 introduction.tex
Adding updated (slightly) bib, adding updates to intro and related work.

@@
 \begin{itemize}
-\item[$\bullet$] We cast the Poisson surface reconstruction problem into the framework of shift-invariant spaces.
+\item[$\bullet$] We reformulate the Poisson surface reconstruction approach using general shift-invariant spaces as the target approximation space
 \item[$\bullet$] Specifically, we investigate the reconstruction of surfaces in both a sub-optimal (Cartesian) and an optimal (BCC)
-  box-spline function space.
-\item[$\bullet$] We present a variational scheme that not only considers the usual centered generating kernels, but allows for the
-  possibility of recovering each component of the gradient field in a space spanned by a shifted kernel. On the Cartesian
-  lattice, these components are orthogonal whereas on the BCC lattice,  the components are non-orthogonal and correspond to the directions associated with the underlying box-spline matrix.
-\item[$\bullet$] We present an extension of the error kernel of Blu and Unser to general linear operators, and show how to design filters that respect the approximation order of the approximation space.
+  box-spline function space
+\item[$\bullet$] We present a new variational resampling scheme that resamples the original scattered oriented points' normals onto any regular lattice.
+This resampling scheme depends on the generating kernel, but is general enough to be extended to shifted generating kernels as this has been shown to improve gradient estimation in shift invariant spaces.
+\item[$\bullet$] We present an extension of the error kernel of Blu and Unser to general linear operators and show how to design filters that respect the full approximation order of the target approximation space.
 \item[$\bullet$] While our focus is on comparing the surface reconstruction algorithm on both the CC and BCC lattices, we also provide qualitative and quantitative comparisons between the presented technique (on both the Cartesian and BCC lattices) and similar methods.

### 2015-02-10 relatedwork.tex
Adding updated (slightly) bib, adding updates to intro and related work.

@@
 \section{Related Work}
-.
-Surface reconstruction is an active area of research in computer graphics.
-It is beyond the scope of this work to touch on all the relevant research surrounding the subject.
-Thus, we only very briefly review some relevant contributions.
-Those seeking a more in-depth review may look to a recent survey of the subject \cite{sve05ss}, we focus mainly on some of the more related recent developments.
+Surface reconstruction is still a very active area of research in computer 
+graphics and it's beyond the scope of this work to touch on all the material 
+related to the subject. We therefore very briefly review some relevant contributions -- 
+those seeking a more in-depth review may look to a recent survey of the field 
+\cite{reconstar_eg14}. We focus mainly on some of the more related and recent 
+developments.
 
-Surface reconstruction algorithms generally fall under two categories:
-\emph{implicit} algorithms and \emph{explicit} algorithms. The common
-theme of implicit algorithms is the desire to find an implicit
-function $f : \realn^3 \mapsto \realn $, for which the iso-surface
-defined by $f(\mathbf{x})=s$ (for some iso-value $s \in \realn$)
-represents an approximation to the original surface. Explicit
-algorithms rely on combinatorial techniques, inferring meshes through
-a set predefined logic or rules.
+Many surface reconstruction algorithms are so-called 
+``\emph{implicit}'' reconstruction algorithms. They attempt to 
+reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose 
+level-set, $f(\mathbf{x})=s$ (for some iso-value $s \in \realn$), represents an
+approximation to the original surface. Other non-implicit techniques
+generally infer meshes through some other combinatorial means, 
+or a set predefined logic or rules.
 
-In terms of explicit algorithms, there exist many Delaunay style
-algorithms in which a triangulation is constructed using only a subset
-of the original point-set \cite{delaunay}. The Power Crust
-\cite{powercrust} and Cocone \cite{cocone} algorithms are two
-well-known techniques that fall under this category. These techniques
-often aim to interpolate the input point set, thus in the presence of
-noise, tend to over-fit the surface. When the input data are noisy,
-implicit approaches often perform better, as they inherently attempt
-to fit locally smooth basis functions to the data, averaging out any
-noise. Reconstructing either a distance function or an indicator
-function is common to these approaches.
+For example, there exist many Delaunay style algorithms in which a 
+triangulation is constructed using a subset of the original point-set 
+\cite{delaunay}. The Power Crust \cite{powercrust} and Cocone \cite{cocone} 
+algorithms are two other well-known techniques that do not construct 
+implicit functional representations. These techniques
+often aim to exactly interpolate the input point set, and in the presence of
+noise tend to over-fit the surface. When the input data are noisy
+implicit approaches often perform better than non-implicit algorithms, 
+as implicit algorithms inherently attempt to fit locally smooth basis 
+functions to the data, averaging out any noise. Reconstructing either 
+a distance function or an indicator function is common to these 
+approaches.
 
-One of the most well known implicit algorithms is the %Graph Cut \tm{this is not graph cuts!!}
-algorithm of by Hoppe et al.~\cite{hoppecut}. In this work a set of
+One of the most well known implicit algorithms is the algorithm of 
+by Hoppe et al.~\cite{hoppecut}. In this work a set of
 tangent planes is constructed to create an approximation to a
@@
 function, its gradient, and its Hessian. These constraints are
-tantamount to requiring that the reconstructed function be an
+equvalent to requiring that the reconstructed function be an
 approximation to the distance field of the original model. Other
@@
 Recently, there has also been research that incorporates point normals
-into the radial basis reconstruction framework \cite{hermite}.
+into the radial basis reconstruction framework \cite{hermite}. \ednote{Add 
+that paper from torsten here}
 
-Another approach is to find an approximate indicator function of the
-original model. A well known technique \cite{fftk} transforms the
-smoothed gradient to the Fourier domain, inverts it, then reconstructs
-it in the spatial domain. This approach often deals well with
-incomplete, missing or otherwise noisy data, with the guarantee of
+Another approach is to find an indicator function that approximates the
+``inside-outside'' function of original model. An early technique \cite{fftk} 
+transforms the smoothed gradient to the Fourier domain, applies an appropriate 
+operator, then reconstructs it in the spatial domain. This approach often deals well with
+incomplete, missing, or otherwise noisy data and has the guarantee of
 creating a water tight surface. However, it involves reconstructing
@@
 \cite{Kazhdan06,screenedk}. Moreover, they seek to rectify the memory
-limitations of said work, while still maintaining the benefits it
-provides. However, current techniques based on this idea have been
-shown to over-smooth the initial point-set, and thus the resulting
-surface. \cite{reconbench}.
+limitations of that work, while still maintaining its benefits. However, 
+current techniques based on this idea have been shown to over-smooth 
+the initial point-set, and therefore the resulting surface. \cite{reconbench}.
 
@@
 field from the oriented point-set. Radial basis functions (RBFs) are
-generally used in the context of the reconstruction of scattered data. 
-However, RBF techniques are often computationally
+generally used in the context of the reconstruction of scattered data, 
+however, RBF techniques are often computationally
 expensive, requiring the solution of large unstable systems of
@@
 problem is to ``\emph{re-sample}'' the input data onto a regular
-shift-invariant space . This allows one to use efficient compact
+shift-invariant space. This allows one to use efficient compact
 reconstruction kernels and data processing techniques
@@
 Having obtained a high-quality lattice-based approximation of the
-gradient field, we invoke the theory behind shift-invariant spaces,
+gradient field, we invoke the theory behind shift-invariant spaces
 and accurately estimate the divergence by applying derivative filters
 that are designed to harness the full approximation capabilities of
-the target space (\SC{sec:divergence}). In a similar manner, we then
-solve the Poisson equation by applying an \emph{inverse} Laplacian
-filter that is tailored to match the approximation order of the target
-space (\SC{sec:recoveringX}).
+the target space (\SC{sec:divergence}).
+
+Once, the smoothed gradient's divergence has been calculated, recovering the indicator
+function is a simple matter of taking the inverse of the Laplacian over domain 
+(i.e. solving the Poisson system). To do this, we take an approach that is also inspired 
+by filtering methodologies in signal processing. In particular, we're interested in 
+an approximate solution to Poisson?s equation that lies in a chosen shift-invariant 
+space. Our solution methodology is reminiscent of the finite 
+element method \cite{finite_el}. However, we do not impose any boundary 
+conditions on the generating kernels. Rather, we satisfy homogeneous 
+Dirichlet boundary conditions implicitly by requiring that the coefficient sequence be odd 
+(Section III). The solution is obtained by applying a digital filter to point samples. 
+We approach the problem from first principles and derive the tools necessary 
+to design solution filters for a chosen shift-invariant space (\SC{sec:recoveringX}).
+\ednote{I still need to fix-up section refs/refs here.}

### 2015-02-11 prelim.tex
Adding review and moving stuff.

--- 2015-02-05 review.tex
@@
 
+\subsection{Shift Invariant Spaces} \label{sec:sis_review}
+As our target reconstruction spaces, we consider the shift-invariant spaces defined by {\small 
+\begin{equation*}
+	\fspce{\varphi}{h\mathbf{L}} := \left\{ g(\vx) := \displaystyle\sum_{\mathbf{m} \in \intn^3} c[\mathbf{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
+\end{equation*}}
+where $\varphi$ is the generating function for the space, $h$ is a scaling parameter that controls the sampling rate or granularity, and $\mathbf{L}$ is the generating matrix for a given sampling lattice.
+Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\mathbf{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.
+
+If the generating function that spans the space satisfies the \emph{Strang-Fix} conditions of order $k$, and $f$ belongs to the Sobolev space of at least order $k$, then it can be shown that the minimum approximation error (in the least-squares sense) decays asymptotically as $O(h^k)$, and the space is said to have approximation order $k$.
+We often only have access to $f$ through a discrete amount of samples, $\mathbf{f} := \left[ f_1 \ f_2 \ \hdots \ f_M \right]^T$ located at sample points $S := \{\vx_1, \vx_2 \hdots \vx_M \}$ respectively.
+When this is the case, the minimum-error approximation is unattainable.
+However, interpolative and quasi-interpolative methods \cite{quasibcc,interprev}, which can be seen as oblique projections onto $\fspce{\varphi}{h\mathbf{L}}$, maintain the same order of accuracy.
+
+For sufficiently smooth functions $f$ that are uniformly sampled and properly prefiltered, the trilinear and linear reconstruction filters (Cartesian and BCC respectively) assure second order convergence, while the tricubic and Quintic assure fourth order.
+Another nicety of these spaces is that data processing techniques --- derivative approximation for example --- can often be represented by a convolution of the coefficient vector with either an \emph{Infinite Impulse Response} (IIR) or \emph{Finite Impulse Response} (FIR) filter.
+
+Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice.
+We denote the set of such points as $\{\mathbf{s}_1,\mathbf{s}_2,\ \hdots  \ \mathbf{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\mathbf{s}_k)$; from this perspective, our function space is now {\small
+\begin{equation}
+	\left\{ \displaystyle\sum_{k=0}^N c_k \varphi_k(\vx) \right\} \subset \fspce{\varphi}{h\mathbf{L}}.
+\end{equation}}
+Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $\Phii_{i,j} := \varphi_j(\vx_i)$.
+Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites, and we must consider alternative schemes for finding $\mathbf{c}.$
+
 \subsection{Box Splines}
@@
 \end{figure}
-
-\subsubsection{Cartesian Lattice}
-Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial.
-It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions.
-Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ I_3  \ I_3 \ I_3  \ I_3 \right]}$.
-A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$.
-We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$.
-
-\subsubsection{BCC Lattice}
-On the BCC lattice, a choice of {\footnotesize
-\begin{equation*}
-	\mathbf{\Xii_{B}} := 
-	\begin{bmatrix} 
-		-1 & 1 & 1 & -1 \\
-		1 & -1 & 1 & -1 \\
-		1 & 1 & -1 & -1 
-	\end{bmatrix}
-\end{equation*}}
-generates a piecewise linear polynomial function \cite{practicalbox}.
-The support of this box spline is a rhombic dodecahedron, which incidentally contains the set of first nearest neighbors to the Voronoi region of the lattice at the origin, and is a natural fit for the lattice.
-The quintic box spline is given by the matrix $\mathbf{\Xii_{B2}} := \left[\mathbf{\Xii_{B}} \ \mathbf{\Xii_{B}}\right]$, or may also be seen as the convolution of the linear box spline with itself.
-However, there exist both an efficient piecewise polynomial representation \cite{practicalbox}, and an efficient implementation \cite{fastbox} of these piecewise quintic polynomial functions.
-
-\subsubsection{Shifted Basis Functions}
-We also consider shifted box splines $M_{\mathbf{\Xii}}^{\xi_i}(\vx) := M_{\mathbf{\Xii}}(\vx - \frac{1}{2}\mathbf{\xi}_i)$, where $\mathbf{\xi}_i$ is any direction vector in $\mathbf{\Xii}$.
-In the univariate case with linear B-splines, it has been shown that introducing a shift can offer an improvement when representing scalar data \cite{linearrev}.
-More generally and relevant to our purposes, they have also been shown to reduce error when approximating the gradient of scalar fields \cite{gradrev}.
-
-\subsection{Shift Invariant Spaces} \label{sec:sis_review}
-As our target reconstruction spaces, we consider the shift-invariant spaces defined by {\small 
-\begin{equation*}
-	\fspce{\varphi}{h\mathbf{L}} := \left\{ g(\vx) := \displaystyle\sum_{\mathbf{m} \in \intn^3} c[\mathbf{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
-\end{equation*}}
-where $\varphi$ is the generating function for the space, $h$ is a scaling parameter that controls the sampling rate or granularity, and $\mathbf{L}$ is the generating matrix for a given sampling lattice.
-Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\mathbf{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.
-
-If the generating function that spans the space satisfies the \emph{Strang-Fix} conditions of order $k$, and $f$ belongs to the Sobolev space of at least order $k$, then it can be shown that the minimum approximation error (in the least-squares sense) decays asymptotically as $O(h^k)$, and the space is said to have approximation order $k$.
-We often only have access to $f$ through a discrete amount of samples, $\mathbf{f} := \left[ f_1 \ f_2 \ \hdots \ f_M \right]^T$ located at sample points $S := \{\vx_1, \vx_2 \hdots \vx_M \}$ respectively.
-When this is the case, the minimum-error approximation is unattainable.
-However, interpolative and quasi-interpolative methods \cite{quasibcc,interprev}, which can be seen as oblique projections onto $\fspce{\varphi}{h\mathbf{L}}$, maintain the same order of accuracy.
-
-For sufficiently smooth functions $f$ that are uniformly sampled and properly prefiltered, the trilinear and linear reconstruction filters (Cartesian and BCC respectively) assure second order convergence, while the tricubic and Quintic assure fourth order.
-Another nicety of these spaces is that data processing techniques --- derivative approximation for example --- can often be represented by a convolution of the coefficient vector with either an \emph{Infinite Impulse Response} (IIR) or \emph{Finite Impulse Response} (FIR) filter.
-
-Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice.
-We denote the set of such points as $\{\mathbf{s}_1,\mathbf{s}_2,\ \hdots  \ \mathbf{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\mathbf{s}_k)$; from this perspective, our function space is now {\small
-\begin{equation}
-	\left\{ \displaystyle\sum_{k=0}^N c_k \varphi_k(\vx) \right\} \subset \fspce{\varphi}{h\mathbf{L}}.
-\end{equation}}
-Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $\Phii_{i,j} := \varphi_j(\vx_i)$.
-Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites, and we must consider alternative schemes for finding $\mathbf{c}.$
 

### 2015-02-11 results.tex
Adding review and moving stuff.

--- 2015-02-05 review.tex
@@
-\section{Preliminaries}\label{sec:pois_review}
-\subsection{Poisson Surface Reconstruction}
-We denote the indicator function of a model $M$ as $$ \chi_M(\mathbf{x}) :=
-\begin{cases}
-1, & \text{if }\mathbf{x}\text{ is in the interior of the model } M \\
-\frac{1}{2}, & \text{if } \mathbf{x}\text{ is on the model's surface}\\
-0, & \text{if }\mathbf{x}\text{ is exterior to } M
-\end{cases}. $$
-Integral to formulating surface reconstruction as a Poisson problem, is the observation that if one obtains some function $\vec{V}(\mathbf{x})\approx{\nabla}\chi_M$ that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small
-\begin{equation} \label{eq:poisson}
-	\lapl{\inda} = {\grad} \cdot \vec{V}.
-\end{equation}}
-We define the set of input surface points to be $P:=\{(\mathbf{p}_1,\mathbf{n}_1), (\mathbf{p}_2,\mathbf{n}_2) \hdots (\mathbf{p}_M,\mathbf{n}_M) : (\mathbf{p}_i,\mathbf{n}_i) \in
-\realn^3 \times \realn^3 \}$ where $\mathbf{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively.
-Orientation can be succinctly represented with only two values, however, it is convenient to keep it denoted as the normal at a point.
-This is because the length of the normal can be used to encode the sampling density of the point-set at a point.
-For the following discussion, we also need to introduce the notation $\patch_{\mathbf{s}}$, which denotes a patch of the surface model about the sample location $\mathbf{s}$.
-
-Inspired by the approach of Kazhdan et al.~\cite{Kazhdan06} the approximation $\vec{V}(\vx)$ is defined to be  {\small 
-\begin{eqnarray}
-	\vec{V}(\vx) & := & \sum_{(\mathbf{s},\mathbf{n}) \in P}\left|\patch_s\right|F(\vx-\mathbf{s})\cdot\vn \label{eq:vdef} \\
-	 & \approx & \sum_{(\mathbf{s},\mathbf{n}) \in P} \int_{\patch_s}{F(\mathbf{x} - \mathbf{p}) \nabla \chi (\mathbf{p})} \mathrm{d} \mathbf{p}. \notag  
-\end{eqnarray}}
-Thus, $\vec{V}(\vx)$ approximates the gradient of the indicator smoothed by some filter $F$, broken up over surface patches of the model.
-We assume the point sampling to be uniform, thus the area of each patch $\left|\patch_s\right|$ should be a constant, and our resulting approximation will be scaled by an unknown factor.
-We return to this in \SC{sec:levelset}.
-The choice of $F$ places computational constraints on the resulting algorithm.
-
-$F$ is often explicitly chosen to be a compactly supported function.
-This simplifies and reduces the computational cost of the method when used in conjunction with an oct-tree based representation of $\vec{V}(\vx)$ \cite{Kazhdan06}.
-However, there is a disadvantage in that $F$ may over smooth data in areas of high curvature \cite{reconbench}, much in the same way that a representation of a sampled signal may fail to take advantage of the full approximation power of the function space in which it is represented if it is not properly prefiltered.
-Theoretically, one could reconstruct the surface at higher resolutions, allowing the basis functions to become more ``fine'', but increasing the total amount of memory used.
-However, this is not realistic in praxis.
-Another approach is to impose a type of ``interpolation'' constraint on the original data \cite{screenedk}.
-
-Ideally, the filter $F$ should correspond to some globally supported RBF.
-However, as the support of $F$ grows, so does the cost of evaluating it at lattice sites.
-Moreover, the added benefit of a globally supported RBF is partially lost as the subsequent steps are entirely lattice-based and do not take the RBF into consideration.
-Our approach circumvents the choice of $F$ entirely by posing the gradient approximation problem as a variational problem that, in addition to imposing the interpolation constraint, also imposes constraints on the ``compactness'' and ``smoothness'' of the gradient approximation.
-The only kernel we need to consider is the one that generates our target shift-invariant space, i.e.
-the space used to recover the smoothed indicator function.
-This type of variational reconstruction can be seen as an approximation to radial basis approaches~\cite{variational}, and is well-suited to our Poisson formulation in shift-invariant spaces.
-
-Before presenting our approach (\SC{sec:pipeline}), we review the necessary background behind shift-invariant spaces and its connection to irregular sampling.
-%\ednote{UA: Provided additional motivation for the variational framework, and added a gluing paragraph to imrpove the flow.}
-
-\subsection{Sampling Lattices} \label{sec:smpl_review}
-In the univariate case, there is only one way to uniformly sample a signal; take equally spaced samples along the independent axis.
-However, when sampling multivariate signals, the situation is not as straightforward.
-A common approach is to inherit the ideas from the univariate case, and sample the function at regular intervals in each axis (known as a Cartesian sampling), while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling).
-If $\mathbf{L}$ is a unimodular matrix, the set $\{\mathbf{L}\cdot\mathbf{n} : \mathbf{n} \in \intn^3 \}$ (linear combinations of the vectors of $\mathbb{L}$ with integer coefficients), represents all possible sampling lattices.
-$\mathbf{L}$ is often called the \emph{generating matrix} for a lattice.
-To control the sampling rate of a function, a uniform scaling parameter $h$ is introduced.
-Typically, for the problem of surface reconstruction, our input data are not uniformly distributed in space (or even about the surface of the model).
-However, the concept of a sampling lattice is fundamental in forming the definition of our target approximation spaces (\SC{sec:sis_review}).
-
-The Cartesian lattice is given by the generating matrix $\mathbf{L}_C:=\mathbf{I}_3$, where $\mathbf{I}_3$ is the $3 \times 3$ identity matrix.
-There are many factors that contribute to the ubiquity of the Cartesian lattice in practice.
-Possibly one of its most attractive features is its separability.
-Owing to this, the implementation of generating functions that span function spaces on the Cartesian lattice may be realized by a tensor product extension of existing univariate techniques.
-Filtering techniques are also easy to implement, as the Fast Fourier Transform is also separable, and may be applied independently to each axis of the data.
-However, in terms of sampling efficiency, the BCC lattice is the optimal lattice in $\realn^3$, while the Cartesian is sub-optimal.
-
-The Body-Centered Cubic (BCC) lattice is generated by the integer matrix  {\footnotesize
-\begin{equation*} 
-	\mathbf{L}_B := 
-	\begin{bmatrix}
-		-1 & 1 & 1 \\ 
-		1 & -1 & 1 \\ 
-		1 & 1 & -1 
-	\end{bmatrix}.
-\end{equation*}}
-However, the BCC lattice is non-separable, and requires special care in data retrieval and indexing.
-\FG{fig:lattices} shows these lattices and their Voronoi regions, including the dual of the BCC lattice, the FCC lattice (the Cartesian lattice is dual to itself.)
-
-\subsection{Box Splines}
-\label{sec:box_review}
-Box splines are compact piece-wise polynomial functions $ M_\mathbf{\Xii} : \realn^s \to \realn.$ The matrix $\mathbf{\Xii}$ denotes a collection of direction vectors, $\mathbf{\Xii} := \left[ \xi_1 \ \xi_2 \hdots \xi_n\right].$ When $n=s$, the function $M_\mathbf{\Xii}(\vx)$ is defined to be $\frac{1}{det|\mathbf{\Xii}|}$ inside the polytope formed by the Minkowski sum of the direction vectors of $\mathbf{\Xii}$, and zero otherwise (that is, $\frac{1}{det|\mathbf{\Xii}|}$ when $\vx \in \{ \mathbf{\xi}_1 t_1 + \hdots + \mathbf{\xi}_s t_s  : t_i\in [0,1) \})$.
-When $n > s$, the box spline is recursively defined as {\small
-\begin{equation} \label{eq:box_def}
-	M_{\mathbf{\Xii}}(\vx) := \int_0^1{\!M_{\mathbf{\Xii/\xi}_n}(\vx - t\mathbf{\xi}_n)} \mathrm{d}t,
-\end{equation}}
-where $\!M_{\mathbf{\Xii/\xi}_n}$ is the matrix obtained by removing the column vector $\xi_n$ from $\mathbf{\Xii}$.
-Box splines are a natural fit for our purposes, and are chosen to span our function spaces.
-One motivating factor that encourages the use of box splines on the BCC lattice over the Cartesian lattice is that the support of the box splines on the BCC lattice contains less lattice sites as opposed to their Cartesian counterparts.
-At the same time, they maintain the same order of accuracy and smoothness.
-This implies that one should expect roughly the same quality reconstruction, with less memory accesses per reconstructed value.
-
-The evaluation of a box spline, in general, can be achieved by evaluating a simple recursive expression \cite{boorboxsplines}.
-However, for many purposes, this form of evaluation is too slow.
-There has been a line of research \cite{firstbox} aimed towards obtaining fast piecewise polynomial representations of the box splines on the BCC lattice, and showing their advantage in speed and accuracy over splines on the Cartesian lattice when the data to be interpolated are sufficiently smooth.
-
-\begin{figure}
-  \centering
-  \mbox{} \hfill
-	\includegraphics[width=\linewidth]{figures/boxspline/2dex}
-  \caption{\label{fig:box2d}%
-  An example of box splines in 2D.
-On the left is the box spline comprised of the direction vectors $\mathbf{\xi}_1, \mathbf{\xi}_2$, (the case n=s) which is the indicator function of the Minkowski sum of the vectors.
-The box spline on the right, includes a third vector $\mathbf{\xi}_3$, which can be thought of as ``smearing'' the first spline along the direction $\mathbf{\xi}_3$.
-  }
-\end{figure}
+\subsection{Experiments and Results}
 
@@
 More generally and relevant to our purposes, they have also been shown to reduce error when approximating the gradient of scalar fields \cite{gradrev}.
-
-\subsection{Shift Invariant Spaces} \label{sec:sis_review}
-As our target reconstruction spaces, we consider the shift-invariant spaces defined by {\small 
-\begin{equation*}
-	\fspce{\varphi}{h\mathbf{L}} := \left\{ g(\vx) := \displaystyle\sum_{\mathbf{m} \in \intn^3} c[\mathbf{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
-\end{equation*}}
-where $\varphi$ is the generating function for the space, $h$ is a scaling parameter that controls the sampling rate or granularity, and $\mathbf{L}$ is the generating matrix for a given sampling lattice.
-Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\mathbf{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.
-
-If the generating function that spans the space satisfies the \emph{Strang-Fix} conditions of order $k$, and $f$ belongs to the Sobolev space of at least order $k$, then it can be shown that the minimum approximation error (in the least-squares sense) decays asymptotically as $O(h^k)$, and the space is said to have approximation order $k$.
-We often only have access to $f$ through a discrete amount of samples, $\mathbf{f} := \left[ f_1 \ f_2 \ \hdots \ f_M \right]^T$ located at sample points $S := \{\vx_1, \vx_2 \hdots \vx_M \}$ respectively.
-When this is the case, the minimum-error approximation is unattainable.
-However, interpolative and quasi-interpolative methods \cite{quasibcc,interprev}, which can be seen as oblique projections onto $\fspce{\varphi}{h\mathbf{L}}$, maintain the same order of accuracy.
-
-For sufficiently smooth functions $f$ that are uniformly sampled and properly prefiltered, the trilinear and linear reconstruction filters (Cartesian and BCC respectively) assure second order convergence, while the tricubic and Quintic assure fourth order.
-Another nicety of these spaces is that data processing techniques --- derivative approximation for example --- can often be represented by a convolution of the coefficient vector with either an \emph{Infinite Impulse Response} (IIR) or \emph{Finite Impulse Response} (FIR) filter.
-
-Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice.
-We denote the set of such points as $\{\mathbf{s}_1,\mathbf{s}_2,\ \hdots  \ \mathbf{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\mathbf{s}_k)$; from this perspective, our function space is now {\small
-\begin{equation}
-	\left\{ \displaystyle\sum_{k=0}^N c_k \varphi_k(\vx) \right\} \subset \fspce{\varphi}{h\mathbf{L}}.
-\end{equation}}
-Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $\Phii_{i,j} := \varphi_j(\vx_i)$.
-Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites, and we must consider alternative schemes for finding $\mathbf{c}.$
-
-\subsection{Irregular Sampling}
-\label{sec:vari_review}
-%When reconstructing functions whose data are sampled regularly on a lattice, finding an oblique projection of the original function in the target function space is relatively straight-forward.
-However, except on very rare occasions, samples placed over the surface of a model do not coincide with lattice sites.
-A solution to this problem is to ``re-sample'' the input point set onto said lattices sites.
-In the work by Kazdhan et al.
-\cite{fftk} the range data are splatted via a linear filter onto a regular Cartesian grid.
-This tends to over-smooth the resulting reconstruction, as it allows the surface to deviate from the original sample locations.
-Ideally, we would like to find a function that not only interpolates the input data, but provides the representation with the smallest possible ``shell'' about the initial point set (i.e., the fewest non zero coefficients) while still interpolating the data and eliciting a unique solution.
-
-Thus, we recast the problem of finding a representation of $g$ within our function space as an optimization problem.
-There are similar works that impose variational constraints on random point samples for images \cite{variational}, as well as multi-resolution techniques for volumetric data \cite{onvari} and an extension to box spline spaces \cite{xu2012rec}.
-In the same vein, we seek a function $g \in \fspce{\varphi}{h\mathbf{L}}$ that attempts to interpolate the input data, and minimize a functional $E$.
-Specifically, we seek a $g$ that minimizes {\small
-\begin{equation} \label{eq:minexp}
- 	\sump_{i=1}^{M} (g(\vx_i) -  f_i)^2 + E(g).
-\end{equation}}
-It is important to introduce a bit of notation before proceeding, $\dv{\mathbf{v}} f := \mathbf{v} \cdot \grad f$ defines the directional derivative of $f$ in the direction $\mathbf{v}$.
-The Beppo-Levi inner product of order $n$ is defined as $\blip{n}{f}{g}:= \sum_{|\mathbf{p}|=n}({n!}/{\mathbf{p}!}) \innerp{\mathbf{D^p}f}{\mathbf{D^p}g}$, where $\mathbf{p}$ is an integer vector such that $\left| \mathbf{p}\right| := p_1 + p_2 + p_3 $.
-We also use the short hand $\mathbf{D^p}f := \partial^{\left| \mathbf{p}\right|}f/({\partial^{p_1}x_1}{\partial^{p_2}x_2}{\partial^{p_3}x_3}).$ The second order Beppo-Levi norm of $f$ is defined as $\bln{2}{f}^2:=\blip{2}{f}{f}$.
-
-The second order Beppo-Levi norm can be thought to measure the ``smoothness'' of a function.
-However, constraining the smoothness of our approximation alone is not sufficient to elicit the desired solution in our case.
-We propose that the smoothed normal field should also minimize the inner product of the function with itself.
-This has the physical interpretation of forcing the solution to be close to zero everywhere except near the input points.
-Our proposed cost functional is then $E(g) := \lambda_1 \left|\left|{g}\right|\right| + \lambda_2 \bln{2}{g}.$ Here, $\lambda_1$ controls the amount to which the function is penalized for large coefficient values.
-When combined with the interpolation constraint, this imposes the behavior of forcing the function to be zero away from the surface.
-The parameter $\lambda_2$ controls the smoothness of the resulting normal field.
-%\begin{equation} \label{eq:functional}
-%	E(g) := \lambda_1 \left|\left|{g}\right|\right| + \lambda_2 \bln{2}{g}.
-%\end{equation}
-
-Finding $g$ that minimizes equation \EQ{eq:minexp} involves rewriting the minimization problem in terms of $\mathbf{c}$ \cite{xu2012rec}.
-Following some straightforward algebraic manipulations (see \cite{xu2012rec} for details), the coefficient vector can be obtained by taking $\mathbf{c} = ( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S})^{-1}\mathbf{\Phii}^T\mathbf{f}$, where $G_{i,j}:=\innerp{\varphi_i}{\varphi_j}$ and $S_{i,j}:=\blip{2}{\varphi_i}{\varphi_j}$.
-Since $\varphi$ is known in closed form, the entries of both $\mathbf{G}$ and $\mathbf{S}$ can be evaluated analytically.
-The above vector equation can be efficiently solved using the Conjugate Gradient method.
-%\begin{equation}
-%	\mathbf{c} = \left( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S}\right)^{-1}\mathbf{\Phii}^T\mathbf{f},
-%\label{eq:variationalSolution}
-%\end{equation}

### 2015-02-15 approach.tex
Added Floating surface recon

\section{Approach}
\label{sec:pipeline}
\begin{figure*} 
	\centering
	\input{images/pipeline.pdf_tex}
	\caption{A high level overview of our surface reconstruction pipeline in 2D. On the far left, a) shows the initial point-set. b) is the result of the smoothed variational reconstruction of the gradient of the indicator, the top image is the component in basis, the bottom is the y component. The approximate divergence of the smoothed indicator function is c), and d) is the resulting indicator function. \ednote{UA: Please fix this.}}
	\label{fig:pipeline}
\end{figure*}

A high level description of our approach is outlined in \FG{fig:pipeline}. From the oriented surface samples, we construct the approximation $\vec{V}(\vx)$ using our variational formulation. We then apply FIR filters to the coefficients of the approximation to construct a scalar field representing the approximate divergence of the smoothed normal field (\FG{fig:pipeline}c.) We then use an appropriate discretization of the inverse Laplacian operator to solve the Poisson equation \EQ{eq:poisson}, and obtain a smooth function that approximates the original indicator function (\FG{fig:pipeline}c). Our code will is also available for download

\subsection{Obtaining $\vec{V}(\vx)$} \label{sec:getting_vd}
\label{sec:obtainingV}
We define the vector field as $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1(\vx) \ \upsilon_2(\vx) \ \upsilon_3(\vx)\right]^T$ where $\mathbf{L := [b_1 \ b_2 \ b_3]}$ is a basis for $\realn^3$ that contains the principal lattice directions of the chosen lattice. Each $\upsilon_i$ is a scalar function representing the projection of the smoothed normal field onto each respective principal lattice direction $\mathbf{b}_i$. This may seem unintuitive at first, however, using a non-canonical basis to represent $\vec{V}$ will be convenient in two ways. Firstly, it will allow us to approximate the divergence of $\vec{V}$ by taking directional derivatives of $\vec{V}$ in the principal lattice directions. This is motivated by the fact that it is more natural to approximate derivatives in the principal lattice directions on non-Cartesian lattices. Secondly, it will allow us to construct divergence of the smoothed normal field from more than three principal lattice directions. We also allow each function $\upsilon_i$ to potentially be represented in different function spaces, i.e. {\small 
\begin{equation} 
	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_k^i \varphi_k^i(\vx) \in \fspce{\varphi^i}{h\mathbf{L}}.
\end{equation}}
The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$. We consider each component of $\vec{V}(\vx)$ separately, thus, it suffices to only look at one $\upsilon_i$. We simply find the $\upsilon_i$ that minimizes {\small 
\begin{equation} \label{eq:vari_eqn}
 	\sump_{\forall (\vx,\vn) \in P }^{M} (\upsilon_i(\vx) - (\mathbf{L}^{-1})_i \cdot \mathbf{n})^2 + E(\upsilon_i).
\end{equation} }
Where $(\mathbf{L}^{-1})_i$ is the $i^{th}$ column of $(\mathbf{L}^{-1}).$ As before, this provides us with a parametrized way of controlling the smoothness of the resulting approximation, without the need to explicitly choose a smoothing kernel.

%In what follows, $\mathbf{L}$ is chosen to be the canonical basis $\mathbf{I_3}$ for the Cartesian lattice, whereas for the BCC lattice, we choose $\mathbf{L = L}_B$.

\subsection{Divergence of $\vec{V}(\vx)$}
\label{sec:divergence}
A simple way to obtain the divergence of $\vec{V}(\vx)$ is to consider its analytical partial derivatives which, due to the linearity of the expression, requires one to only take the analytic partial derivatives of the underlying kernel functions. However, this reduces the smoothness of the solution \cite{zahgrad}. There is also no conclusive evidence that suggests the analytic derivative of the kernel provides a better approximation to true underlying derivative. With this in mind, we choose to take a discrete filtering approach and approximate the divergence of $\vec{V}$ with a set of discrete FIR filters. While these filters do not strictly facilitate the best approximation scheme for derivatives, they provide a good compromise between compactness versus accuracy, even more so when the reconstruction spaces are shifted \cite{gradrev}.

\subsubsection{Spaces Spanned by a Single Generating Function}
When each space is identical (when $\upsilon_i \in \fspce{\varphi}{L}$) the divergence can be found by taking directional derivatives of $\vec{V}$ along the vectors in $\mathbf{L}$ as follows: {\small 
\begin{eqnarray}\label{eq:div_dir}
	\grad \cdot \vec{V}(\vx) & = & \grad \cdot \mathbf{L} \left[\upsilon_1(\vx) \ \upsilon_2(\vx) \ \upsilon_3(\vx)\right]^T \notag \\
	 & = & \left[ \mathbf{(\grad \cdot b_1) \ (\grad \cdot b_2) \ (\grad \cdot b_3 ) }\right] \cdot \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3\right]^T \\
	 & = & \dv{\mathbf{b_1}}\upsilon_1 + \dv{\mathbf{b_2}}\upsilon_2 + \dv{\mathbf{b_3}}\upsilon_3. \notag
\end{eqnarray} }
This allows us to approximate the divergence of $\vec{V}$ by simply convolving the coefficient vector corresponding to $\upsilon_i$ with an appropriate 1D derivative filter $d[n]$, then sum the coefficients. The expression for the resulting coefficient vector of the divergence is then {\small
\begin{equation}
	\mathbf{f}:= \sum_{i=1}^3{ \mathbf{v}_i*\mathbf{d}_i}
\label{eq:divergenceViaFiltering}
\end{equation}}
where $\mathbf{d}_i$ is a directional derivative filter obtained by orienting the 1D filter $d$ 
along the direction $\mathbf{b}_i.$

\subsubsection{Shifted Reconstruction Spaces}
To reconstruct within a shifted space, the input point-set is shifted by $\frac{1}{2}\mathbf{b_i}$ then reconstructed within $\fspce{\varphi}{L}$. This is clearly equivalent to reconstructing in a shifted basis space, however, care must be taken to ensure that the data are brought back to a centered representation. Our choice of a shifted derivative filter $s[n]$ accounts for this and brings the resulting approximation back to the unshifted space. Both the shifted and unshifted filters we utilize are found in \TA{tab:filters} and are chosen so that they provide a fourth-order discretization of the 1D derivative operator~\cite{gradrev}.

\subsubsection{Four Direction Divergence on the BCC Lattice}
It is also possible to consider a basis $\mathbf{L}$ in which we choose more than three principal directions to reconstruct the divergence. Thus, we may choose $\mathbf{L} = \mathbf{\Xii_{B}} $ as the basis for our function. To accommodate for this, we redefine $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T$ Since this matrix is not square, it is not possible to take its inverse in \EQ{eq:vari_eqn}. Instead, the least norm inverse $\mathbf{L^T(LL}^T\mathbf{)}^{-1}$ is used. It is easy to see that, by the same reasoning as in equation \EQ{eq:div_dir}, $\grad \cdot \vec{V} = \dv{\mathbf{b_1}}\upsilon_1 + \dv{\mathbf{b_2}}\upsilon_2 + \dv{\mathbf{b_3}}\upsilon_3 + \dv{\mathbf{b_4}}\upsilon_4$. Thus, we may use the same idea as in the three direction case, approximating each direction separately, and summing the coefficients to obtain an approximation to the divergence (the shifted case is also similar.)
%\begin{equation}
%	\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T
%\end{equation}

### 2015-02-15 conclusion.tex
Added Floating surface recon

\subsection{Robustness}
When the input data contain noise, our method allows us to choose an appropriate smoothing parameter $\lambda_2$ to average out said error. However, our method fails to be as robust as the Screened Poisson algorithm when the data are non-uniform. We speculate that this is due to the fact that we employ no heuristics to account for the deviation from the assumption of uniformity (\FG{fig:r2}.)

\subsection{Complexity}
In terms of re-sampling speed, representation memory consumption, and reconstruction time, the BCC approach tends to outperform the Cartesian. However, when compared to similar methods whose function spaces are sparse, our method is limited. Specifically, our memory requirement grows as $O(n^3)$ where $n$ is the grid size, and the matrix solve is quite slow as $n$ is large. While the regularization matrices on the BCC lattice are more sparse, and tend to converge faster, their size is still prohibitive for big $n$. These limitations prevent us from going to the same resolutions that similar methods allow.

One possible remedy to this, is to construct our solution within a wavelet or multiresolution space defined over the BCC lattice. Since the function we wish to reconstruct only needs a detailed representation near the surface or the model, one can expect much better memory consumption. However, this is still an open problem, and needs further research. Another possibility, would be to break the initial point-set up into smaller sets, reconstruct the surface over those sets, then join the resulting meshes.

\subsection{Parameter Selection}
In our experiments, choosing $\lambda_2$ to be small reduced smoothing as expected. However, we observed that when $\lambda_2$ passed below a threshold, the surface began to show ringing or aliasing artifacts. This is somewhat to be expected, as choosing a very thin smoothing will cause the approximation \EQ{eq:vdef} to break down. Additionally, the choice of $\lambda_1$, the compactness constraint, didn't seem to effect the solution much, it's only effect was on the choice of the parameter $\lambda_2$. That is, when $\lambda_1$ was large, $\lambda_2$ had to be large to obtain similar smooth solutions.

The parameterized nature of our solution allows us to control the degree to which the initial data are smoothed. However, this also makes it difficult to conclusively compare methods. More investigation and exploration of the parameter space is required. Moreover, there also appears to be a point at which choosing $\lambda_2$ to be too small introduces aliasing artifacts.

\section{Conclusion}
The results regarding reconstruction methods are not surprising, they show that the Poisson methods in question are not using the full representation power of their approximation spaces they use. Further, when the we focus on solely on the method presented in this paper, we see an improvement in reconstruction quality. Reconstruction space can play a significant role in the fidelity of surface reconstruction. From the optimality argument, it is not surprising to see that function spaces defined over the BCC lattice tend to reconstruct more details at equivalent resolutions when compared to those defined over the Cartesian lattice. Furthermore, reconstructing within shifted spaces seems to better reconstruct higher frequency details.

The main hindrance for this method its cubic memory requirement, which prevents us from utilizing high density grids, and prevents the method from being used in practical settings verbatim. However, since no multiresolution techniques are currently available on non-Cartesian lattices in 3D, such topics are subject of future work. Additionally, a more complete analysis is required for parameter selection between the two lattices, and research into a faster (perhaps multiresolution) variational algorithm is needed.

### 2015-02-15 indicator.tex
Added Floating surface recon

\section{Recovering the Indicator}
\label{sec:recoveringX}
Once the divergence of the smoothed vector field has been computed, the remaining step is to find a function that satisfies equation \EQ{eq:poisson}. As with the computation of a function's derivative, we also seek a filtering solution for the inverse of the Laplacian. We desire a filter $\mathbf{l}^{-1}[\mathbf{m}]$ that provides a fourth-order discretization of the inverse Laplacian operator $\Delta^{-1}$. This can be achieved by first obtaining a 1D filter $l$ that provides a fourth-order discretization of the 1D second-derivative operator. On the Cartesian and BCC lattices, application of this filter along the principal directions followed by a summation of the resulting coefficients, yields a fourth-order discretization of the Laplacian~\cite{usmanthesis}. The inverse Laplacian filter $\mathbf{l}^{-1}$ is simply the inverse of the resulting Laplacian filter. Our approximation $\inda(\vx)$ can now be written as {\small
\begin{equation}
	\inda(\vx)  = \displaystyle\sum_{\mathbf{k}} (\mathbf{f} \ast \mathbf{l}^{-1})_k\varphi_k(\vx)
\end{equation}}
where $\mathbf{f}$ is the coefficient vector obtained in the previous step (cf. equation~\EQ{eq:divergenceViaFiltering}). The only stipulations to this is that the indicator function must satisfy zero Dirichlet boundary conditions (which is given as part of the problem definition). In practice, the filter $\mathbf{l}^{-1}$ does not need to be computed explicitly as it can be efficiently applied in the Fourier domain via a Discrete Sine Transform (DST) that only depends on the 1D filter $l$~\cite[Chapter 4]{usmanthesis}. Whereas the DST on the Cartesian lattice is well-defined, on the BCC lattice, we utilize a  modified DST that can be efficiently implemented via 1D DSTs~\cite{bccdst}. The particular filter $l$ used in our experiments can be found in \TA{tab:filters}.

\subsection{Extracting the Iso-Contour}\label{sec:levelset}
With a true indicator function, the level-set desired is the set of points $\vx$ such that $\inda(\vx) = \frac{1}{2}$, which can readily be visualized either via marching algorithms, ray tracing, or other volumetric visualization techniques. However, the constant scaling factor of equation \EQ{eq:vdef} offsets the appropriate level set at which to threshold the indicator function. A common approach that has shown to be quite robust in this situation \cite{fftk}, is to average the levelset obtained by evaluating the approximation at the input points $\frac{1}{|P|}\sum_{(\vx,\vn)\in P}{\tilde{\chi}(\vx)}.$ The reasoning for this, is that the iso-value at the input data should be on, or at least near the surface of the model. Once the iso-surface has been determined, the mesh is extracted via marching cubes, with the step density set to half the lattice scaling factor ($frac{h}{2}$) \cite{}

### 2015-02-15 relatedwork.tex
Added Floating surface recon

@@
 Recently, there has also been research that incorporates point normals
-into the radial basis reconstruction framework \cite{hermite}. \ednote{Add 
-that paper from torsten here}
+into the radial basis reconstruction framework \cite{hermite}. It's also
+possible to construct an implicit function as a normalize sum of 
+compactly supported basis functions defined over an oct-tree, 
+essentially ``smearing'' the point-set around space and constructing 
+an indicator ``shell'' around them \cite{Fuhrmann2014}.
 

### 2015-02-15 results.tex
Added Floating surface recon

@@
 \end{equation*}}
+
 generates a piecewise linear polynomial function \cite{practicalbox}.
@@
 More generally and relevant to our purposes, they have also been shown to reduce error when approximating the gradient of scalar fields \cite{gradrev}.
+
+\begin{table}[!t]
+	%% increase table row spacing, adjust to taste
+	\renewcommand{\arraystretch}{1.5}
+	% if using array.sty, it might be a good idea to tweak the value of
+	%\extrarowheight % as needed to properly center the text within the cells
+	\centering
+	% Some packages, such as MDW tools, offer better commands for making tables
+	% than the plain LaTeX2e tabular which is used here.
+	\begin{tabular}{|r||c||c|c|}
+		\hline
+		Filter & Notation & Filter wieghts  \\
+		\hline
+		\hline
+		Derivative & $d[n]$ & $[\frac{-1}{12} \ \frac{2}{3} \ 0 \ \frac{-2}{3} \ \frac{1}{12}]$ \\
+		\hline
+		Shifted Derivative & $s[n]$  & $[\frac{-1}{24} \ \frac{9}{8} \ \frac{-9}{8} \ \frac{1}{24} \ 0]$ \\
+		\hline
+		Second Derivative & $l[n]$  & $[\frac{-1}{12} \ \frac{4}{3} \ \frac{-5}{2} \ \frac{4}{3} \ \frac{-1}{12}]$ \\
+		\hline
+	\end{tabular}
+	\caption{Filters used in our experiments. These filters are applied along the principal lattice directions.}
+	\label{tab:filters}
+\end{table}
+
+\section{Results and Discussion}
+For our tests, we restrict ourselves to the function spaces spanned by the Cubic tensor product basis on the Cartesian lattice, and the Quintic basis function on the BCC lattice.
+To provide a baseline reconstruction with which to compare our results, we consider FFT, Poisson and Screened Poisson Methods.
+We utilize the test models and point-sets of the Anchor, Daratech, Dancing Children, Gargoyle, and Quasimoto models provided by the Surface Reconstruction Benchmark \cite{reconbench}.
+
+% This isn't true for the images that are currently in the paper.
+%For our visual comparisons, we ray trace the iso-surface produced by our method.
+We reason that that any marching algorithm that produces a triangulated mesh, inherently uses linear interpolation to fill in missing data, and potentially reduces the approximation power of our function space.
+However, in order to measure the error between our reconstructions and a baseline, a mesh must be extracted.
+In that case we march to twice the resolution of an equivalent Cartesian grid.
+
+Quantitatively, we evaluate whether function spaces on the BCC lattice provide better approximation spaces than those on the Cartesian lattice.
+In order to reduce any artifacts that may arise from any noise or the non-uniformity of the data, we utilize the ideal reference point-sets of our test models.
+We measure both the Hausdorff distance, mean distance, and angle deviation from the original shape with the tools provided by Berger et al.~\cite{reconbench}.
+We evaluate the FFT, Poisson, and Screened Poisson surface reconstruction algorithms, as their theory is close to ours.
+We choose $\lambda_1$ and $\lambda_2$ so that the reconstructions are comparable to the Screened Poisson results.
+
+%- Perhaps a little more discussion on how the approach compares to Poisson and screened poisson, both quantitative and qualitative. -
+Since the Gargoyle model has many interesting high frequency features, we consider reconstructing it at increasing grid resolutions.
+For the Poisson and Screened Poisson methods, we restrict the depth of the tree so that the finest resolution provided by the oct-tree is equivalent to that of the regular Cartesian, \FG{fig:t1}.
+We also seem to be able to improve upon the Screened Poisson method, however, the parameter space needs to be explored further to conclusively assert this.
+Regardless, it is still a good baseline with which to compare our results.
+
+%You should really try to bring out the role of the shifts.
+We fix the resolution of the grid at $128^3$, and reconstruct the remaining models (\FG{fig:t2}.) We choose this resolution as it seems to be a point of contention between the cases with the Gargoyle model.
+However, there seems to be a consistent advantage in using the BCC lattice over the Cartesian lattice.
+Moreover, in both cases, we noticed that introducing a shift tends to reduce all error metrics.
+Unfortunately, reconstructing the divergence of the smoothed vector field from more than three lattice directions produced little difference.
+\FG{fig:r1} shows a visual comparison of the techniques.
+We manage to outperform the FFT and Poisson techniques by a large margin, and outperform the screened Poisson case.
+
+\begin{figure*} 
+	\centering
+	\begin{tabular}{c c c c}
+	\includegraphics[width=0.23\linewidth]{figures/dist32.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/dist64.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/dist128.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/dist256.eps} \\
+	\includegraphics[width=0.23\linewidth]{figures/angle32.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/angle64.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/angle128.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/angle256.eps} 
+	\end{tabular}
+	\caption{An error comparison for the Gargoyle model as the grid resolution increases from $32^3$ to $256^3$ in steps of powers of two.
+The top row represents the Hausdorff (bar height) and mean distance (black line) to the original baseline model, while the bottom row represents the max angle deviation.
+$\lambda_1 = 100$, and $\lambda_2$, was chosen to be $1\scint{-3}$, $1\scint{-4}$, $1\scint{-5}$ and $1\scint{-6}$ from left to right respectively.
+Notice that the introduced shift greatly reduces angular error.}
+	\label{fig:t1}
+\end{figure*}
+
+\begin{figure*} 
+	\centering
+	\begin{tabular}{c c c c}
+	\includegraphics[width=0.23\linewidth]{figures/anchor/_dist.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/daratech/_dist.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/dc/_dist.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/quasimoto/_dist.eps} \\
+
+	\includegraphics[width=0.23\linewidth]{figures/anchor/_angle.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/daratech/_angle.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/dc/_angle.eps} &
+	\includegraphics[width=0.23\linewidth]{figures/quasimoto/_angle.eps} \\
+	Anchor & Daratech & Dancing Children & Quasimoto 
+	\end{tabular}
+	\caption{A similar comparison for the case in which the grid is fixed at a resolution of $128^3$ for all models.
+Here, $\lambda_1=1\scint{2}$, and $\lambda_2=5\scint{-5}$.
+Again, we see the same trend of the BCC lattice outperforming the comparable Cartesian lattices, and the Screened Poisson approach.}
+	\label{fig:t2}
+\end{figure*}
+
+\begin{figure} 
+	\centering
+	\begin{tabular}{c c}
+		\includegraphics[width=0.48\linewidth,natwidth=750,natheight=750]{images/gargoyle/original.eps} &
+		\includegraphics[width=0.48\linewidth,natwidth=750,natheight=750]{images/gargoyle/poisson.eps} \\
+		Original & Poisson \\
+		\includegraphics[width=0.48\linewidth,natwidth=750,natheight=750]{images/gargoyle/bcc.eps} &
+		\includegraphics[width=0.48\linewidth,natwidth=750,natheight=750]{images/gargoyle/bccs.eps} \\ 
+		BCC & BCC Shifted \\ 
+		\includegraphics[width=0.49\linewidth,natwidth=750,natheight=750]{images/gargoyle/bcc4.eps} &
+		\includegraphics[width=0.49\linewidth,natwidth=750,natheight=750]{images/gargoyle/bcc4s.eps} \\
+		BCC4 & BCC4 Shifted \\ 
+		\includegraphics[width=0.49\linewidth,natwidth=750,natheight=750]{images/gargoyle/cc.eps} &
+		\includegraphics[width=0.49\linewidth,natwidth=750,natheight=750]{images/gargoyle/ccs.eps}  \\
+		Cartesian & Cartesian Shifted 
+	\end{tabular}
+	\caption{A set of reconstructions on a $128^3$ Cartesian grid, $50\times50\times100$ BCC grid or an oct-tree depth of 7.
+Parameters were chosen as $\lambda_1 = 1\scint{2}$ and $\lambda_2 = 1\scint{-4}$.
+Comparing between the Cartesian and BCC reconstruction spaces, the BCC lattice seems to consistently outperform the Cartesian lattice beyond a resolution of $128^3$, moreover, the advantage of shifting the reconstruction space is apparent, specifically around the teeth and lips of the model.}
+	\label{fig:r1}
+\end{figure}
+
+\begin{figure} 
+	\centering
+	\begin{tabular}{c c}
+		\includegraphics[width=0.48\linewidth]{images/robust/pointset.eps} &
+		\includegraphics[width=0.48\linewidth]{images/robust/poisson.eps} \\
+		Noisy Point-set & Screened Poisson  \\
+		\includegraphics[width=0.48\linewidth]{images/robust/bcclowlambda.eps} &
+		\includegraphics[width=0.48\linewidth]{images/robust/bccbiggerlambda.eps} \\ 
+		BCCS $\lambda_2=5\scint{-5}$ & BCCS $\lambda_2 = 5\scint{-4}$ \\
+	\end{tabular}
+	\caption{Varying the smoothing parameter $\lambda_2$ allows us to smooth our noise from practical data sets $(\lambda_1 = 1\scint{2})$.
+The Screened Poisson method is able to more faithfully reconstruct the center hole of the Anchor model.
+Our method, however, is unable to infer the importance of the samples on the interior of the Anchor.}
+	\label{fig:r2}
+\end{figure}

### 2015-02-16 introduction.tex
Adding refs to optimal lattice stuff in 2d.

@@
 Reconstructing a solid model from a scattered set of points is a common and well studied problem in computer graphics.
-Interest in this problem is rooted in the desire to convert real life data-sets -- acquired from range and now increasingly from commodity hardware like the Kinect -- to 3D polygonal models.
-The idea also has a applications in model re-meshing and hole filling.
-\ednote{This needs more meat, it's a pretty weak ending to the intro paragraph.}
+Interest in this problem is rooted in the desire to convert real life data-sets -- data acquired from range scanners and now increasingly from commodity hardware like the Kinect -- to 3D polygonal models.
+The idea also has a applications in model re-meshing and mesh hole filling, when one has a poorly formatted mesh and would like a better representation of it.
 
@@
    \hfill \mbox{}
-  \caption{\label{fig:lattices}%
+  \caption{\label{fig:lattices}
   Sampling lattices (top) with with their corresponding Voronoi regions (bottom). Left to right are the CC, BCC and FCC lattices respectively.
@@
 Using an appropriate discretization of the derivative/divergence operator is an important step in recovering the indicator function of the initial model.
-\ednote{Need to emphasize the error-kern here}
+We also derive specific error bounds, based on an error kernel formulation, for approximations of linear operators in arbitrary shift invariant spaces.
 
@@
 \end{itemize}
-
-\ednote{OVERALL: What is lacking from this intro is the true purpose of this work (from the surface reconstruction aspect.) We want to show that the BCC beats the CC lattice.
-NOT that our scheme is better than Kazhdan's.
-We do show this, but we need to emphasize it above!}

### 2015-02-16 relatedwork.tex
Adding refs to optimal lattice stuff in 2d.

@@
 
+Outside of the context of surface reconstruction there has been considerable
+evidence that shows non-Cartesian approaches to volume rendering 
+\cite{firstbox, practicalbox, hvolrecon} and fluid flow \cite{lboltzman} outperform 
+Cartesian approaches in both speed and memory consumption. Additionally, 
+finite difference Laplacian stencils on non-Cartesian grids lead to reduced 
+numerical dispersion compared to their Cartesian  counterparts (see e.g. 
+\cite{hamilton2013, hamilton2013hexagonal} and references therein). It is 
+therefore natural to question whether these advantages can be exploited 
+within the context of surface reconstruction.
+
 Our approach aims to solve the Poisson surface reconstruction problem
-in the setting of shift-invariant spaces. A crucial step in this
+in the setting of general shift-invariant spaces. A crucial step in this
 regard is the accurate estimation of the divergence of the gradient

### 2015-02-16 indicator.tex
Updating refs and splitting results

@@
 \section{Recovering the Indicator}
+
 \label{sec:recoveringX}
@@
 A common approach that has shown to be quite robust in this situation \cite{fftk}, is to average the levelset obtained by evaluating the approximation at the input points $\frac{1}{|P|}\sum_{(\vx,\vn)\in P}{\tilde{\chi}(\vx)}.$ The reasoning for this, is that the iso-value at the input data should be on, or at least near the surface of the model.
-Once the iso-surface has been determined, the mesh is extracted via marching cubes, with the step density set to half the lattice scaling factor ($frac{h}{2}$) \cite{}
+Once the iso-surface has been determined, the mesh is extracted via marching cubes, with the step density set to half the lattice scaling factor ($\frac{h}{2}$) \cite{}

### 2015-02-16 relatedwork.tex
Updating refs and splitting results

@@
 reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose 
-level-set, $f(\mathbf{x})=s$ (for some iso-value $s \in \realn$), represents an
+level-set, for some iso-value $s \in \realn$, $f(\mathbf{x})=s$ represents an
 approximation to the original surface. Other non-implicit techniques
-generally infer meshes through some other combinatorial means, 
-or a set predefined logic or rules.
+generally infer meshes through some other combinatorial means 
+or set predefined logic/rules.
 

### 2015-02-19 prelim.tex
Changed some notation to fit with Usman's work, added error section to prelim, fixed a few small spelling/notation mistakes.

@@
 \realn^3 \times \realn^3 \}$ where $\mathbf{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively.
-Orientation can be succinctly represented with only two values, however, it is convenient to keep it denoted as the normal at a point.
-This is because the length of the normal can be used to encode the sampling density of the point-set at a point.
+Orientation can be succinctly represented with only two values, however, it is convenient to keep it as the normal at a point, because the length of the normal can be used to encode the sampling density of the point-set at a point.
 For the following discussion, we also need to introduce the notation $\patch_{\mathbf{s}}$, which denotes a patch of the surface model about the sample location $\mathbf{s}$.
@@
 This simplifies and reduces the computational cost of the method when used in conjunction with an oct-tree based representation of $\vec{V}(\vx)$ \cite{Kazhdan06}.
-However, there is a disadvantage in that $F$ may over smooth data in areas of high curvature \cite{reconbench}, much in the same way that a representation of a sampled signal may fail to take advantage of the full approximation power of the function space in which it is represented if it is not properly prefiltered.
-Theoretically, one could reconstruct the surface at higher resolutions, allowing the basis functions to become more ``fine'', but increasing the total amount of memory used.
-However, this is not realistic in praxis.
-Another approach is to impose a type of ``interpolation'' constraint on the original data \cite{screenedk}.
+However, the  disadvantage of this choice is that $F$ may over smooth data in areas of high curvature \cite{reconbench}, much in the same way that a representation of a sampled signal may fail to take advantage of the full approximation power of the function space in which it is represented if it is not properly prefiltered.
+Theoretically, one could simply reconstruct the surface at higher resolutions, allowing the basis functions to become more ``fine'', but increasing the total amount of memory used.
+On a regular grid, this is undesirable.
+Another approach is to impose a type of ``interpolation'' constraint on the original data \cite{screenedk} \SC{section on this}.
 
@@
 Before presenting our approach (\SC{sec:pipeline}), we review the necessary background behind shift-invariant spaces and its connection to irregular sampling.
-%\ednote{UA: Provided additional motivation for the variational framework, and added a gluing paragraph to imrpove the flow.}
 
 \subsection{Sampling Lattices} \label{sec:smpl_review}
-In the univariate case, there is only one way to uniformly sample a signal; take equally spaced samples along the independent axis.
-However, when sampling multivariate signals, the situation is not as straightforward.
-A common approach is to inherit the ideas from the univariate case, and sample the function at regular intervals in each axis (known as a Cartesian sampling), while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling).
-If $\mathbf{L}$ is a unimodular matrix, the set $\{\mathbf{L}\cdot\mathbf{n} : \mathbf{n} \in \intn^3 \}$ (linear combinations of the vectors of $\mathbb{L}$ with integer coefficients), represents all possible sampling lattices.
-$\mathbf{L}$ is often called the \emph{generating matrix} for a lattice.
-To control the sampling rate of a function, a uniform scaling parameter $h$ is introduced.
-Typically, for the problem of surface reconstruction, our input data are not uniformly distributed in space (or even about the surface of the model).
-However, the concept of a sampling lattice is fundamental in forming the definition of our target approximation spaces (\SC{sec:sis_review}).
+In the univariate case, there is only one way to uniformly sample a signal: take equally spaced samples along the independent axis.
+However, when sampling multivariate signals the situation is not as straightforward.
+A common approach is to inherit the ideas from the univariate case and sample the function at regular intervals in each axis -- a Cartesian sampling --  while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling).
+If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\mathbf{n} : \mathbf{n} \in \intn^3 \}$ represents all possible sampling lattices.
+$\mathbf{L}$ is often called the \emph{generating matrix} for a lattice, and we'll assume that $\mathbf{L}$ is normalized so that $\left|\det\mathbf{L}\right| = 1$.
+The lattice's dual, denoted by $\duallattice{L}$, is the lattice generated by $\mathbf{L}^{-T}$.
+Finally, to control the sampling rate of a function a uniform scaling parameter $h$ is introduced -- lattices scaled by this parameter will be denoted by $\lattice{L}_h$.
+Typically, for the problem of surface reconstruction, our input data are not uniformly distributed in space, or even about the surface of the model, but the concept of a sampling lattice is fundamental in forming the definition of our target approximation spaces (\SC{sec:sis_review}).
 
@@
 Owing to this, the implementation of generating functions that span function spaces on the Cartesian lattice may be realized by a tensor product extension of existing univariate techniques.
-Filtering techniques are also easy to implement, as the Fast Fourier Transform is also separable, and may be applied independently to each axis of the data.
+Filtering techniques are also easy to implement, as the Fast Fourier Transform is  separable and may be applied independently to each axis of the data.
 However, in terms of sampling efficiency, the BCC lattice is the optimal lattice in $\realn^3$, while the Cartesian is sub-optimal.
 
-The Body-Centered Cubic (BCC) lattice is generated by the integer matrix  {\footnotesize
+The Body-Centered Cubic (BCC) lattice is generated by the matrix  {\footnotesize
 \begin{equation*} 
-	\mathbf{L}_B := 
+	\mathbf{L}_B := \frac{1}{\sqrt[3]{4}}
 	\begin{bmatrix}
@@
 \begin{equation*}
-	\fspce{\varphi}{h\mathbf{L}} := \left\{ g(\vx) := \displaystyle\sum_{\mathbf{m} \in \intn^3} c[\mathbf{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
+	\fspce{\varphi}{ \lattice{L}_h} := \left\{ g(\vx) := \displaystyle\sum_{\mathbf{m} \in \intn^3} c[\mathbf{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
 \end{equation*}}
@@
 Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\mathbf{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.
+
+Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice.
+We denote the set of such points as $\{\mathbf{s}_1,\mathbf{s}_2,\ \hdots  \ \mathbf{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\mathbf{s}_k)$; from this perspective, our function space is now {\small
+\begin{equation}
+	\left\{ \displaystyle\sum_{k=0}^N c_k \varphi_k(\vx) \right\} \subset \fspce{\varphi}{\lattice{L}_h}.
+\end{equation}}
+Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $\Phii_{i,j} := \varphi_j(\vx_i)$.
+Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites and we must consider alternative schemes for finding $\mathbf{c}$, which we'll come back to in \SC{sec:vari_review}
+
+\subsection{Error Analysis} \label{sec:sis_error}
+To facilitate the classical analysis of signals in a shift-invariant space, we need a few notions first.
+The first tool we need is the Fourier transform of a multivariate function $f(\mathbf{x})$, which we define as $\ft{f}(\vect{\omega}) := \int_{\reel^3} f(\vect{x}) \exp(-2\pi \imath
+\vect{\omega} \cdot \vect{x})  \mathrm{d}\vect{x} $.
+The discrete time Fourier transform (DTFT) of a sequence $c[\cdot]$ associated with a lattice $\lattice{L}$ is defined as $\ft{C}(\vect{\omega}) := \sum_{\vect{m}  \in \ints^3} c[\vect{m}] \exp(-2 \pi \imath \vect{\omega} \cdot
+(\mat{L}\vect{n}))$.
+Recall that $\ft{C}(\vect{\omega})$ is periodic with respect to the dual lattice $\duallattice{L}$, i.e.
+$\ft{C}(\vect{\omega} + \invtransp{\mat{L}} \vect{m}) = \ft{C}(\vect{\omega}), \forall \vect{m} \in \ints^3$.
+The notation `$\ftpairs{}{}$' is subsequently employed to denote transform pairs, i.e.
+$\ftpairs{f(\vect{x})}{\ft{f}(\vect{\omega})}$ (Fourier transform pairs) and $\ftpairs{c[\vect{m}]}{\ft{C}(\vect{\omega})}$ (DTFT pairs).
+
+The inner product between two real valued functions $f_1$ and $f_2$ belonging to $L_2(\reel^3)$ is denoted as $\ip{f}{g} := \int_{\reel^3} f(\vect{x}) g(\vect{x}) d\vect{x}$.
+Likewise, the inner product between two functions $f_1$ and $f_2$ that belong to $L_2(\cube^s)$ is denoted as $\innerproduct{f_1}{f_2} := {2^{-s}} \int_{\cube^s} f_1(\vect{x}) f_2(\vect{x}) d\vect{x}$.
+The norms induced by these inner products are denoted as $\Ltwonorm{\cdot}$ and $\LLnorm{\cdot}$ respectively.
+
+In order to ensure that any function $g \in \aspace{\lattice{L}}{\varphi}$ has a unique representation in terms of a finite energy coefficient sequence $c[\cdot]$, the lattice translates $\{\varphi(\cdot - \mat{L}\vect{n})\}_{\vect{n}  \in \ints^s}$ must form a Riesz basis~\cite{kreyszig89}, i.e.
+there exist positive constants $a$ and $b$ such that $\forall c[\cdot] \in l_2(\ints^s)$,
+\begin{equation*}
+  a \norm{c}^2_{l_2(\ints^s)} \le \Ltwonormbig{\sum_{\vect{n} \in \ints^s}
+  c[\vect{n}] \varphi(\vect{x} - \mat{L}\vect{n})}^2 \le b
+	\norm{c}^2_{l_2(\ints^s)}.
+\end{equation*}
+
+\subsection{The Error Kernel}
+
+introduce error kernel.
+
+ polynomial spaces,
+
+introduce notion of decay.
 
@@
 
-Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice.
-We denote the set of such points as $\{\mathbf{s}_1,\mathbf{s}_2,\ \hdots  \ \mathbf{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\mathbf{s}_k)$; from this perspective, our function space is now {\small
-\begin{equation}
-	\left\{ \displaystyle\sum_{k=0}^N c_k \varphi_k(\vx) \right\} \subset \fspce{\varphi}{h\mathbf{L}}.
-\end{equation}}
-Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $\Phii_{i,j} := \varphi_j(\vx_i)$.
-Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites, and we must consider alternative schemes for finding $\mathbf{c}.$
-
-\subsection{Box Splines}
-\label{sec:box_review}
+\subsection{Box Splines} \label{sec:box_review}
 Box splines are compact piece-wise polynomial functions $ M_\mathbf{\Xii} : \realn^s \to \realn.$ The matrix $\mathbf{\Xii}$ denotes a collection of direction vectors, $\mathbf{\Xii} := \left[ \xi_1 \ \xi_2 \hdots \xi_n\right].$ When $n=s$, the function $M_\mathbf{\Xii}(\vx)$ is defined to be $\frac{1}{det|\mathbf{\Xii}|}$ inside the polytope formed by the Minkowski sum of the direction vectors of $\mathbf{\Xii}$, and zero otherwise (that is, $\frac{1}{det|\mathbf{\Xii}|}$ when $\vx \in \{ \mathbf{\xi}_1 t_1 + \hdots + \mathbf{\xi}_s t_s  : t_i\in [0,1) \})$.

### 2015-02-19 review.tex
Changed some notation to fit with Usman's work, added error section to prelim, fixed a few small spelling/notation mistakes.

@@
 Before presenting our approach (\SC{sec:pipeline}), we review the necessary background behind shift-invariant spaces and its connection to irregular sampling.
-%\ednote{UA: Provided additional motivation for the variational framework, and added a gluing paragraph to imrpove the flow.}
 
 \subsection{Sampling Lattices} \label{sec:smpl_review}
-In the univariate case, there is only one way to uniformly sample a signal; take equally spaced samples along the independent axis.
-However, when sampling multivariate signals, the situation is not as straightforward.
+In the univariate case, there is only one way to uniformly sample a signal: take equally spaced samples along the independent axis.
+However, when sampling multivariate signals the situation is not as straightforward.
 A common approach is to inherit the ideas from the univariate case, and sample the function at regular intervals in each axis (known as a Cartesian sampling), while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling).
-If $\mathbf{L}$ is a unimodular matrix, the set $\{\mathbf{L}\cdot\mathbf{n} : \mathbf{n} \in \intn^3 \}$ (linear combinations of the vectors of $\mathbb{L}$ with integer coefficients), represents all possible sampling lattices.
+If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\mathbf{n} : \mathbf{n} \in \intn^3 \}$ (linear combinations of the column vectors of $\mathbb{L}$ with integer coefficients), represents all possible sampling lattices.
 $\mathbf{L}$ is often called the \emph{generating matrix} for a lattice.

### 2015-02-20 poisson_errker.tex
Added error kernel to prelim, layout for additional sections set.

\section{Poisson's Equation}

\subsection{Greens Function}

\subsection{Fourier Interpretation}

\subsection{Approximate Solution}

\subsection{Error Analysis}

\subsection{Relationship to the Galerkin method}

### 2015-02-20 prelim.tex
Added error kernel to prelim, layout for additional sections set.

@@
 
-introduce error kernel.
-
+The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation
+$\appf{f} \in \aspace{\lattice{L}_h}{\varphi}$ can conveniently be
+quantified via an error kernel in the Fourier domain. It is defined as
+\begin{equation}
+  E(\vect{\omega}) := \underbrace{1 - \frac{\abs{\ft{\varphi}(\vect{\omega})}^2}{\ft{A}_{\varphi}(\vect{\omega})}}_{E_{\mathsf{min}}(\vect{\omega})}
+  + 
+  \underbrace{
+    \ft{A}_{\varphi}(\vect{\omega})
+    \abs{\ft{\analysis{\varphi}}(\vect{\omega}) -
+      \ft{\dual{\varphi}}(\vect{\omega})}^2
+  }_{E_{\mathsf{res}}(\vect{\omega})}.
+  \label{eq:scErrorKernel}
+\end{equation}
+For a bandlimited function $f$ whose spectrum is entirely contained
+within the Voronoi cell of $\duallattice{L}_h$ centered around
+$\vect{\omega} = 0$, we have 
+\begin{equation}
+\Ltwonorm{f - \appf{f}} = \int_{\reel^s}
+\abs{\ft{f}(\vect{\omega})}^2 E(h\vect{\omega}) d\vect{\omega},
+\label{eq:avgError}
+\end{equation}
+whereas when $f \in W_2^k(\reel^s)$ with $k > \frac{1}{2}$, the
+integral in~\eqref{eq:avgError} gives the $L_2$-error averaged over
+all possible shifts of $f$. Even though this kernel was initially
+proposed in the univariate setting by Blu and Unser~\cite{blu99}, multivariate
+non-Cartesian extensions have also appeared in the
+literature~\cite{condat05hexagonal, condat07, condat08, alim10,
+  condat11}. Note that the minimum-error approximation scenario occurs
+when $f$ is orthogonally projected to $\aspace{\lattice{L}_h}{\varphi}$,
+or in other words $\analysis{\varphi}$ is chosen to be  $\dual{\varphi}$.
  polynomial spaces,
 
-introduce notion of decay.
+\subsection{Approximation Error}
 

### 2015-02-20 results.tex
Updating refs and splitting results
Added error kernel to prelim, layout for additional sections set.

@@
-\subsection{Experiments and Results}
+\section{Experiments}
 
-\subsubsection{Cartesian Lattice}
+\subsection{Cartesian Lattice}
+Blurb about cartesian lattices.
+
+\subsubsection{Basis function}
 Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial.
@@
 
-\subsubsection{BCC Lattice}
+\subsubsection{Filter weights}
+
+\subsection{BCC Lattice}
+Blurb about cartesian lattices.
+
+\subsubsection{Basis function}
 On the BCC lattice, a choice of {\footnotesize
@@
 
-\subsubsection{Shifted Basis Functions}
+\subsubsection{Filter weights}
+
+\subsection{Shifted Basis Functions}
 We also consider shifted box splines $M_{\mathbf{\Xii}}^{\xi_i}(\vx) := M_{\mathbf{\Xii}}(\vx - \frac{1}{2}\mathbf{\xi}_i)$, where $\mathbf{\xi}_i$ is any direction vector in $\mathbf{\Xii}$.
@@
 
-% This isn't true for the images that are currently in the paper.
-%For our visual comparisons, we ray trace the iso-surface produced by our method.
-We reason that that any marching algorithm that produces a triangulated mesh, inherently uses linear interpolation to fill in missing data, and potentially reduces the approximation power of our function space.
-However, in order to measure the error between our reconstructions and a baseline, a mesh must be extracted.
-In that case we march to twice the resolution of an equivalent Cartesian grid.
-
 Quantitatively, we evaluate whether function spaces on the BCC lattice provide better approximation spaces than those on the Cartesian lattice.
@@
 
-%- Perhaps a little more discussion on how the approach compares to Poisson and screened poisson, both quantitative and qualitative. -
 Since the Gargoyle model has many interesting high frequency features, we consider reconstructing it at increasing grid resolutions.

### 2015-03-08 poisson_errker.tex
Added all of the Poisson work to the paper, still needs to be ref'd and cleaned.

@@
 \section{Poisson's Equation} 
+We seek an approximation of the function $V$ that satisfies the Poisson equation with homogeneous Dirichlet boundary conditions, i.e. 
+\begin{equation} \label{eq:PoissonEquation}
+	\begin{split}
+		\laplacian{V} &= f, \;\; \text{in} \;\; \oucube^s, \\
+		V &= 0, \;\; \text{on} \;\; \partial \ucube^s,
+	\end{split}
+\end{equation}
+where $\laplacian$ is the $s$-dimensional Laplace operator and
+$\partial \ucube^s$ denotes the boundary of $\ucube^s$,
+i.e. $\partial \ucube^s \cup \oucube^s = \ucube^s$.
 
 \subsection{Greens Function}
+The Poisson equation is an example of a well-studied partial differential equation.
+When the domain of interest is the unit cube $\ucube^s$, the solution can be analytically expressed in terms of a Green's function $\mathsf{G}(\vect{x},\vect{y})$ that represents the potential due to a point source placed at the location $\vect{x}$ inside $\ucube^s$.
+In other words $\laplacian_{\vect{x}} \mathsf{G}(\vect{x},\vect{y}) = \delta(\vect{x}-\vect{y})$.
+The Green's function $\mathsf{G}$ has the Fourier Sine series expansion
+\begin{equation}
+	\mathsf{G}(\vect{x},\vect{y}) = \sum_{\vect{m} \in \ints^s_+} 
+	\frac{\prod_{i=1}^s \sin(m_i \pi x_i) \sin(m_i \pi y_i)}
+	{-\pi^2 \norm{\vect{m}}^2},
+	\label{eq:green}
+\end{equation}
+and the solution $V$ is given by
+\begin{equation}
+	V(\vect{x}) = \int_{\ucube^s}f(\vect{y})\mathsf{G}(\vect{x},\vect{y}) d\vect{y}.
+	\label{eq:analytic}
+\end{equation}
 
@@
 
+Even though there has been much effort on finding alternate rapidly
+convergent series representations of the Green's function (see
+e.g. Marshall~\cite{marshall99}), it turns out that the form of the
+Green's function given in~\eqref{eq:green}, is ideally suited
+for our needs as it allows us to easily express the solution in the
+Fourier domain in terms of the Fourier coefficients of $f$.
+
+Suppose we are given an $L_2(\ucube^s)$ function $\rho(x)$ that is
+defined on the open unit cube $\oucube^s$. In order to obtain a
+Fourier sine series that converges to $\rho$ almost everywhere in
+$\oucube^s$, we need to extend $\rho$ periodically such that it is odd
+with respect to each variable. Particularly, let us extend the domain
+of $\rho$ so that, within the interval $\cube^s$, it satisfies
+\begin{equation}
+  \small{
+ \rho(\vect{x}) :=  
+\begin{cases}
+\bigl( \prod_{i=1}^s \sgn(x_i) \bigr)
+\rho(|x_1|, \ldots, |x_s| ) &\mbox{if } \forall i \; |x_i| \ne 0 \\ 
+0 &\mbox{otherwise},
+\end{cases}
+}
+\label{eq:oddextension}
+\end{equation}
+while outside $\cube^s$, it is $\cube^s$-periodic, i.e. $\rho(\vect{x}
++ 2\vect{k}) = \rho(\vect{x})$ for $\vect{k} \in \ints^s$. The
+extended function $\rho$ can be developed into a multidimensional
+Fourier sine series, the coefficients of which are given by 
+\begin{equation}
+  \st{\rho}[\vect{m}] = 2^s \innerproduct{\rho(\vect{x})}
+  {\textstyle{\prod_{i=1}^s}\sin(m_i\pi x_i)}, \; \text{for}\; \vect{m} \in \ints^s_+.
+\end{equation}
+The coefficient sequence $\st{\rho}[\vect{m}]$ can also be seen as a
+special case of the more general multidimensional Fourier
+series. In fact, with an odd extension of the sequence $\st{\rho}$, the
+function $\rho$ can be expressed as a Fourier series. In particular,
+if we define the Fourier series coefficients $\ft{\rho}[\vect{m}]$
+(for $\vect{m} \in \ints^s$) as
+\begin{equation}
+  \small{
+  \ft{\rho}[\vect{m}] := 
+\begin{cases}
+\frac{1}{(2\imath)^{s}} \prod_i \sgn(m_i)
+\st{\rho}[|m_1|,\ldots,|m_s|] &\mbox{if } \forall i \; |m_i| \ne 0 \\
+0 &\mbox{otherwise},
+\end{cases}
+}
+\label{eq:oddFourierExtension}
+\end{equation}
+then  $\rho$ is also given by the Fourier series
+$
+  \rho(\vect{x}) = \sum_{\vect{m} \in
+    \ints^s} \ft{\rho}[\vect{m}] 
+\exp(\imath \pi \vect{m} \cdot \vect{x})
+$.
+Thus, we use the notation $\st{\rho}[\cdot]$ and $\ft{\rho}[\cdot]$ to
+distinguish between the Fourier sine series and Fourier series
+coefficients of the periodic function $\rho$.
+%Note that in the above equation, $\ft{\rho}[\vect{m}]$
+%denotes the Fourier series of $\rho$ and is valid for all $\vect{m} \in
+%\ints^s$.
+
+Since the Green's function $\mathsf{G}$ is defined in $\oucube^s$ and has a
+Fourier sine series representation, it is natural to seek a solution
+that can be developed into a Fourier sine series as
+well. Consequently, for the remainder of this section, we shall only
+be dealing with Fourier sine series. Therefore, it suffices to
+consider only the coefficients in $\ints^s_+$.
+
+Using the analytic solution~\eqref{eq:analytic} and the sine series
+representation of the Green's function~\eqref{eq:green}, it is easy to show that
+the solution is given by
+\begin{equation}
+  \st{V}[\vect{m}] = -
+  \frac{\st{f}[\vect{m}]}{\pi^2 \norm{\vect{m}}^2},
+\label{eq:fourierSolution}
+\end{equation}
+where $\vect{m} \in \ints^s_+$ and $\st{f}[\cdot]$ represents the Fourier
+sine series coefficients of the odd extension of $f$. To facilitate subsequent
+discussions, let us introduce the solution operator
+$\stpairs{\invlaplacian}{\frac{1}{-\pi^2 \norm{\vect{m}}^2}}$  ($\vect{m} \in
+\ints^s_+$), where the symbol $\stpairs{}{}$ represents how the Fourier sine
+series coefficients are affected by the operator.
+%\begin{equation}
+%V(\vect{x}) = \invlaplacian\Bigl( f(\vect{x}) +
+%\sum_{i=1}^s D^0_i g^0_i(\vect{x}) + D^1_i g^1_i(\vect{x}) \bigr), 
+%\label{eq:operatorAnalytic}
+%\end{equation}
+The self-adjoint operator $\invlaplacian$ is the inverse of the Laplace
+operator. Self-adjointness can be easily verified with
+the aid of Parseval's relation, which states that
+$
+  \innerproduct{a}{b} = \sum_{\vect{m} \in \ints^s_+} \st{a}[\vect{m}]
+  \st{b}[\vect{m}] 
+$
+for any $\cube^s$-periodic functions $a$ and $b$ that are in
+$L_2(\cube^s)$ and odd.
+
 \subsection{Approximate Solution}
+We are interested in the scenario where the function $f$ is only known
+through its point samples. Specifically, we assume that the samples of
+$f$ reside on the sites of the lattice $\lattice{L}_h$. For the
+purpose of enumerating the samples that are contained within
+$\cube^s$, let us define the point set
+\begin{equation}
+  \pointset{P}_h := \underbrace{\{\vect{x}_1,\ldots,\vect{x}_{2^sN} \}}_{\pointset{I}_h}
+  \cup
+\underbrace{\{\vect{x}_{2^sN + 1},\ldots,\vect{x}_{2^sN + M} \}}_{\pointset{B}_h},
+\end{equation}
+where $\pointset{I}_h := \ocube^s \cap \{\vect{x} + \vect{m} :
+\vect{x} \in \lattice{L}_h \cap \oucube^s, \vect{m} \in \ints^s \}$
+consists of interior lattice points, while $\pointset{B}_h$ consists
+of extended boundary points, i.e. $\pointset{B}_h := (\lattice{L}_h
+\cap \partial\cube^s \cap (-1,1]^s) \cup (\lattice{L}_h \cap
+\ocube^s\backslash \pointset{I}_h)$. Two dimensional illustrations are
+shown in Figure~\ref{fig:pointset}. We note that with the above
+definition of $\pointset{I}_h$, the points $\vect{x}_j$ for $j \in
+\{1, \ldots, N\}$ are contained in the open unit cube $\oucube^s$
+whereas the remaining points ($\vect{x}_j$ for $j \in \{N+1, \ldots,
+2^sN\}$) lie outside. Furthermore, we assume
+that the lattice $\lattice{L}$ and the sampling rate $h$ are such that
+the set $\{\vect{x} + 2\vect{m} : \vect{x} \in \pointset{P}_h,
+\vect{m} \in \ints^s\} = \lattice{L}_h$. We remark that this
+requirement for $\lattice{L}_h$ is also
+satisfied by integration lattices that are commonly used
+to devise quadrature rules within the unit cube $\ucube^s$~\cite{nied92}.
+\begin{figure}[t]
+  \centering
+  \subfloat[Cartesian]{\label{fig:cartesian}\input{./figures/2DCartesian}}
+  \hspace{2em}
+  \subfloat[Quincunx]{\label{fig:quincunx}\input{./figures/2DQuincunx}}
+  \caption[Interior and boundary samples]{Illustration of the point set
+  $\pointset{P}_h$ on the two
+    dimensional Cartesian ($\mat{L} = \bigl( \begin{smallmatrix} 1&0\\
+      0&1
+    \end{smallmatrix} \bigr)$, $h=\tfrac{1}{8}$) and Quincunx ($\mat{L} = \bigl(
+    \begin{smallmatrix} 1&-1\\
+      1&1
+    \end{smallmatrix} \bigr)$, $h=\tfrac{1}{10}$) lattices. The interior points
+    ($\bullet$) belong to the set $\pointset{I}_h$ while the extended
+    boundary points ($\circ$) belong to $\pointset{B}_h$.}
+  \label{fig:pointset}
+\end{figure}
+
+We denote the interior samples of $f$ as $f[\vect{x}_j] :=
+f(\vect{x}_j)$ where $\vect{x}_j \in \pointset{I}_h$. Note that
+$f[\vect{x}_j]$ only needs to be known in $\oucube^s$ ($j \in
+\{1,\ldots,N\}$), the other samples can be inferred from
+oddity.
+
+We wish to use the samples of $f$ to seek an approximation $\appf{V}$ of the
+function $V$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. Since
+$V$ is a periodic function, we follow the recipe of Jacob \textit{et
+al.}~\cite{jacob02} and seek an approximation that lies in a space generated by
+a periodic reconstruction function. Specifically, we are interested in the case
+where $\appf{V}$ lies in the space $\aspace{\lattice{L}_h}{\varphi_p} :=
+\mathrm{span}_{\vect{x}_j\in\pointset{P}_h}\{
+\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}) \}$ that is spanned by the scaled and
+translated versions of a periodic function $\varphi_p$. Our sought-after
+approximation is given by
+\begin{equation}
+  \appf{V}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{P}_h} c[\vect{x}_j] 
+\varphi_p\bigl(\frac{\vect{x} - \vect{x}_j}{h}\bigr),
+\label{eq:ansatz}
+\end{equation}
+where $c[\vect{x}_j]$ is an unknown coefficient sequence defined on
+the point set $\pointset{P}_h$ that is to be determined from the
+samples of $f$. The function
+$\varphi_p$ is a periodized version of a generating function $\varphi$
+and is defined as
+\begin{equation}
+\varphi_p(\vect{x}) := \sum_{\vect{m} \in \ints^s} 
+\varphi\bigl(\vect{x} - \frac{2}{h} \vect{m} \bigr).
+\label{eq:periodization}
+\end{equation}
+
+%\begin{figure}[t]
+ % \centering
+ % \subfloat[$\cbs^3(x)$]{\includegraphics[width=0.28\columnwidth]
+  %{./figures/periodization/cubic}}
+  %\hspace{2em}
+  %\subfloat[$\cbs^3_p(x)$]{\includegraphics[width=0.28\columnwidth]
+  %{./figures/periodization/cubicPeriodized}}
+  %\hspace{2em}
+  %\subfloat[$\cbs^3_p(\tfrac{x}{h})$]{\includegraphics[width=0.28\columnwidth]
+  %{./figures/periodization/cubicPeriodizedScaled}}
+  %\caption[Making a generator periodic]{1D illustration of the periodization
+  %operation defined by~\eqref{eq:periodization}: $\varphi(x) = \cbs^3(x)$
+  %and $h = 0.2$.}
+  %\label{fig:periodization}
+%\end{figure}
+
+It is easy to verify that, with this definition of $\varphi_p$,
+$\appf{V}$ is also $\cube^s$-periodic. Even though we are only
+interested in the behavior of $\appf{V}$ inside $\ucube^s$, extending
+$\appf{V}$ to the entire domain $\cube^s$ using~\eqref{eq:ansatz}
+allows us to use the Fourier domain error kernel proposed by Jacob
+\textit{et. al}~\cite{jacob02} to quantify the approximation error
+$\LLnorm{V - \appf{V}}$.
+
+Another simplification is in order here. Since the solution $V$ to the Poisson
+problem~\eqref{eq:PoissonEquation} is odd with respect to each variable, we look
+for an approximate solution $\appf{V} \in \aspace{\lattice{L}_h}{\varphi_p}$
+that is also odd in each variable. This can be achieved by setting
+the boundary coefficients to zero and by requiring that the resulting sequence
+be odd.  With $c[\vect{x}_j] = 0$ for $\vect{x}_j
+\in \pointset{B}_h$, the approximation~\eqref{eq:ansatz} simplifies to
+\begin{equation}
+\appf{V}(\vect{x}) = \sum_{j=1}^{2^sN} c[\vect{x}_j] 
+\varphi_p(\frac{\vect{x} - \vect{x}_j}{h}).
+\label{eq:simplifiedAnsatz}
+\end{equation}
+If the generator $\varphi$ is even and the sequence $c[\cdot]$ is odd,
+the resulting approximation $\appf{V}$ is odd and satifies zero
+Dirichlet boundary conditions (see Appendix~\ref{app:1}). With this
+simplification, the coefficient sequence $c[\vect{x}_j]$ only needs to
+be determined for $j \in \{1,\ldots,N\}$. The rest can be inferred
+from oddity.
 
@@
 
+\subsubsection{Error Kernel for Periodic Functions}
+\label{sec:periodicErrorKernel}
+In many approximation problems involving periodic functions, one is interested
+in seeking an approximation $\appf{z}$ of a periodic function $z$ from its
+measurements that lie on some sampling lattice. In light of the notations
+introduced earlier, suppose that $z \in L_2(\cube^s)$ and is also
+$\cube^s$-periodic. Additionally, suppose that the measurements are made at the
+locations $\vect{x}_j \in \pointset{P}_h$ so that one can obtain an
+approximation $\appf{z}$ that belongs to  $\aspace{\lattice{L}_h}{\varphi_p}$
+and --- in a manner similar to the expansion~\eqref{eq:ansatz} --- is given by
+$
+  \appf{z}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{P}_h}
+  \zeta[\vect{x}_j] \varphi_p(\frac{\vect{x}-\vect{x}_j}{h}),
+$
+where the
+coefficient sequence $\zeta[\cdot]$ is obtained through the discrete
+measurements
+\begin{equation}
+  \zeta[\vect{x}_j] = \innerproduct{z(\vect{x})}{\analysis{\varphi}_p(\frac{\vect{x} - \vect{x}_j}{h})}
+\label{eq:measurements}
+\end{equation}
+made with the scaled and shifted versions of a periodic analysis
+function $\analysis{\varphi}_p(\vect{x})$ (the periodization operation
+is defined by~\eqref{eq:periodization}). The main result of Jacob
+\textit{et al.}~\cite{jacob02} states that the mean square
+approximation error $\LLnorm{z - \appf{z}}$ at scale $h$ can
+be predicted according to
+\begin{equation}
+  \sqrt{\sum_{\vect{m} \in \ints^s} \norm{\ft{z}[\vect{m}]}^2 E(\frac{h}{2}\vect{m})}
+\label{eq:prediction}
+\end{equation}
+where $\ft{z}[\vect{m}]$ are the Fourier series coefficients of $z$
+and $E(\cdot)$ is the error kernel of Blu and Unser~\cite{blu99}
+introduced earlier~\eqref{eq:scErrorKernel}.  Remarkably, the same
+error kernel can be used to predict the error for periodic and
+non-periodic functions alike. The only change that needs to be made is
+in the prediction equation. For functions in $L_2(\reel^s)$, the error
+is predicted according to the integral in~\eqref{eq:avgError}. On the
+other hand, for periodic functions that belong to $L_2(\cube^s)$, the
+prediction equation turns into the summation given
+in~\eqref{eq:prediction}. We refer the reader to Jacob \textit{et
+  al.}~\cite{jacob02} for details.
+
+\subsubsection{Extension to Linear Operators}
+We are interested in approximating from the discrete measurements
+of $z$, not the function $z$ itself but a function $\Gamma z$ that is obtained
+by applying the linear operator $\Gamma$ to $z$. 
+% This is exactly the problem we
+% are faced with in the case of approximating the analytic
+% solution~\eqref{eq:fourierSolution} to Poisson's equation. 
+We would like to
+extend the error kernel formulation~\eqref{eq:scErrorKernel} so that it will
+allow us to quantify the error incurred in approximating $\Gamma z$ from the
+measurements of $z$. Towards this end, we assume that the approximation
+$\appf{(\Gamma z)}$ lies in a shift-invariant space spanned by the generator
+$\varphi_p$, where the coefficients are obtained from the measurements through a
+digital filtering operation. Particularly, we seek an approximation that is
+given by
+\begin{equation}
+\appf{(\Gamma z)}(\vect{x}) = C_h \sum_{\vect{x}_j \in \pointset{P}_h} 
+(\zeta \pconv \gamma_h)[\vect{x}_j]
+\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}),
+\label{eq:opApproximation}
+\end{equation}
+where $\zeta$ denotes the discrete measurements of $z$ obtained
+through~\eqref{eq:measurements}, $\gamma$ is a digital filter defined on
+the lattice $\lattice{L}$ and $\gamma_h$ is its corresponding scaled
+version, i.e. $\gamma_h[\vect{x}_j] := \gamma[\tfrac{\vect{x}_j}{h}]$ where
+$\tfrac{\vect{x}_j}{h} \in \lattice{L}$, and $C_h$ is an associated
+scaling constant. The digital filter $\gamma$ represents a suitable
+discretization of the operator $\Gamma$ on the lattice $\lattice{L}$. It is
+to be applied to the measurements through a cyclic convolution
+operation (denoted by $\pconv$) on the lattice $\lattice{L}_h$ using a
+periodized version of $\gamma_h$. In particular, the convolution operation
+in~\eqref{eq:opApproximation} is defined as
+\begin{equation}
+  (\zeta \pconv \gamma_h)[\vect{x}_j] :=
+  \sum_{\vect{x}_k \in \pointset{P}_h}
+  \bigl(
+    \sum_{\vect{m} \in \ints^s}\gamma[\frac{\vect{x}_k + 2\vect{m}}{h}]
+  \bigr)
+  \zeta[\vect{x}_j - \vect{x}_k],
+\label{eq:cyclicConvolution}
+\end{equation}
+where $\vect{x}_j \in \lattice{L}_h$. In the above definition,
+$\zeta[\cdot]$ is assumed to be $\cube^s$-periodic.  Furthermore, the
+resulting sequence $(\zeta \pconv \gamma_h)[\cdot]$ is also
+$\cube^s$-periodic.
+
+% periodic boundary conditions on $\zeta$. Note that, even though $t$ is not
+% periodic, the resulting convolution $\zeta \pconv t_h$ is since $\zeta$ itself
+% is periodic.
+Let $\ft{\Gamma}(\vect{\omega})$ be the Fourier transform of the operator
+$\Gamma$, and $\ft{G}(\vect{\omega})$ be the DTFT of the filter $\gamma$.
+Furthermore, let $\Gamma$ be bounded so that $\Gamma z \in L_2(\cube^s)$.
+A simple modification of the measurement process~\eqref{eq:measurements} yields
+the desired extension of the error kernel formulation~\eqref{eq:scErrorKernel}.
+Our main result can be summarised as follows.
+\begin{thm}
+  Suppose that $\Gamma$ is self-adjoint and shift-invariant. The Fourier
+  error kernel that predicts the approximation error
+  $\LLnorm{\appf{(\Gamma z)} - \Gamma z}$ is given by $E(\vect{\omega}) :=
+  E_{\mathsf{min}}(\vect{\omega}) + E_{\mathsf{mod}}(\vect{\omega})$,
+  where the minimum error kernel $E_{\mathsf{min}}(\vect{\omega})$ is
+  given in~\eqref{eq:scErrorKernel}, while the modified residue
+  error kernel is given by
+  \begin{equation}
+    E_{\mathsf{mod}}(\vect{\omega}) = 
+    \ft{A}_{\varphi}(\vect{\omega})
+    \abs{
+      \frac{\ft{\analysis{\varphi}}(\vect{\omega}) \ft{G}(\vect{\omega})}
+      {\ft{\Gamma}(\vect{\omega})}
+      - 
+      \ft{\dual{\varphi}}(\vect{\omega})}^2.
+    \label{eq:opResidue}
+  \end{equation}
+\label{thm:1}
+\end{thm}
+The proof is given in Appendix~\ref{app:proofs}.
+
+Note that, even though the operator $\Gamma$ acts in the space $L_2(\cube^s)$,
+it is extended to the more general space $L_2(\reel^s)$ in this error kernel
+formulation.
+Therefore,~\eqref{eq:opResidue} can be used to quantify the $L_2$ error in both
+$L_2(\reel^s)$ and $L_2(\cube^s)$. Going back to the original
+problem~\eqref{eq:PoissonEquation}, Theorem~\ref{thm:1} gives us a way to design
+and analyze digital filtering solutions that approximate the analytic
+solution~\eqref{eq:fourierSolution}. In particular, the linear operator that we
+wish to discretize is $\invlaplacian$. In the sequel, we show how to use the
+modified residue error kernel~\eqref{eq:opResidue} to design filtering schemes
+that discretize this operator and can be efficiently implemented in the
+Fourier domain.
+
+In order to characterize the order of accuracy provided by a periodic
+generating function $\varphi_p$, we shall switch to the more general
+space $L_2(\reel^s)$.  The link between the approximation properties
+of $\varphi$ and those of its periodized version $\varphi_p$ is
+established by the error kernel formulation introduced
+in~\SC{sec:periodicErrorKernel}. Since the same kernel can be used in
+both cases, henceforth, we shall reason about the approximation
+properties of the generator $\varphi$ as the same properties are also
+applicable to its periodized counterpart $\varphi_p$.
+
+In many approximation scenarios, one typically assumes a Dirac point sampling
+model, i.e. $\analysis{\varphi}(\vect{x}) = \delta(\vect{x})$.
+This prevents the direct realization of the minimum approximation scenario.
+Furthermore, for many functions encountered in practice, the power spectrum is
+concentrated around $\vect{\omega} = 0$. For such scenarios, one speaks of an
+\emph{asymptotically optimal} $k$-th order approximation scheme if the $L_2$
+error behaves as $O(h^k)$ where $k = \order{\lattice{L}}{\varphi}$. Our operator
+discretization approach is also based on these assumptions. Provided that $V \in
+W_2^k(\cube^s)$, our goal is to design suitable digital filters that yield
+$\appf{V}$ such that $\LLnorm{V - \appf{V}} = O(h^k)$. As discussed earlier
+in~\SC{sec:interpQuasiInterp}, the criterion that needs to be satisfied is
+$E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$.
+
 \subsection{Relationship to the Galerkin method}
+\label{sec:Galerkin}
+The modified residue error kernel~\eqref{eq:opResidue} can also be analyzed in
+light of the Galerkin method~\cite{quarteroni08} using a weak formulation of the Poisson
+equation~\eqref{eq:PoissonEquation}, where the trial and test spaces are the
+same with the notable difference that the spaces are not required to explicitly
+satisfy any particular boundary conditions. Rather, a zero boundary condition is
+implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be
+odd as explained in~\SC{sec:approximateSolution}. Here, we establish the
+connection for the homogeneous case but the analysis also easily extends to the
+non-homogeneous case, as well as to other types of differential operators.
+
+In its weak form, the solution $V \in L_2(\cube^s)$ to the homogeneous
+Poisson equation~\eqref{eq:PoissonEquation} satisfies the weak
+formulation
+\begin{equation}
+  \innerproduct{V}{u} = \mathcal{F}(u), \;\; \forall u \in L_2(\cube^s),
+\end{equation}
+where the functions $u$ are suitable test functions. The functional
+$\mathcal{F}(\cdot)$ is defined as $\mathcal{F}(u) :=
+\innerproduct{\invlaplacian f}{u}$, where $f$ is the odd extension of
+the function that appears on the right hand side
+of~\eqref{eq:PoissonEquation}, and the operator
+$\stpairs{\invlaplacian}{\tfrac{1}{-\pi^2\norm{\vect{m}}^2}}$ has the
+interpretation of the inverse Laplacian as introduced
+in~\eqref{eq:fourierSolution}. We remark that this formulation is
+slightly stronger than the usual weak formulations based on the
+Laplacian $\laplacian$ where the trial and test spaces coincide with
+the Sobolev space $W_2^1(\cube^s)$. In comparison, here the trial and
+test spaces coincide with the more general space $L_2(\cube^s)$. This
+formulation is also in direct correspondence with our earlier
+treatment of the problem.
+
+Let us now restrict attention to the finite dimensional space
+$\aspace{\lattice{L}_h}{\varphi_p} \subset L_2(\cube^s)$. We seek a
+weak solution $\appf{V} \in \aspace{\lattice{L}_h}{\varphi_p}$ so that
+\begin{equation}
+  \innerproduct{\appf{V}}{u_h} = \mathcal{F}(u_h), \;\;
+  \forall u_h \in \aspace{\lattice{L}_h}{\varphi_p},
+\end{equation}
+and the Galerkin residual satifies the orthogonality condition
+\begin{equation}
+  \innerproduct{V - \appf{V}}{u_h} = 0, \;\;
+  \forall u_h \in \aspace{\lattice{L}_h}{\varphi_p}.
+  \label{eq:GalerkinOrthogonality}
+\end{equation}
+From this, it can be deduced that the minimum error approximation
+$\appf{V}$ is the orthogonal projection of $V$ upon
+$\aspace{\lattice{L}_h}{\varphi_p}$. The coefficients of the
+approximation are thus given by
+\begin{equation}
+  \begin{split}
+    c[\vect{x}_j] & = \mathcal{F}(h^{-s}
+    \dual{\varphi}(\frac{\vect{x}-\vect{x}_j}{h})) \\
+    & = 
+    \innerproduct{f(\vect{x})}{\invlaplacian(h^{-s}\dual{\varphi}(\frac{\vect{x}-\vect{x}_j}{h}))}.
+  \end{split}
+\end{equation}
+
+Observe that if we use the analysis function $\analysis{\varphi}_p =
+\invlaplacian \dual{\varphi}_p$ (in a distributional sense) in the
+measurement equation~\eqref{eq:measurements}, and subsequently employ
+no filtering (i.e. $\gamma[\vect{x}_j] = \delta[\vect{x}_j]$
+in~\eqref{eq:opApproximation}), then the measurements obtained will realize the orthogonal projection of $V$
+upon $\aspace{\lattice{L}_h}{\varphi_p}$. In this case, the modified Fourier
+residue error kernel~\eqref{eq:opResidue} vanishes,
+i.e. $E_{\mathsf{mod}}(\vect{\omega}) = 0$.
+
+On the other hand, if the point samples of $f$ are already available
+(i.e. $\analysis{\varphi} = \delta$) and the orthogonal projection
+cannot be realized, then the goal of the asymptotically optimal
+procedure is to find a suitable correction filter $\gamma$ such that
+$E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ where
+$k = \order{\lattice{L}}{\varphi}$.  
+%If we define the analysis function
+%$\phi(\vect{x}) := \sum_{\vect{k} \in \ints^s} t[\vect{x}]
+%\delta(\vect{k} - \mat{L}\vect{k})$, then the criterion
+%$E_{\mathsf{res}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ is
+%equivalent to the requirement that the moments of $\phi$ and
+%$\invlaplacian \dual{\varphi}$ (here
+%$\ftpairs{\invlaplacian}{(-4\pi^2\norm{\vect{\omega}}^2)^{-1}}$) match
+%up to the order $k$, i.e.  $\int_{\reel^s}
+%\vect{x}^{\vect{\mu}}(\phi(\vect{x}) - \invlaplacian
+%\dual{\varphi}(\vect{x})) d\vect{x} = 0$ for $0 \le \abs{\vect{\mu}} <
+%k$. 
+In other words, our approximation procedure attempts to reproduce the
+Galerkin orthogonality condition given
+by~\eqref{eq:GalerkinOrthogonality}. This is akin to the
+quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
+in~\SC{sec:interpQuasiInterp}.

### 2015-03-08 figures/3D/results.m

@@ -1,0 +1,111 @@
+%% The scale
+NCC = [16 32 64 128 256 512];
+
+for i = 1:numel(NCC)
+    hlabel{i} = num2str(1/(NCC(i)+1), '%10.2e');
+end
+    
+
+
+% Number of BCC samples are determined so that CC and BCC have roughly the
+% same number of samples
+NBCC = floor((1 + NCC) ./ 2^(1/3));
+
+% Cube root of Number of interior BCC samples
+NBint = (NBCC.^3 + (NBCC-1).^3).^(1/3);
+
+
+
+%% All the extracted data
+% CC Results
+
+ccLinearL2 = [1.798246E+01, 2.739709E-01, 5.081497E-02, 1.210899E-02, 2.995014E-03, 7.494486E-04];
+ccLinearLinf = [2.852765E+01, 1.734704E+00, 2.728010E-01, 6.142977E-02, 1.490395E-02, 3.766861E-03];
+
+ccNnL2 = [1.827384E+01, 6.879408E-01, 2.656328E-01, 1.259476E-01, 6.237209E-02, 3.120521E-02];
+ccNnLinf = [3.001269E+01, 3.060601E+00, 1.026051E+00, 5.076488E-01, 2.535835E-01, 1.288413E-01];
+
+ccCubicL2 = [1.816727E+01, 1.876446E-01, 1.114738E-02, 8.801522E-04, 5.888934E-05, 3.789409E-06];
+ccCubicLinf = [2.918992E+01, 1.098612E+00, 7.470030E-02, 5.309981E-03, 3.633388E-04, 2.328647E-05];
+
+ccQcubicL2 = [1.816755E+01, 1.793499E-01, 4.965959E-03, 1.503652E-04, 6.630578E-06, 3.944909E-07];
+ccQcubicLinf = [2.919649E+01, 9.890588E-01, 4.574515E-02, 1.391657E-03, 5.928562E-05, 3.215544E-06];
+
+% BCC results
+
+bccLinearL2 = [1.953174E+00, 1.980518E-01, 4.417511E-02, 1.065992E-02, 2.670024E-03, 6.620786E-04];
+bccLinearLinf = [7.502254E+00, 1.666201E+00, 4.362832E-01, 1.139844E-01, 2.817720E-02, 7.015853E-03];
+
[…]

### 2015-03-08 figures/pouints.m

@@ -1,0 +1,84 @@
+%% For the 2D Cartesian grid
+
+N = 7;
+[xi yi] = meshgrid(1/(N+1):1/(N+1):1-1/(N+1));
+
+figure
+
+interior = [xi(:)'; yi(:)'];
+interior = union(interior', [-xi(:)' -xi(:)' xi(:)'; yi(:)' -yi(:)' -yi(:)']', 'rows' )';
+scatter(interior(1,:), interior(2,:), 'o', 'MarkerFaceColor', [0 0 0], 'MarkerEdgeColor', [0 0 0] );
+
+bottom = [0:1/(N+1):1; zeros(1,N+2)]';
+left = fliplr(bottom);
+top = [0:1/(N+1):1; ones(1,N+2)]';
+right = fliplr(top);
+
+bdry = union(union(union(bottom,left, 'rows'), top, 'rows'),right, 'rows')';
+
+% The extended boundary points.
+bdry = union(union(bdry',-left(2:end-1,:), 'rows'), -bottom(2:end-1,:), 'rows')';
+bdry= union(union(bdry', [-top(2:end-1,1) top(2:end-1,2)], 'rows'),...
+    [right(2:end-1,1) -right(2:end-1,2)], 'rows' )';
+
+hold on, scatter(bdry(1,:), bdry(2,:), 'o', 'MarkerEdgeColor', [0 0 0] );
+
+
+
+% Draw the squares
+cube = patch([-1 1 1 -1], [-1 -1 1 1], 'k', 'FaceColor', 'none', 'LineWidth',1, 'LineStyle', '--');
+ucube = patch([0 1 1 0], [0 0 1 1], 'k', 'FaceColor', 'none', 'LineWidth',1, 'LineStyle', '-');
+axis off
+axis equal
+
+% Annotations
+%Annotate the point (1,1) and (-1,-1)
+text(1,1,'   (1,1)','HorizontalAlignment','left', 'VerticalAlignment','bottom');
+text(-1,-1,'(-1,-1)','HorizontalAlignment','right','VerticalAlignment','top');
+
+
+%% 2D quincunx grid
+
+M = floor(0.5 + 0.25*sqrt(-4 + 8*(N+2)^2));
+h = 1/(M-1);
+
+figure
+
+bottom = [0:h:1; zeros(1,M)]';
+left = fliplr(bottom);
+top = [0:h:1; ones(1,M)]';
+right = fliplr(top);
+
+
+% Boundary points
[…]

### 2015-04-08 approach.tex
Bringing everything up to date

@@
 We then apply FIR filters to the coefficients of the approximation to construct a scalar field representing the approximate divergence of the smoothed normal field (\FG{fig:pipeline}c.) We then use an appropriate discretization of the inverse Laplacian operator to solve the Poisson equation \EQ{eq:poisson}, and obtain a smooth function that approximates the original indicator function (\FG{fig:pipeline}c).
-Our code will is also available for download
+Our code is also freely available for download.
 
@@
 \begin{equation} 
-	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_k^i \varphi_k^i(\vx) \in \fspce{\varphi^i}{h\mathbf{L}}.
+	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_ki \varphi_k^i(\vx) \in \aspace{\lattice{L}{\varphi^i}}.
 \end{equation}}
-The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$.
-We consider each component of $\vec{V}(\vx)$ separately, thus, it suffices to only look at one $\upsilon_i$.
+The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$.We use the unfortunate notation $\text{v}_j^i, \varphi_k^i$ to denote that those objects belong to $\upsilon_i(x)$, not to denote exponentiation.
+We consider each component of $\vec{V}(\vx)$ separately, thus, it suffices to describe the process at one $\upsilon_i$.
 We simply find the $\upsilon_i$ that minimizes {\small
@@
 Where $(\mathbf{L}^{-1})_i$ is the $i^{th}$ column of $(\mathbf{L}^{-1}).$ As before, this provides us with a parametrized way of controlling the smoothness of the resulting approximation, without the need to explicitly choose a smoothing kernel.
-
-%In what follows, $\mathbf{L}$ is chosen to be the canonical basis $\mathbf{I_3}$ for the Cartesian lattice, whereas for the BCC lattice, we choose $\mathbf{L = L}_B$.
+These $\mathbf{v}_i$ can be obtained using the procedure of \SC{sec:vari_review}.
 
@@
 A simple way to obtain the divergence of $\vec{V}(\vx)$ is to consider its analytical partial derivatives which, due to the linearity of the expression, requires one to only take the analytic partial derivatives of the underlying kernel functions.
-However, this reduces the smoothness of the solution \cite{zahgrad}.
-There is also no conclusive evidence that suggests the analytic derivative of the kernel provides a better approximation to true underlying derivative.
+However, this reduces the smoothness of the solution \cite{zahgrad}, and there is also no conclusive evidence that suggests the analytic derivative of the kernel provides a better approximation to true underlying derivative.
 With this in mind, we choose to take a discrete filtering approach and approximate the divergence of $\vec{V}$ with a set of discrete FIR filters.
@@
 \subsubsection{Spaces Spanned by a Single Generating Function}
-When each space is identical (when $\upsilon_i \in \fspce{\varphi}{L}$) the divergence can be found by taking directional derivatives of $\vec{V}$ along the vectors in $\mathbf{L}$ as follows: {\small
+When each space is identical (when $\upsilon_i \in \aspace{\lattice{L}_h}{\varphi}$) the divergence can be found by taking directional derivatives of $\vec{V}$ along the vectors in $\mathbf{L}$ as follows: {\small
 \begin{eqnarray}\label{eq:div_dir}

### 2015-04-08 indicator.tex
Bringing everything up to date

--- 2015-02-15 indicator.tex
@@
 \section{Recovering the Indicator}
+
 \label{sec:recoveringX}
-Once the divergence of the smoothed vector field has been computed, the remaining step is to find a function that satisfies equation \EQ{eq:poisson}.
+Returning to the surface reconstruction approach, once the divergence of the smoothed vector field has been computed, the remaining step is to find a function that satisfies equation \EQ{eq:poisson}.
 As with the computation of a function's derivative, we also seek a filtering solution for the inverse of the Laplacian.
@@
 Whereas the DST on the Cartesian lattice is well-defined, on the BCC lattice, we utilize a  modified DST that can be efficiently implemented via 1D DSTs~\cite{bccdst}.
-The particular filter $l$ used in our experiments can be found in \TA{tab:filters}.
+%The particular filter $l$ used in our experiments can be found in \TA{tab:filters}.
 
@@
 However, the constant scaling factor of equation \EQ{eq:vdef} offsets the appropriate level set at which to threshold the indicator function.
-A common approach that has shown to be quite robust in this situation \cite{fftk}, is to average the levelset obtained by evaluating the approximation at the input points $\frac{1}{|P|}\sum_{(\vx,\vn)\in P}{\tilde{\chi}(\vx)}.$ The reasoning for this, is that the iso-value at the input data should be on, or at least near the surface of the model.
-Once the iso-surface has been determined, the mesh is extracted via marching cubes, with the step density set to half the lattice scaling factor ($frac{h}{2}$) \cite{}
+A common approach that has shown to be quite robust in this situation \cite{fftk}, is to average the levelset obtained by evaluating the approximation at the input points ${1}/{|P|}\sum_{(\vx,\vn)\in P}{\tilde{\chi}(\vx)}.$ The reasoning for this, is that the iso-value at the input data should be on, or at least near the surface of the model.
+Once the iso-surface has been determined, the mesh is extracted via marching cubes, with the step density set to half the lattice scaling factor ($\frac{h}{2}$) % \cite{}

### 2015-04-08 poisson_errker.tex
Bringing everything up to date

@@
 \section{Poisson's Equation} 
-We seek an approximation of the function $V$ that satisfies the Poisson equation with homogeneous Dirichlet boundary conditions, i.e. 
+Before detailing how to specifically obtain an indicator function from the divergence of $\vec{V}(\vect{x})$, we discuss a general framework for solving Poisson's equation on a rectangular domain.
+We provide an analysis in $s$-dimensions, as this generalization comes at little cost.
+Explicitly, we seek an approximation of the function $\chi(\vect{x})$ that satisfies the Poisson equation with homogeneous Dirichlet boundary conditions, i.e.
 \begin{equation} \label{eq:PoissonEquation}
 	\begin{split}
-		\laplacian{V} &= f, \;\; \text{in} \;\; \oucube^s, \\
-		V &= 0, \;\; \text{on} \;\; \partial \ucube^s,
+		\laplacian{\chi} &= f, \;\; \text{in} \;\; \oucube^s, \\
+		\chi &= 0, \;\; \text{on} \;\; \partial \ucube^s,
 	\end{split}
@@
 \end{equation}
-and the solution $V$ is given by
+and the solution $\chi$ is given by
 \begin{equation}
-	V(\vect{x}) = \int_{\ucube^s}f(\vect{y})\mathsf{G}(\vect{x},\vect{y}) d\vect{y}.
+	\chi(\vect{x}) = \int_{\ucube^s}f(\vect{y})\mathsf{G}(\vect{x},\vect{y}) d\vect{y}.
 	\label{eq:analytic}
@@
 
-Suppose we are given an $L_2(\ucube^s)$ function $\rho(x)$ that is
+Suppose we are given an $L_2(\ucube^s)$ function $\rho(
+\vect{x})$ that is
 defined on the open unit cube $\oucube^s$. In order to obtain a
@@
 \begin{equation}
-  \pointset{P}_h := \underbrace{\{\vect{x}_1,\ldots,\vect{x}_{2^sN} \}}_{\pointset{I}_h}
+  \pointset{T}_h := \underbrace{\{\vect{x}_1,\ldots,\vect{x}_{2^sN} \}}_{\pointset{I}_h}
   \cup
@@
 that the lattice $\lattice{L}$ and the sampling rate $h$ are such that
-the set $\{\vect{x} + 2\vect{m} : \vect{x} \in \pointset{P}_h,
+the set $\{\vect{x} + 2\vect{m} : \vect{x} \in \pointset{T}_h,
 \vect{m} \in \ints^s\} = \lattice{L}_h$. We remark that this
@@
   \caption[Interior and boundary samples]{Illustration of the point set
-  $\pointset{P}_h$ on the two
+  $\pointset{T}_h$ on the two
     dimensional Cartesian ($\mat{L} = \bigl( \begin{smallmatrix} 1&0\\
@@
 where $\appf{V}$ lies in the space $\aspace{\lattice{L}_h}{\varphi_p} :=
-\mathrm{span}_{\vect{x}_j\in\pointset{P}_h}\{
+\mathrm{span}_{\vect{x}_j\in\pointset{T}_h}\{
 \varphi_p(\frac{\vect{x}-\vect{x}_j}{h}) \}$ that is spanned by the scaled and
@@
 \begin{equation}
-  \appf{V}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{P}_h} c[\vect{x}_j] 
+  \appf{V}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{T}_h} c[\vect{x}_j] 
 \varphi_p\bigl(\frac{\vect{x} - \vect{x}_j}{h}\bigr),
@@
 where $c[\vect{x}_j]$ is an unknown coefficient sequence defined on
-the point set $\pointset{P}_h$ that is to be determined from the
+the point set $\pointset{T}_h$ that is to be determined from the
 samples of $f$. The function
@@
 $\cube^s$-periodic. Additionally, suppose that the measurements are made at the
-locations $\vect{x}_j \in \pointset{P}_h$ so that one can obtain an
+locations $\vect{x}_j \in \pointset{T}_h$ so that one can obtain an
 approximation $\appf{z}$ that belongs to  $\aspace{\lattice{L}_h}{\varphi_p}$
@@
 $
-  \appf{z}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{P}_h}
+  \appf{z}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{T}_h}
   \zeta[\vect{x}_j] \varphi_p(\frac{\vect{x}-\vect{x}_j}{h}),
@@
 \begin{equation}
-\appf{(\Gamma z)}(\vect{x}) = C_h \sum_{\vect{x}_j \in \pointset{P}_h} 
+\appf{(\Gamma z)}(\vect{x}) = C_h \sum_{\vect{x}_j \in \pointset{T}_h} 
 (\zeta \pconv \gamma_h)[\vect{x}_j]
@@
   (\zeta \pconv \gamma_h)[\vect{x}_j] :=
-  \sum_{\vect{x}_k \in \pointset{P}_h}
+  \sum_{\vect{x}_k \in \pointset{T}_h}
   \bigl(

### 2015-04-08 prelim.tex
Bringing everything up to date

@@
 \end{cases}. $$
-Integral to formulating surface reconstruction as a Poisson problem, is the observation that if one obtains some function $\vec{V}(\mathbf{x})\approx{\nabla}\chi_M$ that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small
+The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\mathbf{x})$ with $\vec{V}(\mathbf{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small
 \begin{equation} \label{eq:poisson}
@@
 \end{equation}}
-Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $\Phii_{i,j} := \varphi_j(\vx_i)$.
+Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $P_{i,j} := \varphi_j(\vx_i)$.
 Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites and we must consider alternative schemes for finding $\mathbf{c}$, which we'll come back to in \SC{sec:vari_review}
@@
 
-In order to ensure that any function $g \in \aspace{\lattice{L}}{\varphi}$ has a unique representation in terms of a finite energy coefficient sequence $c[\cdot]$, the lattice translates $\{\varphi(\cdot - \mat{L}\vect{n})\}_{\vect{n}  \in \ints^s}$ must form a Riesz basis~\cite{kreyszig89}, i.e.
+In order to ensure that any function $g \in \aspace{\lattice{L}_h}{\varphi}$ has a unique representation in terms of a finite energy coefficient sequence $c[\cdot]$, the lattice translates $\{\varphi(\cdot - \mat{L}\vect{n})\}_{\vect{n}  \in \ints^s}$ must form a Riesz basis~\cite{kreyszig89}, i.e.
 there exist positive constants $a$ and $b$ such that $\forall c[\cdot] \in l_2(\ints^s)$,
@@
 When this is the case, the minimum-error approximation is unattainable.
-However, interpolative and quasi-interpolative methods \cite{quasibcc,interprev}, which can be seen as oblique projections onto $\fspce{\varphi}{h\mathbf{L}}$, maintain the same order of accuracy.
+However, interpolative and quasi-interpolative methods \cite{quasibcc,interprev}, which can be seen as oblique projections onto $\aspace{\lattice{L}_h}{\varphi}$, maintain the same order of accuracy.
 
@@
 \subsection{Box Splines} \label{sec:box_review}
-Box splines are compact piece-wise polynomial functions $ M_\mathbf{\Xii} : \realn^s \to \realn.$ The matrix $\mathbf{\Xii}$ denotes a collection of direction vectors, $\mathbf{\Xii} := \left[ \xi_1 \ \xi_2 \hdots \xi_n\right].$ When $n=s$, the function $M_\mathbf{\Xii}(\vx)$ is defined to be $\frac{1}{det|\mathbf{\Xii}|}$ inside the polytope formed by the Minkowski sum of the direction vectors of $\mathbf{\Xii}$, and zero otherwise (that is, $\frac{1}{det|\mathbf{\Xii}|}$ when $\vx \in \{ \mathbf{\xi}_1 t_1 + \hdots + \mathbf{\xi}_s t_s  : t_i\in [0,1) \})$.
+Box splines are compact piece-wise polynomial functions $ M_\mathbf{\Xii} : \realn^s \to \realn.$ The matrix $\mathbf{\Xii}$ denotes a collection of direction vectors, $\mathbf{\Xii} := \left[ \xi_1 \ \xi_2 \hdots \xi_n\right].$ When $n=s$, the function $M_\mathbf{\Xii}(\vx)$ is defined to be ${1}/|{\det\mathbf{\Xii}}|$ inside the polytope formed by the Minkowski sum of the direction vectors of $\mathbf{\Xii}$, and zero otherwise (that is, ${1}/{|\det\mathbf{\Xii}|}$ when $\vx \in \{ \mathbf{\xi}_1 t_1 + \hdots + \mathbf{\xi}_s t_s  : t_i\in [0,1) \})$.
 When $n > s$, the box spline is recursively defined as {\small
@@
 \end{equation}}
-where $\!M_{\mathbf{\Xii/\xi}_n}$ is the matrix obtained by removing the column vector $\xi_n$ from $\mathbf{\Xii}$.
+where ${\mathbf{\Xii/\xi}_n}$ is the matrix obtained by removing the column vector $\xi_n$ from $\mathbf{\Xii}$.
 Box splines are a natural fit for our purposes, and are chosen to span our function spaces.
@@
 In the work by Kazdhan et al.
-\cite{fftk} the range data are splatted via a linear filter onto a regular Cartesian grid.
+\cite{fftk} the range data, $P$, are splatted via a linear filter onto a regular Cartesian grid.
 This tends to over-smooth the resulting reconstruction, as it allows the surface to deviate from the original sample locations.
@@
 There are similar works that impose variational constraints on random point samples for images \cite{variational}, as well as multi-resolution techniques for volumetric data \cite{onvari} and an extension to box spline spaces \cite{xu2012rec}.
-In the same vein, we seek a function $g \in \fspce{\varphi}{h\mathbf{L}}$ that attempts to interpolate the input data, and minimize a functional $E$.
+In the same vein, we seek a function $g \in \aspace{\lattice{L}_h}{\varphi}$ that attempts to interpolate the input data, and minimize a functional $E$.
 Specifically, we seek a $g$ that minimizes {\small
@@
 Finding $g$ that minimizes equation \EQ{eq:minexp} involves rewriting the minimization problem in terms of $\mathbf{c}$ \cite{xu2012rec}.
-Following some straightforward algebraic manipulations (see \cite{xu2012rec} for details), the coefficient vector can be obtained by taking $\mathbf{c} = ( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S})^{-1}\mathbf{\Phii}^T\mathbf{f}$, where $G_{i,j}:=\innerp{\varphi_i}{\varphi_j}$ and $S_{i,j}:=\blip{2}{\varphi_i}{\varphi_j}$.
-Since $\varphi$ is known in closed form, the entries of both $\mathbf{G}$ and $\mathbf{S}$ can be evaluated analytically.
-The above vector equation can be efficiently solved using the Conjugate Gradient method.
-%\begin{equation}
-%	\mathbf{c} = \left( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S}\right)^{-1}\mathbf{\Phii}^T\mathbf{f},
-%\label{eq:variationalSolution}
-%\end{equation}
+Following some straightforward algebraic manipulations (see \cite{xu2012rec} for details), the coefficient vector can be obtained by taking $\mathbf{c} = ( \mathbf{\Phii}^T\mathbf{\Phii} + \lambda_1\mathbf{G} + \lambda_2\mathbf{S})^{-1}\mathbf{\Phii}^T\mathbf{f}$, where $G_{i,j}:=\innerp{\varphi_i}{\varphi_j}$, $S_{i,j}:=\blip{2}{\varphi_i}{\varphi_j}$, and $P_{i,j} := \varphi_j(\vx_i)$ as before.
+Since $\varphi$ is known in closed form in our test cases, the entries of both $\mathbf{G}$ and $\mathbf{S}$ can be evaluated analytically.
+The above vector equation can be solved using the Conjugate Gradient method.

### 2015-04-08 results.tex
Bringing everything up to date

@@
 \section{Experiments}
+To test our methodology, we choose comparable basis functions on both the Cartesian and BCC lattices.
+These functions are comparable in that they both provide the same approximation order and smoothness.
 
@@
 It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions.
-Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ I_3  \ I_3 \ I_3  \ I_3 \right]}$.
+Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ \Xii_{C2} \ \Xii_{C2} \right]}$.
 A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$.
 We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$.
+Due to the smoothness requirements of the optimization constraint, we only considered the spline $M_{\Xii_{C4}}$.
 
 \subsubsection{Filter weights}
+This is where we derive filter weights for the experiments.
 
@@
 However, there exist both an efficient piecewise polynomial representation \cite{practicalbox}, and an efficient implementation \cite{fastbox} of these piecewise quintic polynomial functions.
+Again, due to the smoothness requirements of the optimization constraint, we only considered the spline $M_{\Xii_{B2}}$.
 

### 2015-04-09 results.tex
Adding filter design section

@@
 \subsection{Cartesian Lattice}
-Blurb about cartesian lattices.
-
 \subsubsection{Basis function}
@@
 
-\subsubsection{Filter weights}
-This is where we derive filter weights for the experiments.
+\subsubsection{Filter Design}
+Extending the filter in table 1
 
 \subsection{BCC Lattice}
-Blurb about cartesian lattices.
-
 \subsubsection{Basis function}
@@
 
-\subsubsection{Filter weights}
+\subsubsection{Filter Design}
+\label{sec:poissonFilterDesign}
+
+We now turn to the problem of designing filters that discretize the operator
+$\ftpairs{\invlaplacian}{(-4\pi^2(\omega_1^2 +
+  \omega_2^2))^{-1}}$, and
+are to be used in conjunction with the tensor-product B-splines. Recall that the
+space $\aspace{\ints^2_h}{\tpbs^k}$ generated by $\tpbs^k(x_1,x_2) =
+\cbs^{k}(x_1)\cbs^{k}(x_2)$ (where $\cbs^k$ is as defined
+in~\EQ{eq:1DBspline}), satisfies the approximation property:
+$\order{\ints^2}{\tpbs^k}=k+1$. This result also extends to the Cartesian lattice in
+higher dimensions. Consequently, we cover the 2D case in detail here. The
+extension to 3D is left to the reader.
+
+\paragraph{Interpolation}
+For the generator $\tpbs^k$, we are interested in a $(k+1)$-th order
+asymptotically optimal discretization of the inverse Laplacian
+$\invlaplacian$. According to Proposition~\ref{prop:1}, we need the
+two filters $p_{\tpbs^k}$ and $\lambda$.
+
+Since $\tpbs^k$ is a compact generator, $p_{\tpbs^k}$ will also be a compact
+filter. Furthermore, since $\tpbs^k$ is separable, $p_{\tpbs^k}$ can be
+determined by sampling $\cbs^k(x)$ to yield the filter $p_{\cbs^k}[n] =
+\cbs^k(n)$ where $n \in \ints$. The weights of $p_{\tpbs^k}$ are then obtained
+by a simple tensor product, i.e. $p_{\tpbs^k}[n_1,n_2] =
+p_{\cbs^k}[n_1]p_{\cbs^k}[n_2] \ftpairs{}{} \ft{P}_{\tpbs^k}(\omega_1,\omega_2)
+= \ft{P}_{\cbs^k}(\omega_1)\ft{P}_{\cbs^k}(\omega_2)$.
+
+As for the filter $\lambda$ that discretizes $\laplacian$, we follow a
+similar approach and first look for a symmetric and compact 1D filter
+$\lambda_1$ that satisfies the 1D analog of~\eqref{eq:opCriterionHomo},
+i.e. $\ft{\Lambda}_1(\omega) = -4\pi^2\omega^2 + O(\omega^{k+3})$. The
+unknown filter weights are determined by requiring that the Taylor
+developments of $(\ft{\Lambda}_1(\omega) + 4\pi^2\omega^2)$ be zero up to
+$\omega^{k+3}$. The filter $\ftpairs{\lambda}{\ft{\Lambda}}$ is then given by a
+simple addition, i.e. $\ft{\Lambda}(\omega_1,\omega_2) =
+\ft{\Lambda}_1(\omega_1) + \ft{\Lambda}_1(\omega_2)$.
+
+The sizes of $p_{\cbs^k}$ and $\lambda_1$ obviously depend on the degree
+$k$. The filters used in our experiments are tabulated in
+Table~\ref{tab:filters}.
+
+\begin{table*}[t!]
+  \footnotesize
+  \caption[Poisson filters for the Cartesian lattice]{The various 1D filters to
+  be used in conjunction with bilinear and bicubic approximation.}
+  \label{tab:filters}
+  \centering
+  \begin{tabular}{cc|cc}
+    \toprule
+     & $\aspace{\ints^2_h}{\tpbs^1}$ & \multicolumn{2}{c}{$\aspace{\ints^2_h}{\tpbs^3}$}\\
+     & Interp. & Interp. & Quasi. ($l=5$)\\
+    \midrule
+    $p_{\cbs^k}[n]$ & $\delta_n$ & $[\tfrac{1}{6}\; \tfrac{2}{3}\; \tfrac{1}{6}]$& $[\tfrac{1}{120}\; \tfrac{13}{60}\; \tfrac{11}{20}\; \tfrac{13}{60}\; \tfrac{1}{120}]$\\
+    $\ft{P}_{\cbs^k}(\tfrac{\nu}{2\pi})$ & $1$ & $\tfrac{1}{3}(2 + \cos(\nu))$&
+    $\tfrac{1}{60}(33+26\cos(\nu) + \cos(2\nu))$\\
+    \midrule
+    $\lambda_1[n]$ & $[1\; {-2}\; 1]$ & $[\tfrac{-1}{12}\; \tfrac{4}{3}\;
+    \tfrac{-5}{2}\; \tfrac{4}{3}\; \tfrac{-1}{12}]$& $[\tfrac{1}{90}\; \tfrac{-3}{20}\; \tfrac{3}{2}\; \tfrac{-49}{18}\; \tfrac{3}{2}\; \tfrac{-3}{20}\; \tfrac{1}{90}]$\\
+    $\ft{\Lambda}_1(\tfrac{\nu}{2\pi})$ & $-2 + 2\cos(\nu)$&
+    $\tfrac{2}{3}(-7+\cos(\nu))\sin^2(\tfrac{\nu}{2})$& $\tfrac{2}{45}(-111 + 23\cos(\nu) - 2\cos(2\nu))\sin^2(\tfrac{\nu}{2})$\\
+    \midrule
+    $w_1[n]$ & & & $[\tfrac{1}{362880}\; \tfrac{251}{181440}\;
+    \tfrac{913}{22680}\; \tfrac{44117}{181440}\; \tfrac{15619}{36288}\; \cdots]$\\
+    $\ft{W}_1(\tfrac{\nu}{2\pi})$ & &
+    \multicolumn{2}{r}{$\scriptscriptstyle{\tfrac{1}{181440}(78095 + 88234\cos(\nu) + 14608\cos(2\nu) + 502\cos(3\nu)+ \cos(4\nu))}$}\\
+    & & & \\
+    $a_{\cbs^k}[n]$ & & & $[\tfrac{1}{5040}\; \tfrac{1}{42}\;
+    \tfrac{397}{1680}\; \tfrac{151}{315}\; \tfrac{397}{1680}\; \tfrac{1}{42}\; \tfrac{1}{5040}]$\\
+    $\ft{A}_{\cbs^k}(\tfrac{\nu}{2\pi})$ & & & $\scriptscriptstyle{\tfrac{1}{2520}(1208 + 1191\cos(\nu) + 120\cos(2\nu) + \cos(3\nu))}$\\
+    \bottomrule
+  \end{tabular}
+\end{table*}
+
+\paragraph{Quasi-Interpolation}
+For the quasi-interpolative model, we need the additional filter
+$q$~\eqref{eq:quasiWeights}. Choosing $\psi$ to be the tensor product
+B-spline $\tpbs^l$ where $l>k$, the weights of $q$ are given by the
+tensor product of the 1D filter $q_1[n] := (\cbs^l \ast
+\dual{\cbs}^k)(n)$ with itself. Using the recursive definition
+of the 1D B-splines, $q_1$ can be further split as $q_1[n]
+= (w_1 \ast a_{\cbs^k}^{-1})[n]$ where $w_1[n] := \cbs^{k+l+1}(n)$ and
+$\ftpairs{a_{\cbs^k}^{-1}[\cdot]}{\tfrac{1}{\ft{A}_{\cbs^k}(\cdot)}}$. Example
+filter weights for the case $l=5$ are provided in Table~\ref{tab:filters}.
+
+\subsubsection{BCC Lattice}
+It is convenient to introduce a scaled version of the BCC lattice
+$\lattice{H}$ generated by the matrix $\mat{H} =
+\sqrt[3]{4}\mat{B}$. With respect to $\lattice{H}$, we denote the
+order-$k$ ($k \in 2\ints_+$) rhombic-dodecahedral box spline as
+$\bccbs{k}(\vect{x}) :=
+\boxsp[k/2]{\mat{\Theta}}(\vect{x}/\sqrt[3]{4})$. Note that $k$ now
+refers to the approximation order of the box-spline rather than its
+polynomial degree.
+
+\paragraph{Interpolation}
+The operator we wish to discretize is
+$\ftpairs{\invlaplacian}{-4\pi^2(\omega_1^2 + \omega_2^2 + \omega_3^2)^{-1}}$.
+According to~Proposition~\ref{prop:1}, we need the combined filter
+$(p_{\bccbs{k}} \ast \lambda)$ where $\ftpairs{\lambda}{\ft{\Lambda}}$
+satisfies~\eqref{eq:discreteLaplacian}, i.e. $\ft{\Lambda}(\vect{\omega}) =
+-4\pi^2\norm{\vect{\omega}}^2 + O(\norm{\vect{\omega}}^{k+2})$. The compact
+filter $p_{\bccbs{k}}$ is non-separable and is determined by the samples of
+$\bccbs{k}$, i.e.
+$p_{\bccbs{k}}[\vect{x}_j] = \bccbs{k}(\vect{x}_j)$ where $\vect{x}_j \in
+\lattice{H}$.
+
+As for the filter $\lambda$, observe that
+\begin{equation}
+  \norm{\vect{\omega}}^2 = \frac{1}{4}\sum_{i=1}^4
+  (\vect{\theta}_i \cdot \vect{\omega})^2,
+\end{equation}
+where the (scaled) box spline direction vectors $\vect{\theta}_i$ ($i
+\in \{1,2,3,4\}$) correspond to the column vectors
+$\transp{(1,1,-1)}$, $\transp{(1,-1,1)}$, $\transp{(-1,1,1)}$ and
+$\transp{(-1,-1,-1)}$ respectively. Since $\vect{\theta}_i \in
+\lattice{H}$, we can re-use the 1D filter $\lambda_1[n]$ from the
+previous section and apply it across the directions $\vect{\theta}_i$
+to yield the filter $\lambda$.  Therefore,
+$\ftpairs{\lambda}{\ft{\Lambda}}$ is given by
+\begin{equation}
+  \ft{\Lambda}(\vect{\omega}) = \frac{1}{4}\sum_{i=1}^4
+  \ft{\Lambda}_1(\vect{\theta}_i \cdot \vect{\omega}),
+\end{equation}
+where the 1D filter $\ftpairs{\lambda_1}{\ft{\Lambda}_1}$ satisfies 
+$\ft{\Lambda}_1(\omega) = -4\pi^2\omega^2 + O(\omega^{k+2})$.
+
+Table~\ref{tab:filtersBCC} summarizes the various filters that are the
+BCC analogs of Cartesian filters listed in Table~\ref{tab:filters}.
+
+\begin{table*}[t]
+  \let\oldcos\cos	
+  \renewcommand\cos{\operatorname{c}}
+  \footnotesize
+  \caption[Poisson filters for the BCC lattice]{Filters to be used in
+  conjunction with the linear and quintic box splines on the BCC lattice.
+  $\cos(\theta)$ is short for $\oldcos(\theta)$.}
+  \label{tab:filtersBCC}
+  \centering
+  \begin{tabular}{lc|>{\raggedright}p{0.2\textwidth} p{0.4\textwidth}}
+    \toprule
+     & $\aspace{\lattice{H}_h}{\bccbs{2}}$ &
+     \multicolumn{2}{c}{$\aspace{\lattice{H}_h}{\bccbs{4}}$}\\
+     & Interp. & Interp. & Quasi. ($l=6$)\\
+    \midrule
+    $p_{\bccbs{k}}[\vect{y}]$ ($\vect{y} \in \lattice{H}$) & $\delta_{\vect{y}}$
+    & $\begin{cases}
+    	\tfrac{2}{5} & \text{if $\vect{y} = \vect{0}$},\\
+    	\tfrac{1}{20} & \text{if $\norm{\vect{y}} = \sqrt{3}$}, \\
+    	\tfrac{1}{30} & \text{if $\norm{\vect{y}} = 2$}, \\
+    	0 & \text{otherwise}
+    \end{cases}$
+    &
+    $\begin{cases}
+    \tfrac{379}{1680} & \text{if $\vect{y} = \vect{0}$},\\
+    	\tfrac{1177}{20160} & \text{if $\norm{\vect{y}} = \sqrt{3}$}, \\
+    	\tfrac{7}{180} & \text{if $\norm{\vect{y}} = 2$}, \\
+    	\tfrac{43}{10080} & \text{if $\norm{\vect{y}} = \sqrt{8}$},\\
+    	\tfrac{17}{20160} & \text{if $\norm{\vect{y}} = \sqrt{11}$},\\
+    	\tfrac{1}{4032} & \text{if $\norm{\vect{y}} = \sqrt{12}$},\\
+    	\tfrac{1}{10080} & \text{if $\norm{\vect{y}} = 4$},\\
+    	0 & \text{otherwise}
+    \end{cases}$ 
+    \\
+    $\ft{P}_{\bccbs{k}}(\tfrac{u}{2\pi},\tfrac{v}{2\pi},\tfrac{w}{2\pi})$
+    & $1$ & 
+    $\tfrac{1}{15}\bigl(6 + \cos(2u)+\cos(2v)+\cos(2w)$ 
+    $+ 6\cos(u)\cos(v)\cos(w) \bigr)$
+    &
+    $\tfrac{1}{5040}\Bigl(
+    2 \cos (u) \cos (v) \cos (w) \bigl[34 \cos (2 u)+34 \cos (2 v)+1143\bigr]$
+    $+2 \cos (2w) \bigl[\cos (2 u) \bigl( 5 \cos (2 v)+43\bigr)+43 \cos (2
+    v)+196\bigr]$ 
+    $+34 \cos(u) \cos (v) \cos (3 w)+43 \cos \bigl(2 (u-v) \bigr)+43 \cos
+    \bigl(2 (u+v)\bigr)$
+    $+392\cos (2 u)+\cos (4 u)+392 \cos (2 v)+\cos (4
+    v)+\cos (4 w)+1137 \Bigr)$
+    \\
+    \midrule
+    $\lambda_1[n]$ & \multicolumn{3}{c}{see Table~\ref{tab:filters}} \\
+    $\ft{\Lambda}_1(\tfrac{\nu}{2\pi})$ & \multicolumn{3}{c}{} \\
+    \midrule
+    $w_{\mathsf{b}}[\vect{y}]$ & N/A & N/A & see
+    supplementary material
+    \\
+    $\ft{W}_{\mathsf{b}}(\vect{\omega})$ & & &  \\
+    $a_{\bccbs{k}}[\vect{y}]$ & N/A & N/A & see
+    supplementary material
+    \\
+    $\ft{A}_{\bccbs{k}}(\vect{\omega})$ & & &\\
+    \bottomrule
+  \end{tabular}
+  \let\cos\oldcos
+\end{table*}
 

### 2015-04-12 introduction.tex
Cleaning up first two sections

@@
 The second advantage to moving to the BCC lattice is that there exist reconstruction filters on the BCC lattice that outperform commonly used filters of equivalent order on the CC lattice in terms of both speed and accuracy \cite{practicalbox} (in software implementations) -- these filters are also more compact than their typical CC counterparts.
-In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice and tend to provide faster convergence when optimizing the initial point set (\SC{sec:that-section-where-i-describe-this}.)
+In the context of our surface reconstruction scheme, this gives rise to regularization matrices that are more sparse on the BCC lattice and tend to provide faster convergence when optimizing the initial point set (\SC{sec:vari_review}).
 
@@
 
-Additionally, we consider the possibility of approximating the smoothed gradient field representation within function spaces that are
-spanned by shifted versions of a single generating kernel. In the context of gradient estimation, introducing a shift in the direction
-of the derivative has shown to improve overall gradient approximation fidelity in terms of gradient orientation and magnitude,
-as well as displaying the ability to capture higher frequency details that are smoothed out in non-shifted schemes~\cite{gradrev}.
+Additionally, we consider the possibility of approximating the smoothed gradient field representation within function spaces that are spanned by shifted versions of a single generating kernel.
+In the context of gradient estimation, introducing a shift in the direction of the derivative has shown to improve overall gradient approximation fidelity in terms of gradient orientation and magnitude, as well as displaying the ability to capture higher frequency details that are smoothed out in non-shifted schemes~\cite{gradrev}.
 Since the divergence operator is intimately connected to the gradient operator, these results are of interest to us.

### 2015-04-12 poisson_errker.tex
Cleaning up first two sections

@@
 \section{Poisson's Equation} 
-Before detailing how to specifically obtain an indicator function from the divergence of $\vec{V}(\vect{x})$, we discuss a general framework for solving Poisson's equation on a rectangular domain.
+Before detailing how to obtain an indicator function from the divergence of $\vec{V}(\vect{x})$, we discuss a general framework for solving Poisson's equation on a rectangular domain.
 We provide an analysis in $s$-dimensions, as this generalization comes at little cost.

### 2015-04-12 relatedwork.tex
Cleaning up first two sections

@@
 \section{Related Work}
-Surface reconstruction is still a very active area of research in computer 
-graphics and it's beyond the scope of this work to touch on all the material 
-related to the subject. We therefore very briefly review some relevant contributions -- 
-those seeking a more in-depth review may look to a recent survey of the field 
-\cite{reconstar_eg14}. We focus mainly on some of the more related and recent 
-developments.
+Surface reconstruction is still a very active area of research in computer graphics and it's beyond the scope of this work to touch on all the material related to the subject.
+We therefore very briefly review some relevant contributions -- those seeking a more in-depth review may look to a recent survey of the field \cite{reconstar_eg14}.
+We focus mainly on some of the more related and recent developments.
 
-Many surface reconstruction algorithms are so-called 
-``\emph{implicit}'' reconstruction algorithms. They attempt to 
-reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose 
-level-set, for some iso-value $s \in \realn$, $f(\mathbf{x})=s$ represents an
-approximation to the original surface. Other non-implicit techniques
-generally infer meshes through some other combinatorial means 
-or set predefined logic/rules.
+Many surface reconstruction algorithms are so-called ``\emph{implicit}'' reconstruction algorithms. They attempt to 
+reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose level-set, for some iso-value $s \in \realn$, $f(\vect{x})=s$ represents an approximation to the original surface.
+Other non-implicit techniques generally infer meshes through some other combinatorial means or set predefined logic/rules.
 
-For example, there exist many Delaunay style algorithms in which a 
-triangulation is constructed using a subset of the original point-set 
-\cite{delaunay}. The Power Crust \cite{powercrust} and Cocone \cite{cocone} 
-algorithms are two other well-known techniques that do not construct 
-implicit functional representations. These techniques
-often aim to exactly interpolate the input point set, and in the presence of
-noise tend to over-fit the surface. When the input data are noisy
-implicit approaches often perform better than non-implicit algorithms, 
-as implicit algorithms inherently attempt to fit locally smooth basis 
-functions to the data, averaging out any noise. Reconstructing either 
-a distance function or an indicator function is common to these 
-approaches.
+For example, there exist many Delaunay style algorithms in which a triangulation is constructed using a subset of the original point-set \cite{delaunay}.
+The Power Crust \cite{powercrust} and Cocone \cite{cocone} algorithms are two other well-known techniques that do not construct implicit functional representations.
+These techniques often aim to exactly interpolate the input point set, and in the presence of noise tend to over-fit the surface.
+When the input data are noisy implicit approaches often perform better than non-implicit algorithms, as implicit algorithms inherently attempt to fit locally smooth basis functions to the data, averaging out any noise.
+Reconstructing either a distance function or an indicator function is common to these approaches.
 
-One of the most well known implicit algorithms is the algorithm of 
-by Hoppe et al.~\cite{hoppecut}. In this work a set of
-tangent planes is constructed to create an approximation to a
-surface's distance function. A more recent work, is the Smoothed
-Signed Distance Field reconstruction technique \cite{ssdrecon}, in
-which an oriented point set imposes constraints on the reconstructed
-function, its gradient, and its Hessian. These constraints are
-equvalent to requiring that the reconstructed function be an
-approximation to the distance field of the original model. Other
-techniques attempt to reconstruct a signed distance function within a
-function space spanned by radial basis functions \cite{radial}.
-Recently, there has also been research that incorporates point normals
-into the radial basis reconstruction framework \cite{hermite}. It's also
-possible to construct an implicit function as a normalize sum of 
-compactly supported basis functions defined over an oct-tree, 
-essentially ``smearing'' the point-set around space and constructing 
-an indicator ``shell'' around them \cite{Fuhrmann2014}.
+One of the most well known implicit algorithms is the algorithm of by Hoppe et al.~\cite{hoppecut}. In this work a set of
+tangent planes is constructed to create an approximation to a surface's distance function. A more recent work, is the Smoothed
+Signed Distance Field reconstruction technique \cite{ssdrecon}, in which an oriented point set imposes constraints on the reconstructed function, its gradient, and its Hessian.
+These constraints are equvalent to requiring that the reconstructed function be an approximation to the distance field of the original model.
+Other techniques attempt to reconstruct a signed distance function within a function space spanned by radial basis functions \cite{radial}.
+Recently, there has also been research that incorporates point normals into the radial basis reconstruction framework \cite{hermite}.
+It's also possible to construct an implicit function as a normalize sum of compactly supported basis functions defined over an oct-tree, essentially ``smearing'' the point-set around space and constructing an indicator ``shell'' around them \cite{Fuhrmann2014}.
 
-Another approach is to find an indicator function that approximates the
-``inside-outside'' function of original model. An early technique \cite{fftk} 
-transforms the smoothed gradient to the Fourier domain, applies an appropriate 
-operator, then reconstructs it in the spatial domain. This approach often deals well with
-incomplete, missing, or otherwise noisy data and has the guarantee of
-creating a water tight surface. However, it involves reconstructing
-the indicator on a regular grid, which becomes very memory intensive
-as the grid is refined.
+Another approach is to find an indicator function that approximates the ``inside-outside'' function of original model.
+An early technique \cite{fftk} transforms the smoothed gradient to the Fourier domain, applies an appropriate operator, then reconstructs it in the spatial domain.
+This approach often deals well with incomplete, missing, or otherwise noisy data and has the guarantee of creating a water tight surface.
+However, it involves reconstructing the indicator on a regular grid, which becomes very memory intensive as the grid is refined.
 
-Poisson surface reconstruction techniques make the observation that
-the Fourier method is equivalently stated as a spatial Poisson problem
-\cite{Kazhdan06,screenedk}. Moreover, they seek to rectify the memory
-limitations of that work, while still maintaining its benefits. However, 
-current techniques based on this idea have been shown to over-smooth 
-the initial point-set, and therefore the resulting surface. \cite{reconbench}.
+Poisson surface reconstruction techniques make the observation that the Fourier method is equivalently stated as a spatial Poisson problem \cite{Kazhdan06,screenedk}.
+Moreover, they seek to rectify the memory limitations of that work, while still maintaining its benefits.
+However, current techniques based on this idea have been shown to over-smooth the initial point-set, and therefore the resulting surface.
+\cite{reconbench}.
 
-It is also possible to reconstruct the indicator of a point set within
-a wavelet basis \cite{wavelet}. In this work, an approximate indicator
-function of the model is projected onto a compact wavelet basis. This
-leads to a simple and efficient algorithm even when the data sets
-are massive. However the method's speed comes at a price, as the
-resulting surfaces are often non-smooth, and display many ``jagged''
-artifacts (although a form of smoothing is applied to the resulting
-indicator function in an attempt to rectify this.)
+It is also possible to reconstruct the indicator of a point set within a wavelet basis \cite{wavelet}.
+In this work, an approximate indicator function of the model is projected onto a compact wavelet basis.
+This leads to a simple and efficient algorithm even when the data sets are massive.
+However the method's speed comes at a price, as the resulting surfaces are often non-smooth, and display many ``jagged'' artifacts (although a form of smoothing is applied to the resulting indicator function in an attempt to rectify this.)
 
-Outside of the context of surface reconstruction there has been considerable
-evidence that shows non-Cartesian approaches to volume rendering 
-\cite{firstbox, practicalbox, hvolrecon} and fluid flow \cite{lboltzman} outperform 
-Cartesian approaches in both speed and memory consumption. Additionally, 
-finite difference Laplacian stencils on non-Cartesian grids lead to reduced 
-numerical dispersion compared to their Cartesian  counterparts (see e.g. 
-\cite{hamilton2013, hamilton2013hexagonal} and references therein). It is 
-therefore natural to question whether these advantages can be exploited 
-within the context of surface reconstruction.
+Outside of the context of surface reconstruction there has been considerable evidence that shows non-Cartesian approaches to volume rendering \cite{firstbox, practicalbox, hvolrecon} and fluid flow \cite{lboltzman} outperform Cartesian approaches in both speed and memory consumption.
+Additionally, finite difference Laplacian stencils on non-Cartesian grids lead to reduced numerical dispersion compared to their Cartesian  counterparts (see e.g.
+\cite{hamilton2013, hamilton2013hexagonal} and references therein).
+It is therefore natural to question whether these advantages can be exploited within the context of surface reconstruction.
 
-Our approach aims to solve the Poisson surface reconstruction problem
-in the setting of general shift-invariant spaces. A crucial step in this
-regard is the accurate estimation of the divergence of the gradient
-field from the oriented point-set. Radial basis functions (RBFs) are
-generally used in the context of the reconstruction of scattered data, 
-however, RBF techniques are often computationally
-expensive, requiring the solution of large unstable systems of
-equations (for exact interpolation.) A proposed solution to this
-problem is to ``\emph{re-sample}'' the input data onto a regular
-shift-invariant space. This allows one to use efficient compact
-reconstruction kernels and data processing techniques
-\cite{variational,onvari}. Recently, an extension of this idea to box
-spline spaces \cite{xu2012rec} proposes a variational reconstruction
-framework in which the BCC lattice consistently outperforms the
-Cartesian lattice. Our method takes a similar variational approach and
-seeks to construct a smoothed lattice-based approximation of the
-gradient of the indicator function (\SC{sec:obtainingV}). Our employed
-constraints force the gradient to be close to zero away from the
-surface, while maintaining a certain degree of smoothness in the
-resulting approximation. This is preferable in comparison to other
-works \cite{fftk,Kazhdan06,screenedk} in which each sample is
-trilinearly distributed about either a grid or an oct-tree
-respectively, and is known to over-smooth data.
+Our approach aims to solve the Poisson surface reconstruction problem in the setting of general shift-invariant spaces.
+A crucial step in this regard is the accurate estimation of the divergence of the gradient field from the oriented point-set.
+Radial basis functions (RBFs) are generally used in the context of the reconstruction of scattered data, however, RBF techniques are often computationally expensive, requiring the solution of large unstable systems of equations (for exact interpolation.) A proposed solution to this problem is to ``\emph{re-sample}'' the input data onto a regular shift-invariant space.
+This allows one to use efficient compact reconstruction kernels and data processing techniques \cite{variational,onvari}.
+Recently, an extension of this idea to box spline spaces \cite{xu2012rec} proposes a variational reconstruction framework in which the BCC lattice consistently outperforms the Cartesian lattice.
+Our method takes a similar variational approach and seeks to construct a smoothed lattice-based approximation of the gradient of the indicator function (\SC{sec:obtainingV}).
+Our employed constraints force the gradient to be close to zero away from the surface, while maintaining a certain degree of smoothness in the resulting approximation.
+This is preferable in comparison to other works \cite{fftk,Kazhdan06,screenedk} in which each sample is trilinearly distributed about either a grid or an oct-tree respectively, and is known to over-smooth data.
 
-Having obtained a high-quality lattice-based approximation of the
-gradient field, we invoke the theory behind shift-invariant spaces
-and accurately estimate the divergence by applying derivative filters
-that are designed to harness the full approximation capabilities of
-the target space (\SC{sec:divergence}).
+Having obtained a high-quality lattice-based approximation of the gradient field, we invoke the theory behind shift-invariant spaces and accurately estimate the divergence by applying derivative filters that are designed to harness the full approximation capabilities of the target space (\SC{sec:divergence}).
 
-Once, the smoothed gradient's divergence has been calculated, recovering the indicator
-function is a simple matter of taking the inverse of the Laplacian over domain 
-(i.e. solving the Poisson system). To do this, we take an approach that is also inspired 
-by filtering methodologies in signal processing. In particular, we're interested in 
-an approximate solution to Poisson?s equation that lies in a chosen shift-invariant 
-space. Our solution methodology is reminiscent of the finite 
-element method \cite{finite_el}. However, we do not impose any boundary 
-conditions on the generating kernels. Rather, we satisfy homogeneous 
-Dirichlet boundary conditions implicitly by requiring that the coefficient sequence be odd 
-(Section III). The solution is obtained by applying a digital filter to point samples. 
-We approach the problem from first principles and derive the tools necessary 
-to design solution filters for a chosen shift-invariant space (\SC{sec:recoveringX}).
-\ednote{I still need to fix-up section refs/refs here.}
+Once, the smoothed gradient's divergence has been calculated, recovering the indicator function is a simple matter of taking the inverse of the Laplacian over domain (i.e.
+solving the Poisson system).
+To do this, we take an approach that is also inspired by filtering methodologies in signal processing.
+In particular, we're interested in an approximate solution to Poisson?s equation that lies in a chosen shift-invariant space.
+Our solution methodology is reminiscent of the finite element method.
+However, we do not impose any boundary conditions on the generating kernels.
+Rather, we satisfy homogeneous Dirichlet boundary conditions implicitly by requiring that the coefficient sequence be odd (Section III).
+The solution is obtained by applying a digital filter to point samples.
+We approach the problem from first principles and derive the tools necessary to design solution filters for a chosen shift-invariant space (\SC{sec:recoveringX}).

### 2015-04-12 results.tex
Cleaning up first two sections

@@
 We now turn to the problem of designing filters that discretize the operator 
-$\ftpairs{\invlaplacian}{(-4\pi^2(\omega_1^2 +
-  \omega_2^2))^{-1}}$, and
-are to be used in conjunction with the tensor-product B-splines. Recall that the
-space $\aspace{\ints^2_h}{\tpbs^k}$ generated by $\tpbs^k(x_1,x_2) =
-\cbs^{k}(x_1)\cbs^{k}(x_2)$ (where $\cbs^k$ is as defined
-in~\EQ{eq:1DBspline}), satisfies the approximation property:
-$\order{\ints^2}{\tpbs^k}=k+1$. This result also extends to the Cartesian lattice in
-higher dimensions. Consequently, we cover the 2D case in detail here. The
-extension to 3D is left to the reader.
+$\ftpairs{\invlaplacian}{(-4\pi^2(\omega_1^2 +\omega_2^2))^{-1}}$, and are to be used in conjunction with the tensor-product B-splines.
+For the generator $M_{\Xii_{C4}}$, we are interested in a $4$-th order asymptotically optimal discretization of the inverse Laplacian $\invlaplacian$.
+According to Proposition~\ref{prop:1}, we need the two filters $p_{M_{\Xii_{C4}}}$ and $\lambda$.
 
-\paragraph{Interpolation}
-For the generator $\tpbs^k$, we are interested in a $(k+1)$-th order
-asymptotically optimal discretization of the inverse Laplacian
-$\invlaplacian$. According to Proposition~\ref{prop:1}, we need the
-two filters $p_{\tpbs^k}$ and $\lambda$.
-
-Since $\tpbs^k$ is a compact generator, $p_{\tpbs^k}$ will also be a compact
-filter. Furthermore, since $\tpbs^k$ is separable, $p_{\tpbs^k}$ can be
+Since $M_{\Xii_{C4}}$ is a compact generator, $p_{M_{\Xii_{C4}}^k}$ will also be a compact filter. Furthermore, since $\tpbs^k$ is separable, $p_{\tpbs^k}$ can be
 determined by sampling $\cbs^k(x)$ to yield the filter $p_{\cbs^k}[n] =
-\cbs^k(n)$ where $n \in \ints$. The weights of $p_{\tpbs^k}$ are then obtained
-by a simple tensor product, i.e. $p_{\tpbs^k}[n_1,n_2] =
-p_{\cbs^k}[n_1]p_{\cbs^k}[n_2] \ftpairs{}{} \ft{P}_{\tpbs^k}(\omega_1,\omega_2)
-= \ft{P}_{\cbs^k}(\omega_1)\ft{P}_{\cbs^k}(\omega_2)$.
+\cbs^k(n)$ where $n \in \ints$. The weights of $p_{M_{\Xii_{C4}}}$ are then obtained
+by a simple tensor product, i.e. $p_{M_{\Xii_{C4}}^k}[n_1,n_2,n_3] =
+p_{\cbs^k}[n_1]p_{\cbs^k}[n_2] \ftpairs{}{} \ft{P}_{\tpbs^k}(\omega_1,\omega_2,\omega_3) = \ft{P}_{\cbs^k}(\omega_1)\ft{P}_{\cbs^k}(\omega_2)\ft{P}_{\cbs^k}(\omega_3)$.
 

### 2015-04-12 abstract.tex
Adding updated (slightly) bib, adding updates to intro and related work.
Adding review and moving stuff.
Added Floating surface recon
Adding refs to optimal lattice stuff in 2d.
Cleaned up refs/sec refs/symbols up to approach.

@@
 The treatment is general, but our specific interest is in reconstructing a surface of a solid model from an oriented point-set within function spaces defined over the body centred cubic lattice.
-We also propose a general framework for approximating the solution to Poisson?s equation in a hypercube with zero Dirichlet boundary conditions, and a new variational scheme to re-sample the initial oriented point-set onto a regular grid.
+We also propose a general framework for approximating the solution to Poisson's equation in a hypercube with zero Dirichlet boundary conditions, and a new variational scheme to re-sample the initial oriented point-set onto a regular grid.
 Once the points have been re-sampled onto a grid, the rest of the pipeline is purely based on digital filtering.
@@
 
-%We analyze the error incurred via this approximation methodology and propose a Fourier domain error kernel that can be used to design solution filters that fully exploit the approximation capabilities of the target space and are akin to interpolation and quasi-interpolation filters.
+%%%%
+% Todo
+%%%%
 
-%Our error kernel formulation is validated by conducting numerical experiments on the two dimensional square lattice and the three dimensional Cartesian and body-centered cubic lattices.
-Additionally, we comment on the equivalence between our method and the finite element method and show how our error kernel formulation can be easily extended to a larger class of differential operators.
+%5. Indicator funcition:
+%Expand
 
-%1. Intro:
-%Highlight the additional contribution that we formulate a way to solve the Poisson equation on non-Cartesian lattices.
-
-%2. Related work:
-%Update references with the work Torsten pointed out and the recent surface reconstruction survey that I mentioned. 
-%Cite additional work that talks about the benefits of non-Cartsian lattices (in volume rendering, flow simulation etc.). 
-%There are a couple of works that deal with solving Poisson?s equation on non-Cartesian lattices. Please see the attached version of my paper.
-
-%3. Preliminaries:
-%Move sections 3.3.1 and 3.3.2 to section 6. Introduce 3.4 earlier.
-
-%4. Approach:
-%Expand 4.3 into a new section ? section 5. Move Table 1 to section 6.
-
-%5. Solving Poisson?s Equation.
+%6. Solving Poisson?s Equation.
 %This section spells out the details of the filtering methodology for solving Poisson?s equation.
@@
 
-%6. Results and Discussion.
-%Start by introducing the specific lattices, basis functions, filters used for the experiments (3.3.1, 3.3.2 and table 1 should come here).
-Additionally, need a subsection here that derives the filter weights for CC and BCC.
-The rest of the section shows the comparative surface reconstruction experimental results + discussion.
-
-%7. Conclusion.
-%Usual mumbo jumbo.
+%7. Results and Discussion.
+% Additionally, need a subsection here that derives the filter weights for CC and BCC. The rest of the section shows the comparative surface reconstruction experimental results + discussion.

### 2015-04-12 prelim.tex
Cleaned up refs/sec refs/symbols up to approach.

@@
 \subsection{Poisson Surface Reconstruction}
-We denote the indicator function of a model $M$ as $$ \chi_M(\mathbf{x}) :=
+We denote the indicator function of a model $M$ as $$ \chi_M(\vect{x}) :=
 \begin{cases}
-1, & \text{if }\mathbf{x}\text{ is in the interior of the model } M \\
-\frac{1}{2}, & \text{if } \mathbf{x}\text{ is on the model's surface}\\
-0, & \text{if }\mathbf{x}\text{ is exterior to } M
+1, & \text{if }\vect{x}\text{ is in the interior of the model } M \\
+\frac{1}{2}, & \text{if } \vect{x}\text{ is on the model's surface}\\
+0, & \text{if }\vect{x}\text{ is exterior to } M
 \end{cases}. $$
-The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\mathbf{x})$ with $\vec{V}(\mathbf{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small
+The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small
 \begin{equation} \label{eq:poisson}
@@
 \end{equation}}
-We define the set of input surface points to be $P:=\{(\mathbf{p}_1,\mathbf{n}_1), (\mathbf{p}_2,\mathbf{n}_2) \hdots (\mathbf{p}_M,\mathbf{n}_M) : (\mathbf{p}_i,\mathbf{n}_i) \in
-\realn^3 \times \realn^3 \}$ where $\mathbf{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively.
+We define the set of input surface points to be $P:=\{(\vect{p}_1,\vect{n}_1), (\vect{p}_2,\vect{n}_2) \hdots (\vect{p}_M,\vect{n}_M) : (\vect{p}_i,\vect{n}_i) \in \realn^3 \times \realn^3 \}$ where $\vect{p}_i$ and $\mathbf{n}_i$ are the position and normal vector of the $i^{th}$ sample respectively.
 Orientation can be succinctly represented with only two values, however, it is convenient to keep it as the normal at a point, because the length of the normal can be used to encode the sampling density of the point-set at a point.
-For the following discussion, we also need to introduce the notation $\patch_{\mathbf{s}}$, which denotes a patch of the surface model about the sample location $\mathbf{s}$.
+For the following discussion, we also need to introduce the notation $\patch_{\vect{s}}$, which denotes a patch of the surface model about the sample location $\vect{s}$.
 
@@
 \begin{eqnarray}
-	\vec{V}(\vx) & := & \sum_{(\mathbf{s},\mathbf{n}) \in P}\left|\patch_s\right|F(\vx-\mathbf{s})\cdot\vn \label{eq:vdef} \\
-	 & \approx & \sum_{(\mathbf{s},\mathbf{n}) \in P} \int_{\patch_s}{F(\mathbf{x} - \mathbf{p}) \nabla \chi (\mathbf{p})} \mathrm{d} \mathbf{p}. \notag  
+	\vec{V}(\vx) & := & \sum_{(\vect{s},\vect{n}) \in P}\left|\patch_s\right|F(\vx-\vect{s})\cdot\vn \label{eq:vdef} \\
+	 & \approx & \sum_{(\vect{s},\vect{n}) \in P} \int_{\patch_s}{F(\vect{x} - \vect{p}) \nabla \chi (\vect{p})} \mathrm{d} \vect{p}. \notag  
 \end{eqnarray}}
@@
 On a regular grid, this is undesirable.
-Another approach is to impose a type of ``interpolation'' constraint on the original data \cite{screenedk} \SC{section on this}.
+Another approach is to impose a type of ``interpolation'' constraint on the original data \cite{screenedk} (\SC{sec:vari_review}).
 
@@
 A common approach is to inherit the ideas from the univariate case and sample the function at regular intervals in each axis -- a Cartesian sampling --  while another might be to place samples at the centres of spheres arranged in the densest possible sphere packing (otherwise known as an FCC sampling).
-If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\mathbf{n} : \mathbf{n} \in \intn^3 \}$ represents all possible sampling lattices.
+If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\vect{n} : \vect{n} \in \intn^3 \}$ represents all possible sampling lattices.
 $\mathbf{L}$ is often called the \emph{generating matrix} for a lattice, and we'll assume that $\mathbf{L}$ is normalized so that $\left|\det\mathbf{L}\right| = 1$.
@@
 \begin{equation*}
-	\fspce{\varphi}{ \lattice{L}_h} := \left\{ g(\vx) := \displaystyle\sum_{\mathbf{m} \in \intn^3} c[\mathbf{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
+	\fspce{\varphi}{ \lattice{L}_h} := \left\{ g(\vx) := \displaystyle\sum_{\vect{m} \in \intn^3} c[\vect{m}]\genfuncdef{\vx} : c \in \ell_2 \right\},
 \end{equation*}}
 where $\varphi$ is the generating function for the space, $h$ is a scaling parameter that controls the sampling rate or granularity, and $\mathbf{L}$ is the generating matrix for a given sampling lattice.
-Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\mathbf{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.
+Representing a function $f$ in a shift invariant space boils down to finding an appropriate coefficient $c[\vect{m}]$ vector that brings $g$ as close as possible to the true underlying function $f$.
 
 Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice.
-We denote the set of such points as $\{\mathbf{s}_1,\mathbf{s}_2,\ \hdots  \ \mathbf{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\mathbf{s}_k)$; from this perspective, our function space is now {\small
+We denote the set of such points as $\{\vect{s}_1,\vect{s}_2,\ \hdots  \ \vect{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\vect{s}_k)$; from this perspective, our function space is now {\small
 \begin{equation}
@@
 Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $P_{i,j} := \varphi_j(\vx_i)$.
-Clearly, if our data are sampled at the lattice sites ($\vx_i = \mathbf{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\mathbf{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites and we must consider alternative schemes for finding $\mathbf{c}$, which we'll come back to in \SC{sec:vari_review}
+Clearly, if our data are sampled at the lattice sites ($\vx_i = \vect{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\vect{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites and we must consider alternative schemes for finding $\mathbf{c}$, which we'll come back to in \SC{sec:vari_review}
 
@@
 To facilitate the classical analysis of signals in a shift-invariant space, we need a few notions first.
-The first tool we need is the Fourier transform of a multivariate function $f(\mathbf{x})$, which we define as $\ft{f}(\vect{\omega}) := \int_{\reel^3} f(\vect{x}) \exp(-2\pi \imath
-\vect{\omega} \cdot \vect{x})  \mathrm{d}\vect{x} $.
-The discrete time Fourier transform (DTFT) of a sequence $c[\cdot]$ associated with a lattice $\lattice{L}$ is defined as $\ft{C}(\vect{\omega}) := \sum_{\vect{m}  \in \ints^3} c[\vect{m}] \exp(-2 \pi \imath \vect{\omega} \cdot
-(\mat{L}\vect{n}))$.
+We define all this notation in $s$-dimensions, as the generalization comes at little cost.
+The first tool we need is the Fourier transform of a multivariate function $f(\vect{x})$, which we define as $ \ft{f}(\vect{\omega}) := \int_{\reel^s} f(\vect{x}) \exp(-2\pi \imath \vect{\omega} \cdot \vect{x}) \mathrm{d}\vect{x} $.
+The discrete time Fourier transform (DTFT) of a sequence $c[\cdot]$ associated with a lattice $\lattice{L}$ is defined as $\ft{C}(\vect{\omega}) := \sum_{\vect{m}  \in \ints^s} c[\vect{m}] \exp(-2 \pi \imath \vect{\omega} \cdot (\mat{L}\vect{n}))$.
 Recall that $\ft{C}(\vect{\omega})$ is periodic with respect to the dual lattice $\duallattice{L}$, i.e.
-$\ft{C}(\vect{\omega} + \invtransp{\mat{L}} \vect{m}) = \ft{C}(\vect{\omega}), \forall \vect{m} \in \ints^3$.
+$\ft{C}(\vect{\omega} + \invtransp{\mat{L}} \vect{m}) = \ft{C}(\vect{\omega}), \forall \vect{m} \in \ints^s$.
 The notation `$\ftpairs{}{}$' is subsequently employed to denote transform pairs, i.e.
@@
 
-The inner product between two real valued functions $f_1$ and $f_2$ belonging to $L_2(\reel^3)$ is denoted as $\ip{f}{g} := \int_{\reel^3} f(\vect{x}) g(\vect{x}) d\vect{x}$.
+The closed unit hypercube $[0,1]^s$ is denoted as $\ucube^s$ while the closed hypercube $[-1,1]^s$ is denoted as $\cube^s$.
+The corresponding open hypercubes are denoted as $\oucube^s$ and $\ocube^s$ respectively.
+The inner product between two real valued functions $f_1$ and $f_2$ belonging to $L_2(\reel^s)$ is denoted as $\ip{f}{g} := \int_{\reel^s} f(\vect{x}) g(\vect{x}) d\vect{x}$.
 Likewise, the inner product between two functions $f_1$ and $f_2$ that belong to $L_2(\cube^s)$ is denoted as $\innerproduct{f_1}{f_2} := {2^{-s}} \int_{\cube^s} f_1(\vect{x}) f_2(\vect{x}) d\vect{x}$.
@@
 \subsection{The Error Kernel}
-
 The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation
@@
 For a bandlimited function $f$ whose spectrum is entirely contained
-within the Voronoi cell of $\duallattice{L}_h$ centered around
-$\vect{\omega} = 0$, we have 
+within the Voronoi cell of $\duallattice{L}_h$ centered around $\vect{\omega} = 0$, we have 
 \begin{equation}
@@
 \end{equation}
-whereas when $f \in W_2^k(\reel^s)$ with $k > \frac{1}{2}$, the
-integral in~\eqref{eq:avgError} gives the $L_2$-error averaged over
-all possible shifts of $f$. Even though this kernel was initially
-proposed in the univariate setting by Blu and Unser~\cite{blu99}, multivariate
-non-Cartesian extensions have also appeared in the
-literature~\cite{condat05hexagonal, condat07, condat08, alim10,
-  condat11}. Note that the minimum-error approximation scenario occurs
-when $f$ is orthogonally projected to $\aspace{\lattice{L}_h}{\varphi}$,
-or in other words $\analysis{\varphi}$ is chosen to be  $\dual{\varphi}$.
- polynomial spaces,
+whereas when $f \in W_2^k(\reel^s)$ with $k > \frac{1}{2}$, the integral in~\eqref{eq:avgError} gives the $L_2$-error averaged over all possible shifts of $f$.
+Even though this kernel was initially proposed in the univariate setting by Blu and Unser~\cite{blu99}, multivariate non-Cartesian extensions have also appeared in the literature~\cite{condat05hexagonal, condat07, condat08, alim10, condat11}.
+Note that the minimum-error approximation scenario occurs when $f$ is orthogonally projected to $\aspace{\lattice{L}_h}{\varphi}$, or in other words $\analysis{\varphi}$ is chosen to be $\dual{\varphi}$.
 

### 2015-04-12 approach.tex
Touching up approach pipeline diagram

@@
 On the far left, a) shows the initial point-set.
-b) is the result of the smoothed variational reconstruction of the gradient of the indicator, the top image is the component in basis, the bottom is the y component.
+b) is the result of the smoothed variational reconstruction of the gradient of the indicator, the top image is the x component, the bottom is the y component.
 The approximate divergence of the smoothed indicator function is c), and d) is the resulting indicator function.
-\ednote{UA: Please fix this.}}
+}
 	\label{fig:pipeline}
@@
 
-\subsection{Obtaining $\vec{V}(\vx)$} \label{sec:getting_vd}
+\subsection{Obtaining the smoothed vector field} \label{sec:getting_vd}
 \label{sec:obtainingV}
@@
 
-\subsection{Divergence of $\vec{V}(\vx)$}
+\subsection{Divergence of the Smoothed Vector Field}
 \label{sec:divergence}

### 2015-04-12 poisson_errker.tex
Touching up approach pipeline diagram

@@
 of $\rho$ so that, within the interval $\cube^s$, it satisfies
+{\small
 \begin{equation}  
-  \small{
  \rho(\vect{x}) :=  
@@
 \end{cases}
-}
 \label{eq:oddextension}
 \end{equation}
+}
+
 while outside $\cube^s$, it is $\cube^s$-periodic, i.e. $\rho(\vect{x}
@@
 (for $\vect{m} \in \ints^s$) as
-\begin{equation}
-  \small{
+{\small \begin{equation}
 	\ft{\rho}[\vect{m}] := 
@@
 	\end{cases}
-}
 	\label{eq:oddFourierExtension}
-\end{equation}
+\end{equation}}
+
 then  $\rho$ is also given by the Fourier series

### 2015-04-12 approach.tex
Fixing some small notation blips

@@
 \begin{equation} 
-	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_ki \varphi_k^i(\vx) \in \aspace{\lattice{L}{\varphi^i}}.
+	\upsilon_i(\vx) = \sum_{k=0}^N \text{v}_k^i \varphi_k^i(\vx) \in \aspace{\lattice{L}}{\varphi^i}.
 \end{equation}}
@@
 \begin{equation} \label{eq:vari_eqn}
- 	\sump_{\forall (\vx,\vn) \in P }^{M} (\upsilon_i(\vx) - (\mathbf{L}^{-1})_i \cdot \mathbf{n})^2 + E(\upsilon_i).
+ 	\sump_{\forall (\vx,\vn) \in P }^{M} (\upsilon_i(\vx) - (\mathbf{L}^{-1})_i \cdot \vect{n})^2 + E(\upsilon_i).
 \end{equation} }
@@
 \end{equation}}
-where $\mathbf{d}_i$ is a directional derivative filter obtained by orienting the 1D filter $d$ 
-along the direction $\mathbf{b}_i.$
+where $\mathbf{d}_i$ is a directional derivative filter obtained by orienting the 1D filter $d$ along the direction $\mathbf{b}_i.$
 
@@
 It is easy to see that, by the same reasoning as in equation \EQ{eq:div_dir}, $\grad \cdot \vec{V} = \dv{\mathbf{b_1}}\upsilon_1 + \dv{\mathbf{b_2}}\upsilon_2 + \dv{\mathbf{b_3}}\upsilon_3 + \dv{\mathbf{b_4}}\upsilon_4$.
-Thus, we may use the same idea as in the three direction case, approximating each direction separately, and summing the coefficients to obtain an approximation to the divergence (the shifted case is also similar.)
-%\begin{equation}
-%	\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T
-%\end{equation}
+Thus, we may use the same idea as in the three direction case, approximating each direction separately, and summing the coefficients to obtain an approximation to the divergence (the shifted case is also similar).

### 2015-04-12 prelim.tex
Touching up approach pipeline diagram
Fixing some small notation blips

@@
-\section{Preliminaries}\label{sec:pois_review}
+\section{Preliminaries}
+\label{sec:pois_review}
 \subsection{Poisson Surface Reconstruction}
-We denote the indicator function of a model $M$ as $$ \chi_M(\vect{x}) :=
+We denote the indicator function of a model $M$ as 
+$$ \chi_M(\vect{x}) :=
 	\begin{cases}
 		1, & \text{if }\vect{x}\text{ is in the interior of the model } M \\
-\frac{1}{2}, & \text{if } \vect{x}\text{ is on the model's surface}\\
+		\frac{1}{2}, & \text{if } \vect{x}\text{ is on the model's surface} \\
 		0, & \text{if }\vect{x}\text{ is exterior to } M
-\end{cases}. $$
+	\end{cases}. 
+$$.
 The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small

### 2015-05-26 poisson_errker.tex
Updating poisson section

@@
 \begin{equation}
-  \st{V}[\vect{m}] = -
+  \st{\chi}[\vect{m}] = -
   \frac{\st{f}[\vect{m}]}{\pi^2 \norm{\vect{m}}^2},
@@
 
-We wish to use the samples of $f$ to seek an approximation $\appf{V}$ of the
-function $V$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. Since
-$V$ is a periodic function, we follow the recipe of Jacob \textit{et
-al.}~\cite{jacob02} and seek an approximation that lies in a space generated by
-a periodic reconstruction function. Specifically, we are interested in the case
-where $\appf{V}$ lies in the space $\aspace{\lattice{L}_h}{\varphi_p} :=
-\mathrm{span}_{\vect{x}_j\in\pointset{T}_h}\{
-\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}) \}$ that is spanned by the scaled and
-translated versions of a periodic function $\varphi_p$. Our sought-after
-approximation is given by
+We wish to use the samples of $f$ to approximate the function $V$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. Since
+$\chi$ is a periodic function, we follow the recipe of Jacob \textit{et al.}~\cite{jacob02} and seek an approximation that lies in a space generated by a periodic reconstruction function.
+Specifically, we are interested in the case
+where $\appf{\chi}$ lies in the space $\aspace{\lattice{L}_h}{\varphi_p} := \mathrm{span}_{\vect{x}_j\in\pointset{T}_h}\{
+\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}) \}$ that is spanned by the scaled and translated versions of a periodic function $\varphi_p$. Our approximation is given by
 \begin{equation}
-  \appf{V}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{T}_h} c[\vect{x}_j] 
+  \appf{\chi}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{T}_h} c[\vect{x}_j] 
 \varphi_p\bigl(\frac{\vect{x} - \vect{x}_j}{h}\bigr),
@@
 \end{equation}
-where $c[\vect{x}_j]$ is an unknown coefficient sequence defined on
-the point set $\pointset{T}_h$ that is to be determined from the
-samples of $f$. The function
-$\varphi_p$ is a periodized version of a generating function $\varphi$
-and is defined as
+where $c[\vect{x}_j]$ is an unknown coefficient sequence defined on the point set $\pointset{T}_h$ that is to be determined from the samples of $f$.
+The function $\varphi_p$ is a periodized version of a generating function $\varphi$ and is defined as
 \begin{equation}
@@
 It is easy to verify that, with this definition of $\varphi_p$,
-$\appf{V}$ is also $\cube^s$-periodic. Even though we are only
-interested in the behavior of $\appf{V}$ inside $\ucube^s$, extending
-$\appf{V}$ to the entire domain $\cube^s$ using~\eqref{eq:ansatz}
-allows us to use the Fourier domain error kernel proposed by Jacob
-\textit{et. al}~\cite{jacob02} to quantify the approximation error
-$\LLnorm{V - \appf{V}}$.
+$\appf{\chi}$ is also $\cube^s$-periodic. Even though we are only
+interested in the behavior of $\appf{V}$ inside $\ucube^s$, extending $\appf{\chi}$ to the entire domain $\cube^s$ using~\eqref{eq:ansatz} allows us to use the Fourier domain error kernel proposed by Jacob \textit{et.
+al}~\cite{jacob02} to quantify the approximation error $\LLnorm{\chi - \appf{\chi}}$.
 
-Another simplification is in order here. Since the solution $V$ to the Poisson
-problem~\eqref{eq:PoissonEquation} is odd with respect to each variable, we look
-for an approximate solution $\appf{V} \in \aspace{\lattice{L}_h}{\varphi_p}$
+Another simplification is in order here.
+Since the solution $\chi$ to the Poisson problem~\eqref{eq:PoissonEquation} is odd with respect to each variable, we look for an approximate solution $\appf{\chi} \in \aspace{\lattice{L}_h}{\varphi_p}$
 that is also odd in each variable. This can be achieved by setting
-the boundary coefficients to zero and by requiring that the resulting sequence
-be odd.  With $c[\vect{x}_j] = 0$ for $\vect{x}_j
-\in \pointset{B}_h$, the approximation~\eqref{eq:ansatz} simplifies to
+the boundary coefficients to zero and by requiring that the resulting sequence be odd.  With $c[\vect{x}_j] = 0$ for $\vect{x}_j \in \pointset{B}_h$, the approximation~\eqref{eq:ansatz} simplifies to
 \begin{equation}

### 2015-07-06 poisson_errker.tex
Correcting some mistakes

@@
 
-\subsection{Approximate Solution}
+\subsection{Approximate Solution} \sec{sub:approximatesol}
 We are interested in the scenario where the function $f$ is only known
@@
 
-We wish to use the samples of $f$ to approximate the function $V$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. Since
+We wish to use the samples of $f$ to approximate the function $\chi$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. Since
 $\chi$ is a periodic function, we follow the recipe of Jacob \textit{et al.}~\cite{jacob02} and seek an approximation that lies in a space generated by a periodic reconstruction function.
@@
 error behaves as $O(h^k)$ where $k = \order{\lattice{L}}{\varphi}$. Our operator
-discretization approach is also based on these assumptions. Provided that $V \in
-W_2^k(\cube^s)$, our goal is to design suitable digital filters that yield
-$\appf{V}$ such that $\LLnorm{V - \appf{V}} = O(h^k)$. As discussed earlier
-in~\SC{sec:interpQuasiInterp}, the criterion that needs to be satisfied is
-$E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$.
+discretization approach is also based on these assumptions.
+Provided that $\chi$ has appropriate smoothness, our goal is to design suitable digital filters that yield %$V \in W_2^k(\cube^s)$, our goal is to design suitable digital filters that yield
+$\appf{\chi}$ such that $\LLnorm{\chi - \appf{chi}} = O(h^k)$.
+%As discussed earlier in~\SC{sec:interpQuasiInterp}, the criterion that needs to be satisfied is $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$.
 
@@
 \label{sec:Galerkin}
-The modified residue error kernel~\eqref{eq:opResidue} can also be analyzed in
-light of the Galerkin method~\cite{quarteroni08} using a weak formulation of the Poisson
-equation~\eqref{eq:PoissonEquation}, where the trial and test spaces are the
-same with the notable difference that the spaces are not required to explicitly
-satisfy any particular boundary conditions. Rather, a zero boundary condition is
-implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be
-odd as explained in~\SC{sec:approximateSolution}. Here, we establish the
-connection for the homogeneous case but the analysis also easily extends to the
-non-homogeneous case, as well as to other types of differential operators.
+The modified residue error kernel~\eqref{eq:opResidue} can also be analyzed in light of the Galerkin method~\cite{quarteroni08} using a weak formulation of the Poisson equation~\eqref{eq:PoissonEquation}, where the trial and test spaces are the same with the notable difference that the spaces are not required to explicitly satisfy any particular boundary conditions.
+Rather, a zero boundary condition is implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be odd as explained in~\SC{sub:approximatesol}.
+Here, we establish the connection for the homogeneous case but the analysis also easily extends to the non-homogeneous case, as well as to other types of differential operators.
 
-In its weak form, the solution $V \in L_2(\cube^s)$ to the homogeneous
-Poisson equation~\eqref{eq:PoissonEquation} satisfies the weak
-formulation
+In its weak form, the solution $\chi \in L_2(\cube^s)$ to the homogeneous Poisson equation~\eqref{eq:PoissonEquation} satisfies the weak formulation
 \begin{equation}
-  \innerproduct{V}{u} = \mathcal{F}(u), \;\; \forall u \in L_2(\cube^s),
+  \innerproduct{\chi}{u} = \mathcal{F}(u), \;\; \forall u \in L_2(\cube^s),
 \end{equation}
@@
 $\aspace{\lattice{L}_h}{\varphi_p} \subset L_2(\cube^s)$. We seek a
-weak solution $\appf{V} \in \aspace{\lattice{L}_h}{\varphi_p}$ so that
+weak solution $\appf{\chi} \in \aspace{\lattice{L}_h}{\varphi_p}$ so that
 \begin{equation}
-  \innerproduct{\appf{V}}{u_h} = \mathcal{F}(u_h), \;\;
+  \innerproduct{\appf{\chi}}{u_h} = \mathcal{F}(u_h), \;\;
   \forall u_h \in \aspace{\lattice{L}_h}{\varphi_p},
@@
 \begin{equation}
-  \innerproduct{V - \appf{V}}{u_h} = 0, \;\;
+  \innerproduct{\chi - \appf{\chi}}{u_h} = 0, \;\;
   \forall u_h \in \aspace{\lattice{L}_h}{\varphi_p}.
@@
 \end{equation}
-From this, it can be deduced that the minimum error approximation
-$\appf{V}$ is the orthogonal projection of $V$ upon
-$\aspace{\lattice{L}_h}{\varphi_p}$. The coefficients of the
-approximation are thus given by
+From this, it can be deduced that the minimum error approximation $\appf{\chi}$ is the orthogonal projection of $\chi$ upon $\aspace{\lattice{L}_h}{\varphi_p}$.
+The coefficients of the approximation are thus given by
 \begin{equation}
@@
 
-Observe that if we use the analysis function $\analysis{\varphi}_p =
-\invlaplacian \dual{\varphi}_p$ (in a distributional sense) in the
-measurement equation~\eqref{eq:measurements}, and subsequently employ
-no filtering (i.e. $\gamma[\vect{x}_j] = \delta[\vect{x}_j]$
-in~\eqref{eq:opApproximation}), then the measurements obtained will realize the orthogonal projection of $V$
-upon $\aspace{\lattice{L}_h}{\varphi_p}$. In this case, the modified Fourier
-residue error kernel~\eqref{eq:opResidue} vanishes,
-i.e. $E_{\mathsf{mod}}(\vect{\omega}) = 0$.
+Observe that if we use the analysis function $\analysis{\varphi}_p = \invlaplacian \dual{\varphi}_p$ (in a distributional sense) in the measurement equation~\eqref{eq:measurements}, and subsequently employ no filtering (i.e.
+$\gamma[\vect{x}_j] = \delta[\vect{x}_j]$ in~\eqref{eq:opApproximation}), then the measurements obtained will realize the orthogonal projection of $\chi$ upon $\aspace{\lattice{L}_h}{\varphi_p}$.
+In this case, the modified Fourier residue error kernel~\eqref{eq:opResidue} vanishes, i.e.
+$E_{\mathsf{mod}}(\vect{\omega}) = 0$.
 
-On the other hand, if the point samples of $f$ are already available
-(i.e. $\analysis{\varphi} = \delta$) and the orthogonal projection
-cannot be realized, then the goal of the asymptotically optimal
-procedure is to find a suitable correction filter $\gamma$ such that
-$E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ where
-$k = \order{\lattice{L}}{\varphi}$.  
+On the other hand, if the point samples of $f$ are already available (i.e. $\analysis{\varphi} = \delta$) and the orthogonal projection cannot be realized, then the goal of the asymptotically optimal
+procedure is to find a suitable correction filter $\gamma$ such that $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ where $k = \order{\lattice{L}}{\varphi}$.  
 %If we define the analysis function
@@
 %k$. 
-In other words, our approximation procedure attempts to reproduce the
-Galerkin orthogonality condition given
-by~\eqref{eq:GalerkinOrthogonality}. This is akin to the
-quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
+In other words, our approximation procedure attempts to reproduce the Galerkin orthogonality condition given by~\eqref{eq:GalerkinOrthogonality}.
+This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
 in~\SC{sec:interpQuasiInterp}.

### 2015-07-27 abstract.tex
Adding appendix

@@
-In this work, we cast the well-known Poisson surface reconstruction algorithm into a more general setting, we reformulate it in terms of shift invariant spaces (spaces that are spanned by lattice translates of an admissible generating function).
+In this work, we cast the well-known Poisson surface reconstruction algorithm into a more general setting -- we reformulate it in terms of shift invariant spaces (spaces that are spanned by lattice translates of an admissible generating function).
 The treatment is general, but our specific interest is in reconstructing a surface of a solid model from an oriented point-set within function spaces defined over the body centred cubic lattice.

### 2015-07-27 poisson_errker.tex
Adding appendix

@@
 
-\subsection{Approximate Solution} \sec{sub:approximatesol}
-We are interested in the scenario where the function $f$ is only known
-through its point samples. Specifically, we assume that the samples of
-$f$ reside on the sites of the lattice $\lattice{L}_h$. For the
-purpose of enumerating the samples that are contained within
-$\cube^s$, let us define the point set
+\subsection{Approximate Solution} \label{sub:approximatesol}
+We are interested in the scenario where the function $f$ is only known through its point samples.
+Specifically, we assume that the samples of $f$ reside on the sites of the lattice $\lattice{L}_h$.
+For the purpose of enumerating the samples that are contained within $\cube^s$, let us define the point set
 \begin{equation}
@@
 The modified residue error kernel~\eqref{eq:opResidue} can also be analyzed in light of the Galerkin method~\cite{quarteroni08} using a weak formulation of the Poisson equation~\eqref{eq:PoissonEquation}, where the trial and test spaces are the same with the notable difference that the spaces are not required to explicitly satisfy any particular boundary conditions.
-Rather, a zero boundary condition is implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be odd as explained in~\SC{sub:approximatesol}.
+Rather, a zero boundary condition is implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be odd.
+% as explained in~\SC{sub:approximatesol}.
 Here, we establish the connection for the homogeneous case but the analysis also easily extends to the non-homogeneous case, as well as to other types of differential operators.
@@
 In other words, our approximation procedure attempts to reproduce the Galerkin orthogonality condition given by~\eqref{eq:GalerkinOrthogonality}.
-This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
+%This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
 in~\SC{sec:interpQuasiInterp}.

### 2015-09-09 appendix.tex
Committing lost work from laptop

\label{app:1}
We need to show that if $\varphi$ is an even function and $c[\cdot]$ is odd, then $\appf{\chi}$~\eqref{eq:simplifiedAnsatz} is also odd. 
This is done by inspecting the Fourier series coefficients of $\appf{\chi}$. 
Using the Poisson summation formula, the Fourier series coefficients $\wft{\appf{\chi}}[\cdot]$ are given by
\begin{equation}
  \wft{\appf{\chi}}[\vect{m}] = \ft{\varphi}\left(\frac{h}{2}\vect{m}\right) 
  \sum_{j=1}^{2^sN} c[\vect{x}_j]
  \exp(-\imath \pi \vect{m} \cdot \vect{x}_j),
\label{eq:ftansatz}
\end{equation}
where $\vect{m} \in \ints^s$.
Since the coefficient sequence $c[\cdot]$ is odd, the summation in~\eqref{eq:ftansatz} can be simplified to yield
\begin{equation}
  \wft{\appf{\chi}}[\vect{m}] = \ft{\varphi}\left(\frac{h}{2}\vect{m}\right)(2\imath)^s
  \st{C}[\vect{m}],
\end{equation}
where $\st{C}[\vect{m}]$ denotes the multidimensional discrete sine transform of the sequence $c[\cdot]$ (not to be confused with the Fourier sine series), and is given by
\begin{equation}
  \st{C}[\vect{m}] := \sum_{j=1}^N c[\vect{x}_j]
  \bigl( 
  \textstyle\prod_{i=1}^s
  \sin(m_i \pi x_{j,i})
  \bigr),
\label{eq:MDST}
\end{equation}
where $\vect{m} \in \ints^s$.
Now, since $\ft{\varphi}(\vect{\omega})$ is a real even function and $\st{C}[\vect{m}]$ is odd, the Fourier series coefficients $\wft{\appf{\chi}}[\vect{m}]$ satisfy the odd extension~\eqref{eq:oddFourierExtension} with the sine series coefficients being $\wst{\appf{\chi}}[\vect{m}] = (-4)^s \ft{\varphi}(\frac{h}{2}\vect{m})\st{C}[\vect{m}]$, for $\vect{m} \in \ints^s_+$. This establishes the fact that the approximate solution $\appf{\chi}$ is also odd.

\section{Proofs}
\label{app:proofs}

\begin{proof}[Theorem~\ref{thm:1}]
  For the purpose of approximating $\Gamma z$ in the space spanned by the
  periodic generator $\varphi_p$, we need to analyze $\Gamma z$ in a manner
  similar to~\eqref{eq:measurements}. Let the analysis function used
  to measure $\Gamma z$ be $\analysis{\psi}_p$, which is obtained by
  periodizing the function $\analysis{\psi}$. Let the resulting coefficient
  sequence be $\tau[\cdot]$, i.e.
  \begin{equation*}
    \tau[\vect{x}_j] = 
    \innerproduct{(\Gamma
    z)(\vect{x})}{\analysis{\psi}_p(\frac{\vect{x}-\vect{x}_j}{h})},
  \end{equation*}
  so that the approximation of $\Gamma z$ is 
  $
  \appf{(\Gamma z)}(\vect{x}) = \sum_{\vect{x}_j \in \pointset{P}_h}
  \tau[\vect{x}_j] \varphi_p(\frac{\vect{x}-\vect{x}_j}{h})
  $.

  The error $\LLnorm{\appf{(\Gamma z)} - \Gamma z}$ can thus be predicted
  according to~\eqref{eq:prediction} and~\eqref{eq:scErrorKernel} with
  the substitutions $\ft{z} \rightarrow \wft{(\Gamma z)}$ and
  $\ft{\analysis{\varphi}} \rightarrow \ft{\analysis{\psi}}$ respectively.

  Now, since $\Gamma$ is self-adjoint and shift-invariant, we have
  \begin{equation*}
    \innerproduct{(\Gamma
    z)(\vect{x})}{\analysis{\psi}_p(\frac{\vect{x}-\vect{x}_j}{h})} = C_h
    \innerproduct{z(\vect{x})}{(\Gamma
    \analysis{\psi})_p(\frac{\vect{x}-\vect{x}_j}{h})},
  \end{equation*}
  where $C_h$ is some constant depending on the scale $h$. Thus,
  measuring $\Gamma z$ with $\analysis{\psi}_p$ is equivalent to measuring
  $z$ with $(\Gamma \analysis{\psi})_p$ in a distributional sense. We are
  interested in a digital filtering solution where $\tau[\vect{x}_j] =
  C_h (\zeta \pconv \gamma_h)[\vect{x}_j]$. This can be realized by requiring
  that $\analysis{\psi}$ satisfies
  $\ft{\Gamma}(\vect{\omega})\ft{\analysis{\psi}}(\vect{\omega}) =
  \ft{\analysis{\varphi}}(\vect{\omega}) \ft{G}(\vect{\omega})$. From
  here, we infer that $\ft{\analysis{\psi}}(\vect{\omega}) =
  \frac{\ft{\analysis{\varphi}}(\vect{\omega})\ft{G}(\vect{\omega})}
  {\ft{\Gamma}(\vect{\omega})}$ and the result follows.
\end{proof}

\begin{proof}[Proposition~\ref{prop:1}]
  From~\eqref{eq:discreteLaplacian},
  \begin{equation*}
    \ft{L}(\vect{\omega}) =
    \ft{P}_{\varphi}(\vect{\omega})\ft{\Lambda}(\vect{\omega}) = -4 \pi^2 \ft{P}_{\varphi}(\vect{\omega})\norm{\vect{\omega}}^2 + O(\norm{\vect{\omega}}^{k+2}).
  \end{equation*}
  After some rearrangement and using the fact that
  $\ft{L}(\vect{\omega}) = O(\norm{\vect{\omega}}^2)$, we obtain
  \begin{equation*}
    -\frac{4\pi^2\norm{\vect{\omega}}^2}{\ft{L}(\vect{\omega})} 
    = \frac{1}{\ft{P}_{\varphi}(\vect{\omega})}
    + O(\norm{\vect{\omega}}^k),
  \end{equation*}
  which satisifies the asymptotic optimality
  criterion~\eqref{eq:opCriterionHomo} since
  $\ft{P}_{\varphi}(\vect{\omega}))^{-1}$ is a quasi-interpolation
  filter and satisfies $(\ft{P}_{\varphi}(\vect{\omega}))^{-1}
  = \ft{\dual{\varphi}}(\vect{\omega}) + O(\norm{\vect{\omega}}^k)$.
\end{proof}

\begin{proof}[Proposition~\ref{prop:2}]
  The modified residue error kernel for this approximation scheme is given by
  \begin{equation*}
    E_{\mathsf{mod}}(\vect{\omega}) = 
    \ft{A}_{\varphi}(\vect{\omega})
    \abs{
      \frac{4\pi^2 \norm{\vect{\omega}}^2}{\ft{L}_\psi(\vect{\omega})}
      \ft{Q}(\vect{\omega})
      + 
      \ft{\dual{\varphi}}(\vect{\omega})}^2,
  \end{equation*}
  where $\ftpairs{l_{\psi}^{-1}}{1/\ft{L}_\psi}$ denotes the filter
  obtained from~\SC{sec:interpModel} with $\psi$ as the generator. Given that 
  $m \ge k$, we need to show that
  $-\frac{4\pi^2\norm{\vect{\omega}}^2}{\ft{L}_\psi(\vect{\omega})}\ft{Q}(\vect{\omega})
  = \ft{\dual{\varphi}}(\vect{\omega}) + O(\norm{\vect{\omega}}^n)$
  for some $n \ge k$.

  Now, from the proof of Proposition~\ref{prop:1} we know that
  $-\frac{4\pi^2\norm{\vect{\omega}}^2}{\ft{L}_\psi(\vect{\omega})} =
  \ft{\dual{\psi}}(\vect{\omega}) +
  O(\norm{\vect{\omega}}^m)$. Furthermore,
  using~\eqref{eq:quasiWeights} and the fact that $\order{\lattice{L}}{\psi} = m$
  and $\order{\lattice{L}}{\varphi} = k$, we have $\ft{Q}(\vect{\omega}) =
  \ft{\psi}(\vect{\omega})\ft{\dual{\varphi}}(\vect{\omega}) +
  O(\norm{\vect{\omega}}^{m+k})$. Therefore,
  \begin{equation*}
    \begin{split}
      & -\frac{4\pi^2 \norm{\vect{\omega}}^2}{\ft{L}_\psi(\vect{\omega})}
      \ft{Q}(\vect{\omega}) =\\
      & \bigl(\ft{\dual{\psi}}(\vect{\omega}) +
      O(\norm{\vect{\omega}}^m)\bigr)
      \bigl(
      \ft{\psi}(\vect{\omega})\ft{\dual{\varphi}}(\vect{\omega}) +
      O(\norm{\vect{\omega}}^{m+k})
      \bigr)\\
      &= \ft{\psi}(\vect{\omega})
      \ft{\dual{\psi}}(\vect{\omega})
      \ft{\dual{\varphi}}(\vect{\omega}) + O(\norm{\vect{\omega}}^m)
      =\ft{\dual{\varphi}}(\vect{\omega}) + O(\norm{\vect{\omega}}^m),
    \end{split}
  \end{equation*}
since $\ft{\psi}$, $\ft{\dual{\psi}}$ and $\ft{\dual{\varphi}}$ are all $O(1)$
around $\vect{\omega} = \vect{0}$.
\end{proof}

### 2015-09-09 operator_discretization.tex
Committing lost work from laptop

\section{Operator Discretization}
\label{sec:opDisc}

The asymptotic optimality criterion amounts to requiring that the
residue error kernel asymptotically behaves like the minimum error
kernel, i.e. $E_{\mathsf{mod}}(\vect{\omega}) \approx
E_{\mathsf{min}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ around
$\vect{\omega} = 0$. In this section, we consider two discretization
models: an \emph{interpolative} model that is based on an
interpolation prefilter obtained from the samples of $\varphi$, and a
more accurate two-stage \emph{quasi-interpolative} model that makes
use of a higher order auxiliary generator $\psi$. Both scenarios yield
digital filters that can be readily applied to the samples in the
Fourier domain via the MDST.

\subsection{Interpolative Model}
\label{sec:interpModel}
Suppose that our desired approximation space is spanned by generator
$\varphi$ where $\order{\lattice{L}}{\varphi} =
k$. From~\eqref{eq:fourierSolution}, the operator that we need to
discretize is $\invlaplacian$. In order to obtain a discretization, we
make use of the filter $\ft{P}_{\varphi}(\vect{\omega})$ that is
obtained from the samples of $\varphi$ that lie on the nodes of
$\lattice{L}$. Recall that the inverse filter
$(\ft{P}_{\varphi}(\vect{\omega}))^{-1}$ is needed to make the generator $\varphi$
interpolating (\SC{sec:interpQuasiInterp}).

Let us denote the discretization of $\invlaplacian$ on the normalized lattice
$\lattice{L}$ as $l^{-1}$ so that the approximate solution on the lattice
$\lattice{L}_h$ can be written as
\begin{equation}
\appf{V}(\vect{x}) = h^2 \sum_{j=1}^{2^s N}
\underbrace{(f \pconv l^{-1}_h)}_{c}[\vect{x}_j]
\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}).
\label{eq:approxHomogeneous}
\end{equation}
Using the
residue error kernel~\eqref{eq:opResidue}, the optimality criterion
boils down to requiring that
\begin{equation}
  \ft{A}_{\varphi}(\vect{\omega})
  \bigl|
  4 \pi^2 \norm{\vect{\omega}}^2 \wft{L^{-1}}(\vect{\omega})
  + 
  \ft{\dual{\varphi}}(\vect{\omega}) 
  \bigr|^2
  = 
  O(\norm{\vect{\omega}}^{2k}).
  \label{eq:opCriterionHomo}
  \end{equation}
  In order to arrive at this result, we have extended the operator
  $\invlaplacian$ to $L_2(\reel^s)$ where $\ftpairs{\invlaplacian}{(-4
    \pi^2 \norm{\vect{\omega}}^2)^{-1}}$. The reason for choosing
  $l^{-1}$ as a discretization of $\invlaplacian$ will become apparent
  in light of the following proposition which gives us a way of
  reformulating the problem of designing $l^{-1}$, a filter that
  discretizes $\invlaplacian$, into a simpler problem of designing the
  filter $l := (l^{-1})^{-1}$ that discretizes the Laplacian
  $\laplacian$.

\begin{prop}
\label{prop:1}
  Let the digital filter $\ft{L}(\vect{\omega})$ be given by the
  combined filter $\ft{L}(\vect{\omega}) =
  \ft{P}_{\varphi}(\vect{\omega})\ft{\Lambda}(\vect{\omega})$, where
  $\ftpairs{\ft{\Lambda}(\cdot)}{\lambda[\cdot]}$ is a digital filter that satisfies
  \begin{equation}
    \ft{\Lambda}(\vect{\omega}) = -4\pi^2\norm{\vect{\omega}}^2 
    + O(\norm{\vect{\omega}}^{k+2}).
    \label{eq:discreteLaplacian}
  \end{equation}
  Then the combined inverse filter $\wft{L^{-1}}(\vect{\omega}) =
  (\ft{P}_{\varphi}(\vect{\omega})\ft{\Lambda}(\vect{\omega}))^{-1}$
  provides a $k$-th order asymptotically optimal discretization of the
  inverse Laplacian $\invlaplacian$.
\end{prop}
The proof is provided in Appendix~\ref{app:proofs}.

It is not hard to see that this method is essentially a collocation method with
respect to the trial space spanned by the generator $\varphi_p$. If we apply the
discrete Laplacian filter $\ftpairs{\lambda}{\ft{\Lambda}}$ to the
coefficients in approximation~\eqref{eq:approxHomogeneous}, we obtain
\begin{equation}
  (\laplacian \appf{V})(\vect{x}) \approx
  \sum_{j=1}^{2^s N}
  (f \pconv p_{\varphi}^{-1})[\vect{x}_j]
  \varphi_p(\frac{\vect{x}-\vect{x}_j}{h}),
\end{equation}
where
$\ftpairs{p_{\varphi}^{-1}[\cdot]}{(\ft{P}_{\varphi}(\cdot))^{-1}}$. Owing to 
the fact that $p^{-1}_{\varphi}$ is an interpolation filter, this approximation,
when evaluated at the lattice sites contained in $\oucube^s$, will yield the
samples of $f$.

\subsection{Quasi-interpolative Model}
% The model described in the previous section heavily relies on the
% interpolation prefilter $1/\ft{P}_{\varphi}$ that ensures that the
% discretized Laplacian of the approximate solution, exactly reproduces
% the sample values of $f$ at the lattice sites. For this reason, it can
% also be regarded as a collocation method with respect to the trial
% space spanned by the generator $\varphi_P$.

We now describe a two-stage model that relies on two spaces: a desired
target space $\aspace{\lattice{L}_h}{\varphi_p}$ spanned by the
generator $\varphi_p$ where $\order{\lattice{L}}{\varphi} = k$, and an
auxiliary space $\aspace{\lattice{L}_h}{\psi_p}$ spanned by the
generator $\psi_p$ where $\order{\lattice{L}}{\psi} \ge k$. In the
first stage, we use the interpolative model from the previous section
to seek an auxiliary solution that lies in
$\aspace{\lattice{L}_h}{\psi_p}$. Then, the auxiliary solution is
orthogonally projected to the target space
$\aspace{\lattice{L}_h}{\varphi_p}$. This method is similar to our
two-stage gradient estimation framework~\cite{hossain10}. Owing to the
shift-invariant nature of the spaces, the orthogonal projection is
tantamount to applying a digital filter to the first-stage
approximation coefficients as described below.

Let us denote the first-stage approximation coefficients as
$c_{\psi}[\vect{x}_j]$. These coefficients are obtained by applying the discrete
operator $l_{\psi}^{-1}$ to the samples of $f$ as given
in~\eqref{eq:approxHomogeneous}. The discretization $l_{\psi}^{-1}$ is obtained
from the interpolative model where the interpolation prefilter $p_\psi$ is derived
from the samples of the first-stage generator $\psi$. Now, if $\psi$ is chosen
to have a sufficiently high order, then we know that this auxiliary
approximation will be very close to the true solution. Therefore, we can use it
to find an approximation in our desired target space
$\aspace{\lattice{L}_h}{\varphi}$. In particular, we orthogonally project the
auxiliary approximation onto the target space so as to minimize the $L_2$ error.
The orthogonal projection is obtained by taking inner products of the auxiliary
approximation with the lattice translates of $\dual{\varphi}_p$: the dual of the
target space generator $\varphi_p$. In particular, the second-stage
approximation can be written as
\begin{equation}
  \begin{split}
  & \appf{V}(\vect{x}) = \\
  & \sum_{j =1}^{2^s N} 
  \Bigl(
    \sum_{k = 1}^{2^s N}
    c_\psi \innerproduct{\psi_p(\frac{\cdot - \vect{x}_k}{h})}
    {h^{-s}\dual{\varphi}_p(\frac{\cdot - \vect{x}_j}{h})}
  \Bigr)
  \varphi_p(\frac{\vect{x}-\vect{x}_j}{h}).
\end{split}
\end{equation}
Assuming that $\psi$ and $\varphi$ are symmetric admissible
generators, this is equivalent to the digital filtering scheme
\begin{equation}
  \appf{V}(\vect{x}) = \sum_{j=1}^{2^s N} (c_\psi \pconv q_h)[\vect{x}_j]
  \varphi_p(\frac{\vect{x}-\vect{x}_j}{h}),
  \label{eq:quasiApprox}
\end{equation}
where the weights of the filter $q_h$ are obtained according to
\begin{equation}
  q_h[h\mat{L}\vect{k}] =  q[\mat{L}\vect{k}] := (\psi \ast
  \dual{\varphi})(\mat{L}\vect{k}).
  \label{eq:quasiWeights}
\end{equation}
Here, $(\psi \ast \dual{\varphi})$ denotes the continuous convolution
of the two generators $\psi$ and $\dual{\varphi}$ in $L_2(\reel^s)$.

An approximation model is said to be
quasi-interpolating of order $k$ if it is capable of reproducing all
multivariate polynomials in $\Pi_{k-1}(\reel^s)$, or  equivalently,
$E_{\mathsf{res}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2m})$  ($m \ge k$)
where $E_{\mathsf{res}}$ is as defined in~\eqref{eq:scErrorKernel}. We retain
the same terminology and say that an approximate solution to the Poisson
equation~\eqref{eq:PoissonEquation} is quasi-interpolating of order $k$ if it
satisfies $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2m})$,
where $m \ge k$. The following proposition gives us a way of choosing the
auxiliary space $\aspace{\lattice{L}_h}{\psi_p}$ so as to ensure that the
resulting approximation~\eqref{eq:quasiApprox} is quasi-interpolating of order
$k$.

\begin{prop}
  Let $\aspace{\lattice{L}_h}{\psi_p}$ and
  $\aspace{\lattice{L}_h}{\varphi_p}$ be the auxiliary and target
  approximation spaces respectively, with $\order{\lattice{L}}{\psi} = m$ and
  $\order{\lattice{L}}{\varphi} = k$. The approximation $\appf{V}$ obtained
  through \eqref{eq:quasiApprox} is quasi-interpolating of order $k$
  if $m \ge k$.
\label{prop:2}
\end{prop}
Please refer to Appendix~\ref{app:proofs} for the proof.\\
We note that when the auxiliary space is chosen to be the same as the
target space, i.e. when $\psi = \varphi$, then $q[\mat{L}\vect{k}] =
\delta[\vect{k}]$, this scheme reduces to the interpolative model
described in the previous section.

### 2015-09-09 poisson_errker.tex
Committing lost work from laptop

@@
 \end{equation}
-where $\laplacian$ is the $s$-dimensional Laplace operator and
-$\partial \ucube^s$ denotes the boundary of $\ucube^s$,
-i.e. $\partial \ucube^s \cup \oucube^s = \ucube^s$.
+where $\laplacian$ is the $s$-dimensional Laplace operator and $\partial \ucube^s$ denotes the boundary of $\ucube^s$, i.e. $\partial \ucube^s \cup \oucube^s = \ucube^s$.
 
@@
 When the domain of interest is the unit cube $\ucube^s$, the solution can be analytically expressed in terms of a Green's function $\mathsf{G}(\vect{x},\vect{y})$ that represents the potential due to a point source placed at the location $\vect{x}$ inside $\ucube^s$.
-In other words $\laplacian_{\vect{x}} \mathsf{G}(\vect{x},\vect{y}) = \delta(\vect{x}-\vect{y})$.
-The Green's function $\mathsf{G}$ has the Fourier Sine series expansion
+In other words $\laplacian_{\vect{x}} \mathsf{G}(\vect{x},\vect{y}) = \delta(\vect{x}-\vect{y})$. The Green's function $\mathsf{G}$ has the Fourier Sine series expansion 
 \begin{equation}
@@
 \subsection{Fourier Interpretation}
-
-Even though there has been much effort on finding alternate rapidly
-convergent series representations of the Green's function (see
-e.g. Marshall~\cite{marshall99}), it turns out that the form of the
-Green's function given in~\eqref{eq:green}, is ideally suited
-for our needs as it allows us to easily express the solution in the
-Fourier domain in terms of the Fourier coefficients of $f$.
+Even though there has been much effort on finding alternate rapidly convergent series representations of the Green's function (see e.g.
+Marshall~\cite{marshall99}), it turns out that the form of the Green's function given in~\eqref{eq:green}, is ideally suited for our needs as it allows us to easily express the solution in the Fourier domain in terms of the Fourier coefficients of $f$.
 

### 2015-09-09 approach.tex
Cleaning up.

@@
 From the oriented surface samples, we construct the approximation $\vec{V}(\vx)$ using our variational formulation. 
-We then apply FIR filters to the coefficients of the approximation to construct a scalar field representing the approximate divergence of the smoothed normal field (\FG{fig:pipeline}c.) We then use an appropriate discretization of the inverse Laplacian operator to solve the Poisson equation \EQ{eq:poisson}, and obtain a smooth function that approximates the original indicator function (\FG{fig:pipeline}c).
+We then apply FIR filters to the coefficients of the approximation to construct a scalar field representing the approximate divergence of the smoothed normal field (\FG{fig:pipeline}c.) 
+Using appropriate discretization of the inverse Laplacian operator we then solve the Poisson equation \EQ{eq:poisson}, and obtain a smooth function that approximates the original indicator function (\FG{fig:pipeline}c).
 Our code is also freely available for download.
@@
 Secondly, it will allow us to construct divergence of the smoothed normal field from more than three principal lattice directions. 
-We also allow each function $\upsilon_i$ to potentially be represented in different function spaces, i.e.
-{\small
+We also allow each function $\upsilon_i$ to potentially be represented in different function spaces, i.e. {\small 
 \begin{equation} 
@@
 \end{equation}}
-The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$.We use the unfortunate notation $\text{v}_j^i, \varphi_k^i$ to denote that those objects belong to $\upsilon_i(x)$, not to denote exponentiation.
+The coefficient vector of $\upsilon_i$ is denoted as $\mathbf{v}_i:=\left[\text{v}_1^i \ \cdots \ \text{v}_N^i \right]$.
+We use the unfortunate notation $\text{v}_j^i, \varphi_k^i$ to denote that those objects belong to $\upsilon_i(x)$, not to denote exponentiation. 
 We consider each component of $\vec{V}(\vx)$ separately, thus, it suffices to describe the process at one $\upsilon_i$. 
@@
 \end{equation} }
-Where $(\mathbf{L}^{-1})_i$ is the $i^{th}$ column of $(\mathbf{L}^{-1}).$ As before, this provides us with a parametrized way of controlling the smoothness of the resulting approximation, without the need to explicitly choose a smoothing kernel.
+Where $(\mathbf{L}^{-1})_i$ is the $i^{th}$ column of $(\mathbf{L}^{-1}).$ 
+As before, this provides us with a parametrized way of controlling the smoothness of the resulting approximation, without the need to explicitly choose a smoothing kernel. 
 These $\mathbf{v}_i$ can be obtained using the procedure of \SC{sec:vari_review}.
@@
 To reconstruct within a shifted space, the input point-set is shifted by $\frac{1}{2}\mathbf{b_i}$ then reconstructed within $\fspce{\varphi}{L}$. 
-This is clearly equivalent to reconstructing in a shifted basis space, however, care must be taken to ensure that the data are brought back to a centered representation.
+This is equivalent to reconstructing in a shifted basis space, however, care must be taken to ensure that the data are brought back to a centered representation. 
 Our choice of a shifted derivative filter $s[n]$ accounts for this and brings the resulting approximation back to the unshifted space. 
@@
 Thus, we may choose $\mathbf{L} = \mathbf{\Xii_{B}} $ as the basis for our function. 
-To accommodate for this, we redefine $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T$ Since this matrix is not square, it is not possible to take its inverse in \EQ{eq:vari_eqn}.
+To accommodate for this, we redefine $\vec{V}(\vx):=\mathbf{L} \left[\upsilon_1 \ \upsilon_2 \ \upsilon_3 \ \upsilon_4 \right.]^T$ 
+Since this matrix is not square, it is not generally possible to take its inverse in \EQ{eq:vari_eqn}. 
 Instead, the least norm inverse $\mathbf{L^T(LL}^T\mathbf{)}^{-1}$ is used. 

### 2015-09-09 conclusion.tex
Cleaning up.

@@
 However, our method fails to be as robust as the Screened Poisson algorithm when the data are non-uniform. 
-We speculate that this is due to the fact that we employ no heuristics to account for the deviation from the assumption of uniformity (\FG{fig:r2}.)
+We speculate that this is due to the fact that we employ no heuristics to account for the deviation from the assumption of uniformity (\FG{fig:r2}).
 
@@
 However, we observed that when $\lambda_2$ passed below a threshold, the surface began to show ringing or aliasing artifacts. 
+% What do I mean here? This is also very awkward...
 This is somewhat to be expected, as choosing a very thin smoothing will cause the approximation \EQ{eq:vdef} to break down. 
@@
 More investigation and exploration of the parameter space is required. 
-Moreover, there also appears to be a point at which choosing $\lambda_2$ to be too small introduces aliasing artifacts.
+Moreover, there also appears to be a point at which choosing $\lambda_2$ to be too small introduces aliasing artefacts.
 

### 2015-09-09 introduction.tex
Cleaning up.

@@
 Interest in this problem is rooted in the desire to convert real life data-sets -- data acquired from range scanners and now increasingly from commodity hardware like the Kinect -- to 3D polygonal models.
-The idea also has a applications in model re-meshing and mesh hole filling, when one has a poorly formatted mesh and would like a better representation of it.
+It also has applications in model re-meshing and mesh hole filling, when one has a poorly structured mesh and would like a better representation of it.
 
@@
 In this work we take a ``signal processing'' approach to this problem -- we cast the problem into a general shift-invariant setting. 
-More explicitly, we reconstruct the desired implicit function within a function space spanned by lattice translates of a single generating function.
-The extension to this class of function spaces allows us to consider anchoring our basis functions at non-Cartesian lattice sites (\SC{sec:smpl_review}).
+More explicitly, we reconstruct the desired implicit function within a space spanned by lattice translates of a single generating function. 
+The extension to this class of function spaces allows us to anchor our basis functions at non-Cartesian lattice sites (\SC{sec:smpl_review}).
 Our approach is general and applicable to any valid lattice and generator, but our implementation is narrowed to applicable function spaces over the \emph{Body Centred Cubic} (BCC) and \emph{Cartesian} (CC) lattices.
@@
 First, it's well known that the BCC lattice generates the optimal sampling pattern in $\realn^3$. 
-The argument for optimality is simple; the sampling of a function with respect to the BCC lattice is equivalent to a periodization of it's frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice.
+The argument for optimality is simple; the sampling of a function with respect to the BCC lattice is equivalent to a periodization of it's Fourier frequency spectrum about the BCC's dual lattice, the \emph{Face Centered Cubic} (FCC) lattice.
 Optimality follows from the observation that the FCC lattice is the optimal sphere packing lattice in three dimensions, that is, it packs frequency replica as tightly as possible in the Fourier domain, resulting in less \emph{pre-aliasing} from sampling.
@@
 First, we construct a smoothed approximation to the gradient field of a model's indicator function. 
-The divergence of the gradient field is estimated and subsequently fed into a Poisson solver that outputs the coefficients needed to approximate the smoothed indicator function in a target shift invariant space.
+We then estimate the divergence of that gradient field and feed it into a Poisson solver that outputs the coefficients needed to approximate the smoothed indicator function in a target shift invariant space.
 This Poisson solver is tailored to cater to the approximation power provided by each space. 

### 2015-09-09 poisson_errker.tex
Cleaning up.

@@
 
-Suppose we are given an $L_2(\ucube^s)$ function $\rho(
-\vect{x})$ that is
-defined on the open unit cube $\oucube^s$. In order to obtain a
-Fourier sine series that converges to $\rho$ almost everywhere in
-$\oucube^s$, we need to extend $\rho$ periodically such that it is odd
-with respect to each variable. Particularly, let us extend the domain
-of $\rho$ so that, within the interval $\cube^s$, it satisfies
+Suppose we are given an $L_2(\ucube^s)$ function $\rho(\vect{x})$ that is defined on the open unit cube $\oucube^s$. 
+In order to obtain a Fourier sine series that converges to $\rho$ almost everywhere in
+$\oucube^s$, we need to extend $\rho$ periodically such that it is odd with respect to each variable. 
+Particularly, let us extend the domain of $\rho$ so that, within the interval $\cube^s$, it satisfies
 {\small
@@
 }
-
-while outside $\cube^s$, it is $\cube^s$-periodic, i.e. $\rho(\vect{x}
-+ 2\vect{k}) = \rho(\vect{x})$ for $\vect{k} \in \ints^s$. The
-extended function $\rho$ can be developed into a multidimensional
-Fourier sine series, the coefficients of which are given by 
+while outside $\cube^s$, it is $\cube^s$-periodic, i.e. $\rho(\vect{x} + 2\vect{k}) = \rho(\vect{x})$ for $\vect{k} \in \ints^s$. 
+The extended function $\rho$ can be developed into a multidimensional Fourier sine series, the coefficients of which are given by 
 \begin{equation}
@@
 \end{equation}
-The coefficient sequence $\st{\rho}[\vect{m}]$ can also be seen as a
-special case of the more general multidimensional Fourier
-series. In fact, with an odd extension of the sequence $\st{\rho}$, the
-function $\rho$ can be expressed as a Fourier series. In particular,
-if we define the Fourier series coefficients $\ft{\rho}[\vect{m}]$
+The coefficient sequence $\st{\rho}[\vect{m}]$ can also be seen as a special case of the more general multidimensional Fourier series. 
+In fact, with an odd extension of the sequence $\st{\rho}$, the function $\rho$ can be expressed as a Fourier series. 
+In particular, if we define the Fourier series coefficients $\ft{\rho}[\vect{m}]$
 (for $\vect{m} \in \ints^s$) as
@@
 
-Since the Green's function $\mathsf{G}$ is defined in $\oucube^s$ and has a
-Fourier sine series representation, it is natural to seek a solution
-that can be developed into a Fourier sine series as
-well. Consequently, for the remainder of this section, we shall only
-be dealing with Fourier sine series. Therefore, it suffices to
-consider only the coefficients in $\ints^s_+$.
+Since the Green's function $\mathsf{G}$ is defined in $\oucube^s$ and has a Fourier sine series representation, it is natural to seek a solution that can be developed into a Fourier sine series as well.
+Consequently, for the remainder of this section, we shall only be dealing with Fourier sine series. 
+Therefore, it suffices to consider only the coefficients in $\ints^s_+$.
 
-Using the analytic solution~\eqref{eq:analytic} and the sine series
-representation of the Green's function~\eqref{eq:green}, it is easy to show that
-the solution is given by
+Using the analytic solution~\eqref{eq:analytic} and the sine series representation of the Green's function~\eqref{eq:green}, it is easy to show that the solution is given by
 \begin{equation}
@@
 \end{equation}
-where $\vect{m} \in \ints^s_+$ and $\st{f}[\cdot]$ represents the Fourier
-sine series coefficients of the odd extension of $f$. To facilitate subsequent
-discussions, let us introduce the solution operator
-$\stpairs{\invlaplacian}{\frac{1}{-\pi^2 \norm{\vect{m}}^2}}$  ($\vect{m} \in
+where $\vect{m} \in \ints^s_+$ and $\st{f}[\cdot]$ represents the Fourier  sine series coefficients of the odd extension of $f$. 
+To facilitate subsequent discussions, let us introduce the solution operator $\stpairs{\invlaplacian}{\frac{1}{-\pi^2 \norm{\vect{m}}^2}}$  ($\vect{m} \in
 \ints^s_+$), where the symbol $\stpairs{}{}$ represents how the Fourier sine
@@
 %\end{equation}
-The self-adjoint operator $\invlaplacian$ is the inverse of the Laplace
-operator. Self-adjointness can be easily verified with
-the aid of Parseval's relation, which states that
+The self-adjoint operator $\invlaplacian$ is the inverse of the Laplace operator. 
+Self-adjointness can be easily verified with the aid of Parseval's relation, which states that
 $
@@
 $
-for any $\cube^s$-periodic functions $a$ and $b$ that are in
-$L_2(\cube^s)$ and odd.
+for any $\cube^s$-periodic functions $a$ and $b$ that are in $L_2(\cube^s)$ and odd.
 
@@
 \end{equation}
-where $\pointset{I}_h := \ocube^s \cap \{\vect{x} + \vect{m} :
-\vect{x} \in \lattice{L}_h \cap \oucube^s, \vect{m} \in \ints^s \}$
-consists of interior lattice points, while $\pointset{B}_h$ consists
-of extended boundary points, i.e. $\pointset{B}_h := (\lattice{L}_h
-\cap \partial\cube^s \cap (-1,1]^s) \cup (\lattice{L}_h \cap
-\ocube^s\backslash \pointset{I}_h)$. Two dimensional illustrations are
-shown in Figure~\ref{fig:pointset}. We note that with the above
-definition of $\pointset{I}_h$, the points $\vect{x}_j$ for $j \in
-\{1, \ldots, N\}$ are contained in the open unit cube $\oucube^s$
-whereas the remaining points ($\vect{x}_j$ for $j \in \{N+1, \ldots,
-2^sN\}$) lie outside. Furthermore, we assume
-that the lattice $\lattice{L}$ and the sampling rate $h$ are such that
-the set $\{\vect{x} + 2\vect{m} : \vect{x} \in \pointset{T}_h,
-\vect{m} \in \ints^s\} = \lattice{L}_h$. We remark that this
-requirement for $\lattice{L}_h$ is also
-satisfied by integration lattices that are commonly used
-to devise quadrature rules within the unit cube $\ucube^s$~\cite{nied92}.
+where $\pointset{I}_h := \ocube^s \cap \{\vect{x} + \vect{m} : \vect{x} \in \lattice{L}_h \cap \oucube^s, \vect{m} \in \ints^s \}$ consists of interior lattice points, while $\pointset{B}_h$ consists of extended boundary points, i.e.
+$\pointset{B}_h := (\lattice{L}_h
+\cap \partial\cube^s \cap (-1,1]^s) \cup (\lattice{L}_h \cap \ocube^s\backslash \pointset{I}_h)$. 
+Two dimensional illustrations are shown in Figure~\ref{fig:pointset}. 
+We note that with the above definition of $\pointset{I}_h$, the points $\vect{x}_j$ for $j \in \{1, \ldots, N\}$ are contained in the open unit cube $\oucube^s$ whereas the remaining points ($\vect{x}_j$ for $j \in \{N+1, \ldots, 2^sN\}$) lie outside.
+Furthermore, we assume that the lattice $\lattice{L}$ and the sampling rate $h$ are such that the set $\{\vect{x} + 2\vect{m} : \vect{x} \in \pointset{T}_h, \vect{m} \in \ints^s\} = \lattice{L}_h$. 
+We remark that this requirement for $\lattice{L}_h$ is also satisfied by integration lattices that are commonly used to devise quadrature rules within the unit cube $\ucube^s$~\cite{nied92}.
 \begin{figure}[t]
@@
 
-We denote the interior samples of $f$ as $f[\vect{x}_j] :=
-f(\vect{x}_j)$ where $\vect{x}_j \in \pointset{I}_h$. Note that
-$f[\vect{x}_j]$ only needs to be known in $\oucube^s$ ($j \in
-\{1,\ldots,N\}$), the other samples can be inferred from
-oddity.
+We denote the interior samples of $f$ as $f[\vect{x}_j] := f(\vect{x}_j)$ where $\vect{x}_j \in \pointset{I}_h$. 
+Note that $f[\vect{x}_j]$ only needs to be known in $\oucube^s$ ($j \in
+\{1,\ldots,N\}$), the other samples can be inferred from oddity.
 
-We wish to use the samples of $f$ to approximate the function $\chi$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. Since
-$\chi$ is a periodic function, we follow the recipe of Jacob \textit{et al.}~\cite{jacob02} and seek an approximation that lies in a space generated by a periodic reconstruction function.
-Specifically, we are interested in the case
-where $\appf{\chi}$ lies in the space $\aspace{\lattice{L}_h}{\varphi_p} := \mathrm{span}_{\vect{x}_j\in\pointset{T}_h}\{
-\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}) \}$ that is spanned by the scaled and translated versions of a periodic function $\varphi_p$. Our approximation is given by
+We wish to use the samples of $f$ to approximate the function $\chi$ that solves the Poisson equation~\eqref{eq:PoissonEquation}. 
+Since $\chi$ is a periodic function, we follow the recipe of Jacob \textit{et al.}~\cite{jacob02} and seek an approximation that lies in a space generated by a periodic reconstruction function. 
+Specifically, we are interested in the case where $\appf{\chi}$ lies in the space $\aspace{\lattice{L}_h}{\varphi_p} := \mathrm{span}_{\vect{x}_j\in\pointset{T}_h}\{
+\varphi_p(\frac{\vect{x}-\vect{x}_j}{h}) \}$ that is spanned by the scaled and translated versions of a periodic function $\varphi_p$. 
+Our approximation is given by
 \begin{equation}
@@
 
-It is easy to verify that, with this definition of $\varphi_p$,
-$\appf{\chi}$ is also $\cube^s$-periodic. Even though we are only
-interested in the behavior of $\appf{V}$ inside $\ucube^s$, extending $\appf{\chi}$ to the entire domain $\cube^s$ using~\eqref{eq:ansatz} allows us to use the Fourier domain error kernel proposed by Jacob \textit{et.
+It is easy to verify that, with this definition of $\varphi_p$, $\appf{\chi}$ is also $\cube^s$-periodic. 
+Even though we are only interested in the behavior of $\appf{V}$ inside $\ucube^s$, extending $\appf{\chi}$ to the entire domain $\cube^s$ using~\eqref{eq:ansatz} allows us to use the Fourier domain error kernel proposed by Jacob \textit{et.
 al}~\cite{jacob02} to quantify the approximation error $\LLnorm{\chi - \appf{\chi}}$.
@@
 Another simplification is in order here. 
-Since the solution $\chi$ to the Poisson problem~\eqref{eq:PoissonEquation} is odd with respect to each variable, we look for an approximate solution $\appf{\chi} \in \aspace{\lattice{L}_h}{\varphi_p}$
-that is also odd in each variable. This can be achieved by setting
-the boundary coefficients to zero and by requiring that the resulting sequence be odd.  With $c[\vect{x}_j] = 0$ for $\vect{x}_j \in \pointset{B}_h$, the approximation~\eqref{eq:ansatz} simplifies to
+Since the solution $\chi$ to the Poisson problem~\eqref{eq:PoissonEquation} is odd with respect to each variable, we look for an approximate solution $\appf{\chi} \in \aspace{\lattice{L}_h}{\varphi_p}$ that is also odd in each variable.
+This can be achieved by setting the boundary coefficients to zero and by requiring that the resulting sequence be odd. 
+With $c[\vect{x}_j] = 0$ for $\vect{x}_j \in \pointset{B}_h$, the approximation~\eqref{eq:ansatz} simplifies to
 \begin{equation}
@@
 \end{equation}
-If the generator $\varphi$ is even and the sequence $c[\cdot]$ is odd,
-the resulting approximation $\appf{V}$ is odd and satifies zero
-Dirichlet boundary conditions (see Appendix~\ref{app:1}). With this
-simplification, the coefficient sequence $c[\vect{x}_j]$ only needs to
-be determined for $j \in \{1,\ldots,N\}$. The rest can be inferred
-from oddity.
+If the generator $\varphi$ is even and the sequence $c[\cdot]$ is odd, the resulting approximation $\appf{V}$ is odd and satifies zero Dirichlet boundary conditions (see Appendix~\ref{app:1}). 
+With this simplification, the coefficient sequence $c[\vect{x}_j]$ only needs to be determined for $j \in \{1,\ldots,N\}$. The rest can be inferred from oddity.
 
@@
 \label{sec:periodicErrorKernel}
-In many approximation problems involving periodic functions, one is interested
-in seeking an approximation $\appf{z}$ of a periodic function $z$ from its
-measurements that lie on some sampling lattice. In light of the notations
-introduced earlier, suppose that $z \in L_2(\cube^s)$ and is also
-$\cube^s$-periodic. Additionally, suppose that the measurements are made at the
-locations $\vect{x}_j \in \pointset{T}_h$ so that one can obtain an
-approximation $\appf{z}$ that belongs to  $\aspace{\lattice{L}_h}{\varphi_p}$
-and --- in a manner similar to the expansion~\eqref{eq:ansatz} --- is given by
+In many approximation problems involving periodic functions, one is interested in seeking an approximation $\appf{z}$ of a periodic function $z$ from its measurements that lie on some sampling lattice.
+In light of the notations introduced earlier, suppose that $z \in L_2(\cube^s)$ and is also $\cube^s$-periodic. 
+Additionally, suppose that the measurements are made at the locations $\vect{x}_j \in \pointset{T}_h$ so that one can obtain an approximation $\appf{z}$ that belongs to  $\aspace{\lattice{L}_h}{\varphi_p}$ and --- in a manner similar to the expansion~\eqref{eq:ansatz} --- is given by
 $
@@
 $
-where the
-coefficient sequence $\zeta[\cdot]$ is obtained through the discrete
-measurements
+where the coefficient sequence $\zeta[\cdot]$ is obtained through the discrete measurements
 \begin{equation}
@@
 \end{equation}
-made with the scaled and shifted versions of a periodic analysis
-function $\analysis{\varphi}_p(\vect{x})$ (the periodization operation
-is defined by~\eqref{eq:periodization}). The main result of Jacob
-\textit{et al.}~\cite{jacob02} states that the mean square
-approximation error $\LLnorm{z - \appf{z}}$ at scale $h$ can
-be predicted according to
+made with the scaled and shifted versions of a periodic analysis function $\analysis{\varphi}_p(\vect{x})$ (the periodization operation is defined by~\eqref{eq:periodization}). 
+The main result of Jacob \textit{et al.}~\cite{jacob02} states that the mean square approximation error $\LLnorm{z - \appf{z}}$ at scale $h$ can be predicted according to
 \begin{equation}
@@
 \end{equation}
-where $\ft{z}[\vect{m}]$ are the Fourier series coefficients of $z$
-and $E(\cdot)$ is the error kernel of Blu and Unser~\cite{blu99}
-introduced earlier~\eqref{eq:scErrorKernel}.  Remarkably, the same
-error kernel can be used to predict the error for periodic and
-non-periodic functions alike. The only change that needs to be made is
-in the prediction equation. For functions in $L_2(\reel^s)$, the error
-is predicted according to the integral in~\eqref{eq:avgError}. On the
-other hand, for periodic functions that belong to $L_2(\cube^s)$, the
-prediction equation turns into the summation given
-in~\eqref{eq:prediction}. We refer the reader to Jacob \textit{et
-  al.}~\cite{jacob02} for details.
+where $\ft{z}[\vect{m}]$ are the Fourier series coefficients of $z$ and $E(\cdot)$ is the error kernel of Blu and Unser~\cite{blu99} introduced earlier~\eqref{eq:scErrorKernel}.
+Remarkably, the same error kernel can be used to predict the error for periodic and
+non-periodic functions alike. 
+The only change that needs to be made is in the prediction equation. 
+For functions in $L_2(\reel^s)$, the error is predicted according to the integral in~\eqref{eq:avgError}. 
+On the other hand, for periodic functions that belong to $L_2(\cube^s)$, the prediction equation turns into the summation given in~\eqref{eq:prediction}. 
+We refer the reader to Jacob \textit{et al.}~\cite{jacob02} for details.
 
 \subsubsection{Extension to Linear Operators}
-We are interested in approximating from the discrete measurements
-of $z$, not the function $z$ itself but a function $\Gamma z$ that is obtained
-by applying the linear operator $\Gamma$ to $z$. 
+We are interested in approximating from the discrete measurements of $z$, not the function $z$ itself but a function $\Gamma z$ that is obtained by applying the linear operator $\Gamma$ to $z$. 
 % This is exactly the problem we
@@
 % solution~\eqref{eq:fourierSolution} to Poisson's equation. 
-We would like to
-extend the error kernel formulation~\eqref{eq:scErrorKernel} so that it will
-allow us to quantify the error incurred in approximating $\Gamma z$ from the
-measurements of $z$. Towards this end, we assume that the approximation
-$\appf{(\Gamma z)}$ lies in a shift-invariant space spanned by the generator
-$\varphi_p$, where the coefficients are obtained from the measurements through a
-digital filtering operation. Particularly, we seek an approximation that is
-given by
+We would like to extend the error kernel formulation~\eqref{eq:scErrorKernel} so that it will allow us to quantify the error incurred in approximating $\Gamma z$ from the measurements of $z$. 
+Towards this end, we assume that the approximation $\appf{(\Gamma z)}$ lies in a shift-invariant space spanned by the generator $\varphi_p$, where the coefficients are obtained from the measurements through a digital filtering operation.
+Particularly, we seek an approximation that is given by
 \begin{equation}
@@
 \end{equation}
-where $\zeta$ denotes the discrete measurements of $z$ obtained
-through~\eqref{eq:measurements}, $\gamma$ is a digital filter defined on
-the lattice $\lattice{L}$ and $\gamma_h$ is its corresponding scaled
-version, i.e. $\gamma_h[\vect{x}_j] := \gamma[\tfrac{\vect{x}_j}{h}]$ where
-$\tfrac{\vect{x}_j}{h} \in \lattice{L}$, and $C_h$ is an associated
-scaling constant. The digital filter $\gamma$ represents a suitable
-discretization of the operator $\Gamma$ on the lattice $\lattice{L}$. It is
-to be applied to the measurements through a cyclic convolution
-operation (denoted by $\pconv$) on the lattice $\lattice{L}_h$ using a
-periodized version of $\gamma_h$. In particular, the convolution operation
-in~\eqref{eq:opApproximation} is defined as
+where $\zeta$ denotes the discrete measurements of $z$ obtained through~\eqref{eq:measurements}, $\gamma$ is a digital filter defined on the lattice $\lattice{L}$ and $\gamma_h$ is its corresponding scaled version, i.e.
+$\gamma_h[\vect{x}_j] := \gamma[\tfrac{\vect{x}_j}{h}]$ where $\tfrac{\vect{x}_j}{h} \in \lattice{L}$, and $C_h$ is an associated scaling constant.
+The digital filter $\gamma$ represents a suitable discretization of the operator $\Gamma$ on the lattice $\lattice{L}$. 
+It is to be applied to the measurements through a cyclic convolution operation (denoted by $\pconv$) on the lattice $\lattice{L}_h$ using a periodized version of $\gamma_h$. 
+In particular, the convolution operation in~\eqref{eq:opApproximation} is defined as
 \begin{equation}
@@
 \end{equation}
-where $\vect{x}_j \in \lattice{L}_h$. In the above definition,
-$\zeta[\cdot]$ is assumed to be $\cube^s$-periodic.  Furthermore, the
-resulting sequence $(\zeta \pconv \gamma_h)[\cdot]$ is also
-$\cube^s$-periodic.
+where $\vect{x}_j \in \lattice{L}_h$. 
+In the above definition, $\zeta[\cdot]$ is assumed to be $\cube^s$-periodic.
+Furthermore, the resulting sequence $(\zeta \pconv \gamma_h)[\cdot]$ is also $\cube^s$-periodic.
 
@@
 % is periodic.
-Let $\ft{\Gamma}(\vect{\omega})$ be the Fourier transform of the operator
-$\Gamma$, and $\ft{G}(\vect{\omega})$ be the DTFT of the filter $\gamma$.
+Let $\ft{\Gamma}(\vect{\omega})$ be the Fourier transform of the operator $\Gamma$, and $\ft{G}(\vect{\omega})$ be the DTFT of the filter $\gamma$.
 Furthermore, let $\Gamma$ be bounded so that $\Gamma z \in L_2(\cube^s)$.
-A simple modification of the measurement process~\eqref{eq:measurements} yields
-the desired extension of the error kernel formulation~\eqref{eq:scErrorKernel}.
+A simple modification of the measurement process~\eqref{eq:measurements} yields the desired extension of the error kernel formulation~\eqref{eq:scErrorKernel}.
 Our main result can be summarised as follows.
 \begin{thm}
-  Suppose that $\Gamma$ is self-adjoint and shift-invariant. The Fourier
-  error kernel that predicts the approximation error
+  Suppose that $\Gamma$ is self-adjoint and shift-invariant. 
+  The Fourier error kernel that predicts the approximation error
   $\LLnorm{\appf{(\Gamma z)} - \Gamma z}$ is given by $E(\vect{\omega}) :=
@@
 
-Note that, even though the operator $\Gamma$ acts in the space $L_2(\cube^s)$,
-it is extended to the more general space $L_2(\reel^s)$ in this error kernel
-formulation.
-Therefore,~\eqref{eq:opResidue} can be used to quantify the $L_2$ error in both
-$L_2(\reel^s)$ and $L_2(\cube^s)$. Going back to the original
-problem~\eqref{eq:PoissonEquation}, Theorem~\ref{thm:1} gives us a way to design
-and analyze digital filtering solutions that approximate the analytic
-solution~\eqref{eq:fourierSolution}. In particular, the linear operator that we
-wish to discretize is $\invlaplacian$. In the sequel, we show how to use the
-modified residue error kernel~\eqref{eq:opResidue} to design filtering schemes
-that discretize this operator and can be efficiently implemented in the
+Note that, even though the operator $\Gamma$ acts in the space $L_2(\cube^s)$, it is extended to the more general space $L_2(\reel^s)$ in this error kernel formulation.
+Therefore,~\eqref{eq:opResidue} can be used to quantify the $L_2$ error in both $L_2(\reel^s)$ and $L_2(\cube^s)$. 
+Going back to the original problem~\eqref{eq:PoissonEquation}, Theorem~\ref{thm:1} gives us a way to design and analyze digital filtering solutions that approximate the analytic
+solution~\eqref{eq:fourierSolution}. 
+In particular, the linear operator that we wish to discretize is $\invlaplacian$.
+In the sequel, we show how to use the modified residue error kernel~\eqref{eq:opResidue} to design filtering schemes that discretize this operator and can be efficiently implemented in the
 Fourier domain.
 
-In order to characterize the order of accuracy provided by a periodic
-generating function $\varphi_p$, we shall switch to the more general
-space $L_2(\reel^s)$.  The link between the approximation properties
-of $\varphi$ and those of its periodized version $\varphi_p$ is
-established by the error kernel formulation introduced
-in~\SC{sec:periodicErrorKernel}. Since the same kernel can be used in
-both cases, henceforth, we shall reason about the approximation
-properties of the generator $\varphi$ as the same properties are also
+In order to characterize the order of accuracy provided by a periodic generating function $\varphi_p$, we shall switch to the more general space $L_2(\reel^s)$.
+The link between the approximation properties of $\varphi$ and those of its periodized version $\varphi_p$ is
+established by the error kernel formulation introduced in~\SC{sec:periodicErrorKernel}.
+Since the same kernel can be used in both cases, henceforth, we shall reason about the approximation properties of the generator $\varphi$ as the same properties are also
 applicable to its periodized counterpart $\varphi_p$.
 
-In many approximation scenarios, one typically assumes a Dirac point sampling
-model, i.e. $\analysis{\varphi}(\vect{x}) = \delta(\vect{x})$.
+In many approximation scenarios, one typically assumes a Dirac point sampling model, i.e. $\analysis{\varphi}(\vect{x}) = \delta(\vect{x})$.
 This prevents the direct realization of the minimum approximation scenario. 
-Furthermore, for many functions encountered in practice, the power spectrum is
-concentrated around $\vect{\omega} = 0$. For such scenarios, one speaks of an
-\emph{asymptotically optimal} $k$-th order approximation scheme if the $L_2$
-error behaves as $O(h^k)$ where $k = \order{\lattice{L}}{\varphi}$. Our operator
-discretization approach is also based on these assumptions.
-Provided that $\chi$ has appropriate smoothness, our goal is to design suitable digital filters that yield %$V \in W_2^k(\cube^s)$, our goal is to design suitable digital filters that yield
-$\appf{\chi}$ such that $\LLnorm{\chi - \appf{chi}} = O(h^k)$.
-%As discussed earlier in~\SC{sec:interpQuasiInterp}, the criterion that needs to be satisfied is $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$.
+Furthermore, for many functions encountered in practice, the power spectrum is concentrated around $\vect{\omega} = 0$. 
+For such scenarios, one speaks of an \emph{asymptotically optimal} $k$-th order approximation scheme if the $L_2$ error behaves as $O(h^k)$ where $k = \order{\lattice{L}}{\varphi}$. 
+Our operator discretization approach is also based on these assumptions. 
+Provided that $\chi$ has appropriate smoothness, our goal is to design suitable digital filters that yield  $\appf{\chi}$ such that $\LLnorm{\chi - \appf{chi}} = O(h^k)$.
 
@@
 Rather, a zero boundary condition is implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be odd. 
-% as explained in~\SC{sub:approximatesol}.
 Here, we establish the connection for the homogeneous case but the analysis also easily extends to the non-homogeneous case, as well as to other types of differential operators.
@@
 \end{equation}
-where the functions $u$ are suitable test functions. The functional
-$\mathcal{F}(\cdot)$ is defined as $\mathcal{F}(u) :=
-\innerproduct{\invlaplacian f}{u}$, where $f$ is the odd extension of
-the function that appears on the right hand side
-of~\eqref{eq:PoissonEquation}, and the operator
-$\stpairs{\invlaplacian}{\tfrac{1}{-\pi^2\norm{\vect{m}}^2}}$ has the
-interpretation of the inverse Laplacian as introduced
-in~\eqref{eq:fourierSolution}. We remark that this formulation is
-slightly stronger than the usual weak formulations based on the
-Laplacian $\laplacian$ where the trial and test spaces coincide with
-the Sobolev space $W_2^1(\cube^s)$. In comparison, here the trial and
-test spaces coincide with the more general space $L_2(\cube^s)$. This
-formulation is also in direct correspondence with our earlier
-treatment of the problem.
+where the functions $u$ are suitable test functions. 
+The functional $\mathcal{F}(\cdot)$ is defined as $\mathcal{F}(u) := \innerproduct{\invlaplacian f}{u}$, where $f$ is the odd extension of the function that appears on the right hand side
+of~\eqref{eq:PoissonEquation}, and the operator $\stpairs{\invlaplacian}{\tfrac{1}{-\pi^2\norm{\vect{m}}^2}}$ has the interpretation of the inverse Laplacian as introduced in~\eqref{eq:fourierSolution}.
+We remark that this formulation is slightly stronger than the usual weak formulations based on the Laplacian $\laplacian$ where the trial and test spaces coincide with the Sobolev space $W_2^1(\cube^s)$.
+In comparison, here the trial and test spaces coincide with the more general space $L_2(\cube^s)$. This formulation is also in direct correspondence with our earlier treatment of the problem.
 
-Let us now restrict attention to the finite dimensional space
-$\aspace{\lattice{L}_h}{\varphi_p} \subset L_2(\cube^s)$. We seek a
-weak solution $\appf{\chi} \in \aspace{\lattice{L}_h}{\varphi_p}$ so that
+Let us now restrict attention to the finite dimensional space $\aspace{\lattice{L}_h}{\varphi_p} \subset L_2(\cube^s)$. 
+We seek a weak solution $\appf{\chi} \in \aspace{\lattice{L}_h}{\varphi_p}$ so that
 \begin{equation}
@@
 $\gamma[\vect{x}_j] = \delta[\vect{x}_j]$ in~\eqref{eq:opApproximation}), then the measurements obtained will realize the orthogonal projection of $\chi$ upon $\aspace{\lattice{L}_h}{\varphi_p}$.
-In this case, the modified Fourier residue error kernel~\eqref{eq:opResidue} vanishes, i.e.
-$E_{\mathsf{mod}}(\vect{\omega}) = 0$.
+In this case, the modified Fourier residue error kernel~\eqref{eq:opResidue} vanishes, i.e. $E_{\mathsf{mod}}(\vect{\omega}) = 0$.
 
@@
 procedure is to find a suitable correction filter $\gamma$ such that $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ where $k = \order{\lattice{L}}{\varphi}$.
-%If we define the analysis function
-%$\phi(\vect{x}) := \sum_{\vect{k} \in \ints^s} t[\vect{x}]
-%\delta(\vect{k} - \mat{L}\vect{k})$, then the criterion
-%$E_{\mathsf{res}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ is
-%equivalent to the requirement that the moments of $\phi$ and
-%$\invlaplacian \dual{\varphi}$ (here
-%$\ftpairs{\invlaplacian}{(-4\pi^2\norm{\vect{\omega}}^2)^{-1}}$) match
-%up to the order $k$, i.e.  $\int_{\reel^s}
-%\vect{x}^{\vect{\mu}}(\phi(\vect{x}) - \invlaplacian
-%\dual{\varphi}(\vect{x})) d\vect{x} = 0$ for $0 \le \abs{\vect{\mu}} <
-%k$. 
+
 In other words, our approximation procedure attempts to reproduce the Galerkin orthogonality condition given by~\eqref{eq:GalerkinOrthogonality}.
-%This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
-in~\SC{sec:interpQuasiInterp}.
+%This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced in~\SC{sec:interpQuasiInterp}.

### 2015-09-09 prelim.tex
Cleaning up.

@@
 	\end{cases}. 
-$$.
-The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, that approximates the smoothed gradient of the indicator function, finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small
+$$
+The key observation of the Poisson surface reconstruction formulation, is that if one obtains a function $\vec{V}(\vect{x})$ with $\vec{V}(\vect{x})\approx{\nabla}\chi_M$, (i.e, it approximates the smoothed gradient of the indicator function) finding an approximation to the indicator function reduces to finding a $\inda$ such that {\small
 \begin{equation} \label{eq:poisson}
@@
 
-Inspired by the approach of Kazhdan et al.~\cite{Kazhdan06} the approximation $\vec{V}(\vx)$ is defined to be  {\small 
+As in the approach of Kazhdan et al.~\cite{Kazhdan06} the approximation $\vec{V}(\vx)$ is defined to be  {\small 
 \begin{eqnarray}
@@
 Thus, $\vec{V}(\vx)$ approximates the gradient of the indicator smoothed by some filter $F$, broken up over surface patches of the model. 
-We assume the point sampling to be uniform, thus the area of each patch $\left|\patch_s\right|$ should be a constant, and our resulting approximation will be scaled by an unknown factor.
-We return to this in \SC{sec:levelset}.
+We assume the point sampling to be uniform, thus the area of each patch $\left|\patch_s\right|$ should be a constant, and our resulting approximation will be scaled by an unknown factor, we return to this in \SC{sec:levelset}.
 The choice of $F$ places computational constraints on the resulting algorithm.
@@
 
-Ideally, the filter $F$ should correspond to some globally supported RBF.
+Ideally, the filter $F$ could correspond to some globally supported RBF. 
 However, as the support of $F$ grows, so does the cost of evaluating it at lattice sites. 
@@
 Our approach circumvents the choice of $F$ entirely by posing the gradient approximation problem as a variational problem that, in addition to imposing the interpolation constraint, also imposes constraints on the ``compactness'' and ``smoothness'' of the gradient approximation.
-The only kernel we need to consider is the one that generates our target shift-invariant space, i.e.
-the space used to recover the smoothed indicator function.
+The only kernel we need to consider is the one that generates our target shift-invariant space, i.e. the space used to recover the smoothed indicator function. 
 This type of variational reconstruction can be seen as an approximation to radial basis approaches~\cite{variational}, and is well-suited to our Poisson formulation in shift-invariant spaces.
@@
 If $\mathbf{L}$ is a unimodular matrix, the set $\lattice{L} := \{\mathbf{L}\cdot\vect{n} : \vect{n} \in \intn^3 \}$ represents all possible sampling lattices. 
-$\mathbf{L}$ is often called the \emph{generating matrix} for a lattice, and we'll assume that $\mathbf{L}$ is normalized so that $\left|\det\mathbf{L}\right| = 1$.
+$\mathbf{L}$ is often called the \emph{generating matrix} for a lattice, and we will assume that $\mathbf{L}$ is normalized so that $\left|\det\mathbf{L}\right| = 1$. 
 The lattice's dual, denoted by $\duallattice{L}$, is the lattice generated by $\mathbf{L}^{-T}$.
@@
 However, the BCC lattice is non-separable, and requires special care in data retrieval and indexing. 
-\FG{fig:lattices} shows these lattices and their Voronoi regions, including the dual of the BCC lattice, the FCC lattice (the Cartesian lattice is dual to itself.)
+\FG{fig:lattices} shows these lattices and their Voronoi regions, including the dual of the BCC lattice, the FCC lattice (the Cartesian lattice is dual to itself).
 
@@
 Typically, as memory is a limited quantity, we are only interested in a finite number of points on a lattice. 
-We denote the set of such points as $\{\vect{s}_1,\vect{s}_2,\ \hdots  \ \vect{s}_N\} \subset \mathbf{L}\intn^3.$ Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\vect{s}_k)$; from this perspective, our function space is now {\small
+We denote the set of such points as $\{\vect{s}_1,\vect{s}_2,\ \hdots  \ \vect{s}_N\} \subset \mathbf{L}\intn^3.$ 
+Corresponding to each lattice site is a coefficient $c_k$; we collect all such coefficients in the column vector $\mathbf{c}:=\left[c_1 \ c_2 \ \hdots \ c_N \right]^T.$ 
+We also use the short hand notation $\varphi_k(\vx) := \varphi(\frac{\vx}{h}-\vect{s}_k)$; from this perspective, our function space is now {\small 
 \begin{equation}
@@
 Further, we denote $\mathbf{\Phii}$ to be the $M \times N$ matrix whose elements are given by sampling the basis functions anchored at each lattice site, or $P_{i,j} := \varphi_j(\vx_i)$. 
-Clearly, if our data are sampled at the lattice sites ($\vx_i = \vect{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\vect{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$ However, our sample locations are almost certain to not coincide with lattice sites and we must consider alternative schemes for finding $\mathbf{c}$, which we'll come back to in \SC{sec:vari_review}
+Clearly, if our data are sampled at the lattice sites ($\vx_i = \vect{s}_i$), then the problem of finding an interpolative scheme reduces to finding $\vect{c}$ such that $\mathbf{\Phii c=f},$ which only involves inverting the square matrix $\mathbf{\Phii}.$
+However, our sample locations are almost certain to not coincide with lattice sites and we must consider alternative schemes for finding $\mathbf{c}$, which we'll come back to in \SC{sec:vari_review}
 
@@
 \subsection{The Error Kernel}
-The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation
-$\appf{f} \in \aspace{\lattice{L}_h}{\varphi}$ can conveniently be
-quantified via an error kernel in the Fourier domain. It is defined as
+The error $\Ltwonorm{f - \appf{f}}$ between $f$ and its approximation $\appf{f} \in \aspace{\lattice{L}_h}{\varphi}$ can conveniently be quantified via an error kernel in the Fourier domain. 
+It is defined as
 \begin{equation}
@@
 \end{equation}
-For a bandlimited function $f$ whose spectrum is entirely contained
-within the Voronoi cell of $\duallattice{L}_h$ centered around $\vect{\omega} = 0$, we have 
+For a band-limited function $f$ whose spectrum is entirely contained within the Voronoi cell of $\duallattice{L}_h$ centered around $\vect{\omega} = 0$, we have 
 \begin{equation}
@@
 \subsection{Approximation Error}
-
 If the generating function that spans the space satisfies the \emph{Strang-Fix} conditions of order $k$, and $f$ belongs to the Sobolev space of at least order $k$, then it can be shown that the minimum approximation error (in the least-squares sense) decays asymptotically as $O(h^k)$, and the space is said to have approximation order $k$.
@@
 For sufficiently smooth functions $f$ that are uniformly sampled and properly prefiltered, the trilinear and linear reconstruction filters (Cartesian and BCC respectively) assure second order convergence, while the tricubic and Quintic assure fourth order.
-Another nicety of these spaces is that data processing techniques --- derivative approximation for example --- can often be represented by a convolution of the coefficient vector with either an \emph{Infinite Impulse Response} (IIR) or \emph{Finite Impulse Response} (FIR) filter.
+Another nicety of these spaces is that data processing techniques -- derivative approximation for example -- can often be represented by a convolution of the coefficient vector with either an \emph{Infinite Impulse Response} (IIR) or \emph{Finite Impulse Response} (FIR) filter.
 
 \subsection{Box Splines} \label{sec:box_review}
-Box splines are compact piece-wise polynomial functions $ M_\mathbf{\Xii} : \realn^s \to \realn.$ The matrix $\mathbf{\Xii}$ denotes a collection of direction vectors, $\mathbf{\Xii} := \left[ \xi_1 \ \xi_2 \hdots \xi_n\right].$ When $n=s$, the function $M_\mathbf{\Xii}(\vx)$ is defined to be ${1}/|{\det\mathbf{\Xii}}|$ inside the polytope formed by the Minkowski sum of the direction vectors of $\mathbf{\Xii}$, and zero otherwise (that is, ${1}/{|\det\mathbf{\Xii}|}$ when $\vx \in \{ \mathbf{\xi}_1 t_1 + \hdots + \mathbf{\xi}_s t_s  : t_i\in [0,1) \})$.
+Box splines are compact piece-wise polynomial functions $ M_\mathbf{\Xii} : \realn^s \to \realn.$ 
+The matrix $\mathbf{\Xii}$ denotes a collection of direction vectors, $\mathbf{\Xii} := \left[ \xi_1 \ \xi_2 \hdots \xi_n\right].$ 
+When $n=s$, the function $M_\mathbf{\Xii}(\vx)$ is defined to be ${1}/|{\det\mathbf{\Xii}}|$ inside the polytope formed by the Minkowski sum of the direction vectors of $\mathbf{\Xii}$, and zero otherwise (that is, ${1}/{|\det\mathbf{\Xii}|}$ when $\vx \in \{ \mathbf{\xi}_1 t_1 + \hdots + \mathbf{\xi}_s t_s  : t_i\in [0,1) \})$.
 When $n > s$, the box spline is recursively defined as {\small 
@@
 A solution to this problem is to ``re-sample'' the input point set onto said lattices sites.
-In the work by Kazdhan et al.
-\cite{fftk} the range data, $P$, are splatted via a linear filter onto a regular Cartesian grid.
+In the work by Kazdhan et al. \cite{fftk} the range data, $P$, are splatted via a linear filter onto a regular Cartesian grid. 
 This tends to over-smooth the resulting reconstruction, as it allows the surface to deviate from the original sample locations. 
@@
 The Beppo-Levi inner product of order $n$ is defined as $\blip{n}{f}{g}:= \sum_{|\mathbf{p}|=n}({n!}/{\mathbf{p}!}) \innerp{\mathbf{D^p}f}{\mathbf{D^p}g}$, where $\mathbf{p}$ is an integer vector such that $\left| \mathbf{p}\right| := p_1 + p_2 + p_3 $.
-We also use the short hand $\mathbf{D^p}f := \partial^{\left| \mathbf{p}\right|}f/({\partial^{p_1}x_1}{\partial^{p_2}x_2}{\partial^{p_3}x_3}).$ The second order Beppo-Levi norm of $f$ is defined as $\bln{2}{f}^2:=\blip{2}{f}{f}$.
+We also use the short hand $\mathbf{D^p}f := \partial^{\left| \mathbf{p}\right|}f/({\partial^{p_1}x_1}{\partial^{p_2}x_2}{\partial^{p_3}x_3}).$ 
+The second order Beppo-Levi norm of $f$ is defined as $\bln{2}{f}^2:=\blip{2}{f}{f}$.
 
@@
 This has the physical interpretation of forcing the solution to be close to zero everywhere except near the input points. 
-Our proposed cost functional is then $E(g) := \lambda_1 \left|\left|{g}\right|\right| + \lambda_2 \bln{2}{g}.$ Here, $\lambda_1$ controls the amount to which the function is penalized for large coefficient values.
+Our proposed cost functional is then $E(g) := \lambda_1 \left|\left|{g}\right|\right| + \lambda_2 \bln{2}{g}.$ 
+Here, $\lambda_1$ controls the amount to which the function is penalized for large coefficient values. 
 When combined with the interpolation constraint, this imposes the behavior of forcing the function to be zero away from the surface. 
@@
 Since $\varphi$ is known in closed form in our test cases, the entries of both $\mathbf{G}$ and $\mathbf{S}$ can be evaluated analytically. 
-The above vector equation can be solved using the Conjugate Gradient method.
+The above matrix equation can be solved using the Conjugate Gradient method.

### 2015-09-09 relatedwork.tex
Cleaning up.

@@
 \section{Related Work}
-Surface reconstruction is still a very active area of research in computer graphics and it's beyond the scope of this work to touch on all the material related to the subject.
+Surface reconstruction is a very active area of research in computer graphics and it's beyond the scope of this work to touch on all the material related to the subject.
 We therefore very briefly review some relevant contributions -- those seeking a more in-depth review may look to a recent survey of the field \cite{reconstar_eg14}.
-We focus mainly on some of the more related and recent developments.
+We focus mainly on some of the more recent and related work.
 
-Many surface reconstruction algorithms are so-called ``\emph{implicit}'' reconstruction algorithms. They attempt to 
-reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose level-set, for some iso-value $s \in \realn$, $f(\vect{x})=s$ represents an approximation to the original surface.
-Other non-implicit techniques generally infer meshes through some other combinatorial means or set predefined logic/rules.
+Many surface reconstruction algorithms are so-called ``\emph{implicit}'' reconstruction algorithms. 
+They attempt to reconstruct an implicit function, $f : \realn^3 \mapsto \realn $, whose level-set, for some iso-value $s \in \realn$, $f(\vect{x})=s$ represents an approximation to the original surface.
+Non-implicit techniques generally infer meshes through some other combinatorial means or set predefined logic/rules.
 
@@
 One of the most well known implicit algorithms is the algorithm of by Hoppe et al.~\cite{hoppecut}. In this work a set of
-tangent planes is constructed to create an approximation to a surface's distance function. A more recent work, is the Smoothed
-Signed Distance Field reconstruction technique \cite{ssdrecon}, in which an oriented point set imposes constraints on the reconstructed function, its gradient, and its Hessian.
-These constraints are equvalent to requiring that the reconstructed function be an approximation to the distance field of the original model.
+tangent planes is constructed to create an approximation to a surface's distance function. 
+A more recent work, is the Smoothed Signed Distance Field reconstruction technique \cite{ssdrecon}, in which an oriented point set imposes constraints on the reconstructed function, its gradient, and its Hessian.
+These constraints are equivalent to requiring that the reconstructed function be an approximation to the distance field of the original model. 
 Other techniques attempt to reconstruct a signed distance function within a function space spanned by radial basis functions \cite{radial}. 
-Recently, there has also been research that incorporates point normals into the radial basis reconstruction framework \cite{hermite}.
+Recently, there has also been work that incorporates point normals into a radial basis reconstruction framework \cite{hermite}. 
 It's also possible to construct an implicit function as a normalize sum of compactly supported basis functions defined over an oct-tree, essentially ``smearing'' the point-set around space and constructing an indicator ``shell'' around them \cite{Fuhrmann2014}.
 
-Another approach is to find an indicator function that approximates the ``inside-outside'' function of original model.
+Another implicit approach is to find an indicator function that approximates the ``inside-outside'' (indicator) function of original model. 
 An early technique \cite{fftk} transforms the smoothed gradient to the Fourier domain, applies an appropriate operator, then reconstructs it in the spatial domain. 
@@
 
-Poisson surface reconstruction techniques make the observation that the Fourier method is equivalently stated as a spatial Poisson problem \cite{Kazhdan06,screenedk}.
+Building on that work, Poisson surface reconstruction techniques make the observation that the Fourier method is equivalently stated as a spatial Poisson problem \cite{Kazhdan06,screenedk}. 
 Moreover, they seek to rectify the memory limitations of that work, while still maintaining its benefits.
@@
 This leads to a simple and efficient algorithm even when the data sets are massive. 
-However the method's speed comes at a price, as the resulting surfaces are often non-smooth, and display many ``jagged'' artifacts (although a form of smoothing is applied to the resulting indicator function in an attempt to rectify this.)
+However the method's speed comes at a price, as the resulting surfaces are often non-smooth, and display many ``jagged'' artefacts (although a form of smoothing is applied to the resulting indicator function in an attempt to rectify this.)
 
@@
 A crucial step in this regard is the accurate estimation of the divergence of the gradient field from the oriented point-set.
-Radial basis functions (RBFs) are generally used in the context of the reconstruction of scattered data, however, RBF techniques are often computationally expensive, requiring the solution of large unstable systems of equations (for exact interpolation.) A proposed solution to this problem is to ``\emph{re-sample}'' the input data onto a regular shift-invariant space.
+Radial basis functions (RBFs) are generally used in the context of the reconstruction of scattered data, however, RBF techniques are often computationally expensive, requiring the solution of large unstable systems of equations (for exact interpolation).
+A proposed solution to this problem is to ``\emph{re-sample}'' the input data onto a regular shift-invariant space. 
 This allows one to use efficient compact reconstruction kernels and data processing techniques \cite{variational,onvari}. 
@@
 
-Once, the smoothed gradient's divergence has been calculated, recovering the indicator function is a simple matter of taking the inverse of the Laplacian over domain (i.e.
-solving the Poisson system).
+Once the smoothed gradient's divergence has been calculated, recovering the indicator function is a simple matter of taking the inverse of the Laplacian over domain (i.e. solving the Poisson system). 
 To do this, we take an approach that is also inspired by filtering methodologies in signal processing.

### 2015-09-09 results.tex
Fixing filter table
Cleaning up.

@@
 \subsubsection{Basis function}
-Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial.
-It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions.
+Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a tri-linear piecewise polynomial. 
+By definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions.
 Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ \Xii_{C2} \ \Xii_{C2} \right]}$. 
@@
 \end{equation*}}
-
 generates a piecewise linear polynomial function \cite{practicalbox}. 
@@
 
-We now turn to the problem of designing filters that discretize the operator 
-$\ftpairs{\invlaplacian}{(-4\pi^2(\omega_1^2 +\omega_2^2))^{-1}}$, and are to be used in conjunction with the tensor-product B-splines.
+We now turn to the problem of designing filters that discretize the operator $\ftpairs{\invlaplacian}{(-4\pi^2(\omega_1^2 +\omega_2^2))^{-1}}$, and are to be used in conjunction with the tensor-product B-splines.
 For the generator $M_{\Xii_{C4}}$, we are interested in a $4$-th order asymptotically optimal discretization of the inverse Laplacian $\invlaplacian$. 
@@
 
-Since $M_{\Xii_{C4}}$ is a compact generator, $p_{M_{\Xii_{C4}}^k}$ will also be a compact filter. Furthermore, since $\tpbs^k$ is separable, $p_{\tpbs^k}$ can be
-determined by sampling $\cbs^k(x)$ to yield the filter $p_{\cbs^k}[n] =
-\cbs^k(n)$ where $n \in \ints$. The weights of $p_{M_{\Xii_{C4}}}$ are then obtained
-by a simple tensor product, i.e. $p_{M_{\Xii_{C4}}^k}[n_1,n_2,n_3] =
-p_{\cbs^k}[n_1]p_{\cbs^k}[n_2] \ftpairs{}{} \ft{P}_{\tpbs^k}(\omega_1,\omega_2,\omega_3) = \ft{P}_{\cbs^k}(\omega_1)\ft{P}_{\cbs^k}(\omega_2)\ft{P}_{\cbs^k}(\omega_3)$.
+Since $M_{\Xii_{C4}}$ is a compact generator, $p_{M_{\Xii_{C4}}^k}$ will also be a compact filter. 
+Furthermore, since $\tpbs^k$ is separable, $p_{\tpbs^k}$ can be determined by sampling $\cbs^k(x)$ to yield the filter $p_{\cbs^k}[n] = \cbs^k(n)$ where $n \in \ints$. 
+The weights of $p_{M_{\Xii_{C4}}}$ are then obtained by a simple tensor product, i.e.
+$p_{M_{\Xii_{C4}}^k}[n_1,n_2,n_3] = p_{\cbs^k}[n_1]p_{\cbs^k}[n_2] \ftpairs{}{} \ft{P}_{\tpbs^k}(\omega_1,\omega_2,\omega_3) = \ft{P}_{\cbs^k}(\omega_1)\ft{P}_{\cbs^k}(\omega_2)\ft{P}_{\cbs^k}(\omega_3)$.
 
-As for the filter $\lambda$ that discretizes $\laplacian$, we follow a
-similar approach and first look for a symmetric and compact 1D filter
-$\lambda_1$ that satisfies the 1D analog of~\eqref{eq:opCriterionHomo},
-i.e. $\ft{\Lambda}_1(\omega) = -4\pi^2\omega^2 + O(\omega^{k+3})$. The
-unknown filter weights are determined by requiring that the Taylor
-developments of $(\ft{\Lambda}_1(\omega) + 4\pi^2\omega^2)$ be zero up to
-$\omega^{k+3}$. The filter $\ftpairs{\lambda}{\ft{\Lambda}}$ is then given by a
-simple addition, i.e. $\ft{\Lambda}(\omega_1,\omega_2) =
-\ft{\Lambda}_1(\omega_1) + \ft{\Lambda}_1(\omega_2)$.
+As for the filter $\lambda$ that discretizes $\laplacian$, we follow a similar approach and first look for a symmetric and compact 1D filter $\lambda_1$ that satisfies the 1D analog of~\eqref{eq:opCriterionHomo}, i.e.
+$\ft{\Lambda}_1(\omega) = -4\pi^2\omega^2 + O(\omega^{k+3})$.
+The unknown filter weights are determined by requiring that the Taylor developments of $(\ft{\Lambda}_1(\omega) + 4\pi^2\omega^2)$ be zero up to $\omega^{k+3}$.
+The filter $\ftpairs{\lambda}{\ft{\Lambda}}$ is then given by a simple addition, i.e.
+$\ft{\Lambda}(\omega_1,\omega_2) = \ft{\Lambda}_1(\omega_1) + \ft{\Lambda}_1(\omega_2)$.
 
-The sizes of $p_{\cbs^k}$ and $\lambda_1$ obviously depend on the degree
-$k$. The filters used in our experiments are tabulated in
-Table~\ref{tab:filters}.
+The sizes of $p_{\cbs^k}$ and $\lambda_1$ obviously depend on the degree $k$. 
+The filters used in our experiments are tabulated in table~\ref{tab:filters}.
 
@@
 \paragraph{Quasi-Interpolation}
-For the quasi-interpolative model, we need the additional filter
-$q$~\eqref{eq:quasiWeights}. Choosing $\psi$ to be the tensor product
-B-spline $\tpbs^l$ where $l>k$, the weights of $q$ are given by the
-tensor product of the 1D filter $q_1[n] := (\cbs^l \ast
-\dual{\cbs}^k)(n)$ with itself. Using the recursive definition
-of the 1D B-splines, $q_1$ can be further split as $q_1[n]
-= (w_1 \ast a_{\cbs^k}^{-1})[n]$ where $w_1[n] := \cbs^{k+l+1}(n)$ and
-$\ftpairs{a_{\cbs^k}^{-1}[\cdot]}{\tfrac{1}{\ft{A}_{\cbs^k}(\cdot)}}$. Example
-filter weights for the case $l=5$ are provided in Table~\ref{tab:filters}.
+For the quasi-interpolative model, we need the additional filter $q$~\eqref{eq:quasiWeights}.
+Choosing $\psi$ to be the tensor product B-spline $\tpbs^l$ where $l>k$, the weights of $q$ are given by the
+tensor product of the 1D filter $q_1[n] := (\cbs^l \ast \dual{\cbs}^k)(n)$ with itself. 
+Using the recursive definition of the 1D B-splines, $q_1$ can be further split as $q_1[n] = (w_1 \ast a_{\cbs^k}^{-1})[n]$ where $w_1[n] := \cbs^{k+l+1}(n)$ and $\ftpairs{a_{\cbs^k}^{-1}[\cdot]}{\tfrac{1}{\ft{A}_{\cbs^k}(\cdot)}}$.
+Example filter weights for the case $l=5$ are provided in Table~\ref{tab:filters}.
 
 \subsubsection{BCC Lattice}
-It is convenient to introduce a scaled version of the BCC lattice
-$\lattice{H}$ generated by the matrix $\mat{H} =
-\sqrt[3]{4}\mat{B}$. With respect to $\lattice{H}$, we denote the
-order-$k$ ($k \in 2\ints_+$) rhombic-dodecahedral box spline as
-$\bccbs{k}(\vect{x}) :=
-\boxsp[k/2]{\mat{\Theta}}(\vect{x}/\sqrt[3]{4})$. Note that $k$ now
-refers to the approximation order of the box-spline rather than its
-polynomial degree.
+It is convenient to introduce a scaled version of the BCC lattice $\lattice{H}$ generated by the matrix $\mat{H} = \sqrt[3]{4}\mat{B}$. 
+With respect to $\lattice{H}$, we denote the order-$k$ ($k \in 2\ints_+$) rhombic-dodecahedral box spline as $\bccbs{k}(\vect{x}) := \boxsp[k/2]{\mat{\Theta}}(\vect{x}/\sqrt[3]{4})$. 
+Note that $k$ now refers to the approximation order of the box-spline rather than its polynomial degree.
 
 \paragraph{Interpolation}
-The operator we wish to discretize is
-$\ftpairs{\invlaplacian}{-4\pi^2(\omega_1^2 + \omega_2^2 + \omega_3^2)^{-1}}$.
-According to~Proposition~\ref{prop:1}, we need the combined filter
-$(p_{\bccbs{k}} \ast \lambda)$ where $\ftpairs{\lambda}{\ft{\Lambda}}$
-satisfies~\eqref{eq:discreteLaplacian}, i.e. $\ft{\Lambda}(\vect{\omega}) =
--4\pi^2\norm{\vect{\omega}}^2 + O(\norm{\vect{\omega}}^{k+2})$. The compact
-filter $p_{\bccbs{k}}$ is non-separable and is determined by the samples of
-$\bccbs{k}$, i.e.
-$p_{\bccbs{k}}[\vect{x}_j] = \bccbs{k}(\vect{x}_j)$ where $\vect{x}_j \in
-\lattice{H}$.
+The operator we wish to discretize is $\ftpairs{\invlaplacian}{-4\pi^2(\omega_1^2 + \omega_2^2 + \omega_3^2)^{-1}}$. 
+According to~Proposition~\ref{prop:1}, we need the combined filter $(p_{\bccbs{k}} \ast \lambda)$ where $\ftpairs{\lambda}{\ft{\Lambda}}$ satisfies~\eqref{eq:discreteLaplacian}, i.e.
+$\ft{\Lambda}(\vect{\omega}) = -4\pi^2\norm{\vect{\omega}}^2 + O(\norm{\vect{\omega}}^{k+2})$.
+The compact filter $p_{\bccbs{k}}$ is non-separable and is determined by the samples of $\bccbs{k}$, i.e. $p_{\bccbs{k}}[\vect{x}_j] = \bccbs{k}(\vect{x}_j)$ where $\vect{x}_j \in \lattice{H}$.
 
@@
 \end{equation}
-where the (scaled) box spline direction vectors $\vect{\theta}_i$ ($i
-\in \{1,2,3,4\}$) correspond to the column vectors
-$\transp{(1,1,-1)}$, $\transp{(1,-1,1)}$, $\transp{(-1,1,1)}$ and
-$\transp{(-1,-1,-1)}$ respectively. Since $\vect{\theta}_i \in
-\lattice{H}$, we can re-use the 1D filter $\lambda_1[n]$ from the
-previous section and apply it across the directions $\vect{\theta}_i$
-to yield the filter $\lambda$.  Therefore,
-$\ftpairs{\lambda}{\ft{\Lambda}}$ is given by
+where the (scaled) box spline direction vectors $\vect{\theta}_i$ ($i \in \{1,2,3,4\}$) correspond to the column vectors $\transp{(1,1,-1)}$, $\transp{(1,-1,1)}$, $\transp{(-1,1,1)}$ and $\transp{(-1,-1,-1)}$ respectively.
+Since $\vect{\theta}_i \in \lattice{H}$, we can re-use the 1D filter $\lambda_1[n]$ from the previous section and apply it across the directions $\vect{\theta}_i$ to yield the filter $\lambda$.
+Therefore, $\ftpairs{\lambda}{\ft{\Lambda}}$ is given by
 \begin{equation}
@@
 \end{equation}
-where the 1D filter $\ftpairs{\lambda_1}{\ft{\Lambda}_1}$ satisfies 
-$\ft{\Lambda}_1(\omega) = -4\pi^2\omega^2 + O(\omega^{k+2})$.
+where the 1D filter $\ftpairs{\lambda_1}{\ft{\Lambda}_1}$ satisfies  $\ft{\Lambda}_1(\omega) = -4\pi^2\omega^2 + O(\omega^{k+2})$.
 
-Table~\ref{tab:filtersBCC} summarizes the various filters that are the
-BCC analogs of Cartesian filters listed in Table~\ref{tab:filters}.
+Table~\ref{tab:filtersBCC} summarizes the various filters that are the BCC analogs of Cartesian filters listed in Table~\ref{tab:filters}.
 
@@
 	\caption{Filters used in our experiments. These filters are applied along the principal lattice directions.}
-	\label{tab:filters}
+	\label{tab:d_filters}
 \end{table}
@@
 We measure both the Hausdorff distance, mean distance, and angle deviation from the original shape with the tools provided by Berger et al.~\cite{reconbench}. 
-We evaluate the FFT, Poisson, and Screened Poisson surface reconstruction algorithms, as their theory is close to ours.
+We evaluate the FFT, Poisson, and Screened Poisson surface reconstruction algorithms, as their collective underlying theory and methodology is close to ours. 
 We choose $\lambda_1$ and $\lambda_2$ so that the reconstructions are comparable to the Screened Poisson results.
@@
 %You should really try to bring out the role of the shifts.
-We fix the resolution of the grid at $128^3$, and reconstruct the remaining models (\FG{fig:t2}.) We choose this resolution as it seems to be a point of contention between the cases with the Gargoyle model.
+We fix the resolution of the grid at $128^3$, and reconstruct the remaining models (\FG{fig:t2}), 
+We choose this resolution as it seems to be a point of contention between the cases with the Gargoyle model.
 However, there seems to be a consistent advantage in using the BCC lattice over the Cartesian lattice. 

### 2015-09-11 approach.tex
cleaning up before the move to gitlab

@@
 This may seem unintuitive at first, however, using a non-canonical basis to represent $\vec{V}$ will be convenient in two ways. 
-Firstly, it will allow us to approximate the divergence of $\vec{V}$ by taking directional derivatives of $\vec{V}$ in the principal lattice directions. 
+First, it will allow us to approximate the divergence of $\vec{V}$ by taking directional derivatives of $\vec{V}$ in the principal lattice directions. 
 This is motivated by the fact that it is more natural to approximate derivatives in the principal lattice directions on non-Cartesian lattices. 
-Secondly, it will allow us to construct divergence of the smoothed normal field from more than three principal lattice directions. 
+Second, it will allow us to construct divergence of the smoothed normal field from more than three principal lattice directions. 
 We also allow each function $\upsilon_i$ to potentially be represented in different function spaces, i.e. {\small 

### 2015-09-11 prelim.tex
cleaning up before the move to gitlab

@@
 where ${\mathbf{\Xii/\xi}_n}$ is the matrix obtained by removing the column vector $\xi_n$ from $\mathbf{\Xii}$. 
-Box splines are a natural fit for our purposes, and are chosen to span our function spaces.
+Box splines are a natural fit for our purposes, and are chosen as bases for our reconstruction spaces.
 One motivating factor that encourages the use of box splines on the BCC lattice over the Cartesian lattice is that the support of the box splines on the BCC lattice contains less lattice sites as opposed to their Cartesian counterparts.
@@
 Our proposed cost functional is then $E(g) := \lambda_1 \left|\left|{g}\right|\right| + \lambda_2 \bln{2}{g}.$ 
-Here, $\lambda_1$ controls the amount to which the function is penalized for large coefficient values. 
+Here, $\lambda_1$ controls the penalization of the function large coefficient values. 
 When combined with the interpolation constraint, this imposes the behavior of forcing the function to be zero away from the surface. 
